---
title: "ConditioningAnalysis"
author: "KMG"
date: "February 15, 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
setwd("C:/Users/kkmgo/Dropbox/Conditioning_MagFields_Project/2017/Behavioral_Observations/Waddling/CSV_WaddleFiles/")
getwd()
```

#December 9

##Read in files
```{r}
L153Dec9W<-read.csv("L153_Dec9_Waddle2.csv")
L154Dec9W<-read.csv("L154_Dec9_Waddle2.csv")
L156Dec9W<-read.csv("L156_Dec9_Waddle2.csv")
L159Dec9W<-read.csv("L159_Dec9_Waddle2.csv")
L161Dec9W<-read.csv("L161_Dec9_Waddle2.csv")
#L162Dec9W<-read.csv("L162_Dec9_Waddle2.csv")
L165Dec9W<-read.csv("L165_Dec9_Waddle5.csv",skip=15,header=T)
L167Dec9W<-read.csv("L167_Dec9_Waddle5.csv",skip=15,header=T)
```

stringr
split - file names
str_split
separate in dplyr

```{r}
#library(dplyr)
#L153Dec9W<-L153Dec9W %>% mutate(diff=Time-lag(Time,default=first(Time)))

L153Dec9W$ID<-rep(NA)
L153Dec9W$ID<-L153Dec9W$ID[is.na(L153Dec9W$ID)]<- "L153"
L154Dec9W$ID<-rep(NA)
L154Dec9W$ID<-L154Dec9W$ID[is.na(L154Dec9W$ID)]<- "L154"
L156Dec9W$ID<-rep(NA)
L156Dec9W$ID<-L156Dec9W$ID[is.na(L156Dec9W$ID)]<- "L156"
L159Dec9W$ID<-rep(NA)
L159Dec9W$ID<-L159Dec9W$ID[is.na(L159Dec9W$ID)]<- "L159"
L161Dec9W$ID<-rep(NA)
L161Dec9W$ID<-L161Dec9W$ID[is.na(L161Dec9W$ID)]<- "L161"
#L162Dec9W$ID<-rep(NA)
#L162Dec9W$ID<-L162Dec9W$ID[is.na(L162Dec9W$ID)]<- "L162"
L165Dec9W$ID<-rep(NA)
L165Dec9W$ID<-L165Dec9W$ID[is.na(L165Dec9W$ID)]<- "L165"
L167Dec9W$ID<-rep(NA)
L167Dec9W$ID<-L167Dec9W$ID[is.na(L167Dec9W$ID)]<- "L167"
```

##Change Names in Files
```{r}
library(plyr)
dfs_Dec9<-list(L153Dec9W,L154Dec9W,L156Dec9W,L159Dec9W,L161Dec9W,L165Dec9W,L167Dec9W)

drops<-c("Total.length","FPS","Subject","Comment","Status")

DropFunction<- function(x) {
  x<-x[ , !(names(x) %in% drops)]
  return(x)
}


Dec9_Waddle = ldply(dfs_Dec9,DropFunction)

names(Dec9_Waddle)<-c("Time","Observer", "Behavior", "Start_Stop","ID")
  
```

##Combine Data to get TimeEl
```{r}
Dec9_StartTimes<-subset(Dec9_Waddle,Start_Stop== "START")
names(Dec9_StartTimes)<- c("StartTime","Observer", "Behavior","Start","ID")
Dec9_StopTimes<-subset(Dec9_Waddle,Start_Stop=="STOP")
names(Dec9_StopTimes)<-c("StopTime","Observer", "Behavior","Stop","ID")
```

Not used.
```{r}Dec9_L153W<-cbind(Dec9_L153_StartTimes,Dec9_L153_StopTimes)
drop_some<-c("Start","Stop")
Dec9_L153W<-Dec9_L153W[ , !(names(Dec9_L153W) %in% drop_some)]
drop_some<-c("ID.1","Behavior.1")
Dec9_L153W<-Dec9_L153W[ , !(names(Dec9_L153W) %in% drop_some)]
library(dplyr)
Dec9_L153W<-mutate(Dec9_L153W,TimeEl=StopTime-StartTime)
```

```{r}
#library(data.table)
#Dec9_StartTimes<-as.data.table(Dec9_StartTimes)
#Dec9_StopTimes<-as.data.table(Dec9_StopTimes)
#Dec9_StartTimes<-as.data.frame(Dec9_StartTimes)
#Dec9_StopTimes<-as.data.frame(Dec9_StopTimes)
#Dec9_StartTimes$StopTime<-NA
#Dec9_StopTimes$StartTime<-NA
#drops_start<-c("Start")
#Dec9_StartTimes<-Dec9_StartTimes[ , !(names(Dec9_StartTimes) %in% drops_start)]
#drops_stop<-c("Stop")
#Dec9_StopTimes<-Dec9_StopTimes[ , !(names(Dec9_StopTimes) %in% drops_stop)]
```

```{r}
Dec9_WaddleTimes<-cbind(Dec9_StartTimes,Dec9_StopTimes)
names(Dec9_WaddleTimes)<-c("StartTime","Observer", "Behavior","Start","ID","StopTime","Obs.2", "Beh.2","Stop","ID.2")
drops_doubles<-c("Start","Obs.2", "Beh.2","Stop","ID.2")
Dec9_WaddleTimes<-Dec9_WaddleTimes[ , !(names(Dec9_WaddleTimes) %in% drops_doubles)]
Dec9_WaddleTimes<-mutate(Dec9_WaddleTimes,TimeEl=StopTime-StartTime)
Dec9_WaddleTimes<-mutate(Dec9_WaddleTimes,Minutes=StartTime/60)
Dec9_WaddleTimes<-mutate(Dec9_WaddleTimes,Date=rep("Dec9"))
```

##Subset Data by ID to set acclimation and test periods

```{r}
library(dplyr)
L153Dec9_W1<-filter(Dec9_WaddleTimes,ID=="L153")
L153Dec9_W1$Observer<-rep(NA)
L153Dec9_W1$Observer<-L153Dec9_W1$Observer[is.na(L153Dec9_W1$Observer)]<- "KaG"

L154Dec9_W1<-filter(Dec9_WaddleTimes,ID=="L154")
L154Dec9_W1$Observer<-rep(NA)
L154Dec9_W1$Observer<-L154Dec9_W1$Observer[is.na(L154Dec9_W1$Observer)]<- "KaG"

L156Dec9_W1<-filter(Dec9_WaddleTimes,ID=="L156")
L156Dec9_W1$Observer<-rep(NA)
L156Dec9_W1$Observer<-L156Dec9_W1$Observer[is.na(L156Dec9_W1$Observer)]<- "AnJ"

L159Dec9_W1<-filter(Dec9_WaddleTimes,ID=="L159")
L159Dec9_W1$Observer<-rep(NA)
L159Dec9_W1$Observer<-L159Dec9_W1$Observer[is.na(L159Dec9_W1$Observer)]<- "AnJ"

L161Dec9_W1<-filter(Dec9_WaddleTimes,ID=="L161")
L161Dec9_W1$Observer<-rep(NA)
L161Dec9_W1$Observer<-L161Dec9_W1$Observer[is.na(L161Dec9_W1$Observer)]<- "NiI"

#L162Dec9_W1<-filter(Dec9_WaddleTimes,ID=="L162")
L165Dec9_W1<-filter(Dec9_WaddleTimes,ID=="L165")
L165Dec9_W1$Observer<-rep(NA)
L165Dec9_W1$Observer<-L165Dec9_W1$Observer[is.na(L165Dec9_W1$Observer)]<- "NiI"

L167Dec9_W1<-filter(Dec9_WaddleTimes,ID=="L167")
L167Dec9_W1$Observer<-rep(NA)
L167Dec9_W1$Observer<-L167Dec9_W1$Observer[is.na(L167Dec9_W1$Observer)]<- "MjH"
```
use string split
```{r}
library(dplyr)
L153Dec9_W1_accl<-filter(L153Dec9_W1,Minutes<=21)
L153Dec9_W1_test<-filter(L153Dec9_W1,Minutes>21 & Minutes<=41)
L154Dec9_W1_accl<-filter(L154Dec9_W1,Minutes<=22)
L154Dec9_W1_test<-filter(L154Dec9_W1,Minutes>22 & Minutes<=42)
L156Dec9_W1_accl<-filter(L156Dec9_W1,Minutes<=21)
L156Dec9_W1_test<-filter(L156Dec9_W1,Minutes>21 & Minutes<=41)
L159Dec9_W1_accl<-filter(L159Dec9_W1,Minutes<=21)
L159Dec9_W1_test<-filter(L159Dec9_W1,Minutes>21 & Minutes<=41)
L161Dec9_W1_accl<-filter(L161Dec9_W1,Minutes<=21)
L161Dec9_W1_test<-filter(L161Dec9_W1,Minutes>21 & Minutes<=41)
#L162Dec9_W1_accl<-filter(L162Dec9_W1,Minutes<=21)
#L162Dec9_W1_test<-filter(L162Dec9_W1,Minutes>21 & Minutes<=41)
L165Dec9_W1_accl<-filter(L165Dec9_W1,Minutes<=22)
L165Dec9_W1_test<-filter(L165Dec9_W1,Minutes>22 & Minutes<=41)
L167Dec9_W1_accl<-filter(L167Dec9_W1,Minutes<=21)
L167Dec9_W1_test<-filter(L167Dec9_W1,Minutes>21 & Minutes<=41)
```

Five Mins Dec9 Waddle 1

```{r}
library(dplyr)
L153Dec9_W1_test5<-filter(L153Dec9_W1,Minutes>21 & Minutes<=26)

L154Dec9_W1_test5<-filter(L154Dec9_W1,Minutes>22 & Minutes<=27)

L156Dec9_W1_test5<-filter(L156Dec9_W1,Minutes>21 & Minutes<=26)

L159Dec9_W1_test5<-filter(L159Dec9_W1,Minutes>21 & Minutes<=26)

L161Dec9_W1_test5<-filter(L161Dec9_W1,Minutes>21 & Minutes<=26)
#L162Dec9_W1_accl<-filter(L162Dec9_W1,Minutes<=21)
#L162Dec9_W1_test<-filter(L162Dec9_W1,Minutes>21 & Minutes<=41)

L165Dec9_W1_test5<-filter(L165Dec9_W1,Minutes>22 & Minutes<=27)

L167Dec9_W1_test5<-filter(L167Dec9_W1,Minutes>21 & Minutes<=26)

Dec9_W1_test5_BH<-rbind(L153Dec9_W1_test5,L156Dec9_W1_test5,L161Dec9_W1_test5,L165Dec9_W1_test5)
Dec9_W1_test5_BH<-mutate(Dec9_W1_test5_BH,FieldType=rep("conditioned"))
Dec9_W1_test5_NB<-rbind(L154Dec9_W1_test5,L159Dec9_W1_test5,L167Dec9_W1_test5)
Dec9_W1_test5_NB<-mutate(Dec9_W1_test5_NB,FieldType=rep("control"))
Dec9_W1_test5<-rbind(Dec9_W1_test5_BH,Dec9_W1_test5_NB)

Dec9_W1_test5<-Dec9_W1_test5 %>% group_by(ID,Observer,FieldType) %>% summarise(TotalTimeEl=sum(TimeEl)) 
```

#Dec9 W1 ten mins

```{r}
library(dplyr)
L153Dec9_W1_test10<-filter(L153Dec9_W1,Minutes>21 & Minutes<=31)

L154Dec9_W1_test10<-filter(L154Dec9_W1,Minutes>22 & Minutes<=32)

L156Dec9_W1_test10<-filter(L156Dec9_W1,Minutes>21 & Minutes<=31)

L159Dec9_W1_test10<-filter(L159Dec9_W1,Minutes>21 & Minutes<=31)

L161Dec9_W1_test10<-filter(L161Dec9_W1,Minutes>21 & Minutes<=31)
#L162Dec9_W1_accl<-filter(L162Dec9_W1,Minutes<=21)
#L162Dec9_W1_test<-filter(L162Dec9_W1,Minutes>21 & Minutes<=41)

L165Dec9_W1_test10<-filter(L165Dec9_W1,Minutes>22 & Minutes<=32)

L167Dec9_W1_test10<-filter(L167Dec9_W1,Minutes>21 & Minutes<=31)

Dec9_W1_test10_BH<-rbind(L153Dec9_W1_test10,L156Dec9_W1_test10,L161Dec9_W1_test10,L165Dec9_W1_test10)
Dec9_W1_test10_BH<-mutate(Dec9_W1_test10_BH,FieldType=rep("conditioned"))
Dec9_W1_test10_NB<-rbind(L154Dec9_W1_test10,L159Dec9_W1_test10,L167Dec9_W1_test10)
Dec9_W1_test10_NB<-mutate(Dec9_W1_test10_NB,FieldType=rep("control"))
Dec9_W1_test10<-rbind(Dec9_W1_test10_BH,Dec9_W1_test10_NB)

Dec9_W1_test10<-Dec9_W1_test10 %>% group_by(ID,Observer,FieldType) %>% summarise(TotalTimeEl=sum(TimeEl)) 
```



```{r}
library(dplyr)
Dec9_W1_accl_BH<-rbind(L153Dec9_W1_accl,L156Dec9_W1_accl,L161Dec9_W1_accl,L165Dec9_W1_accl)
Dec9_W1_test_BH<-rbind(L153Dec9_W1_test,L156Dec9_W1_test,L161Dec9_W1_test,L165Dec9_W1_test)

Dec9_W1_accl_BH<-mutate(Dec9_W1_accl_BH,Field=rep("BH"))
Dec9_W1_accl_BH<-mutate(Dec9_W1_accl_BH,TimePer=rep("accl"))
Dec9_W1_accl_BH<-mutate(Dec9_W1_accl_BH,FieldType=rep("conditioned"))
Dec9_W1_test_BH<-mutate(Dec9_W1_test_BH,Field=rep("BH"))
Dec9_W1_test_BH<-mutate(Dec9_W1_test_BH,TimePer=rep("test"))
Dec9_W1_test_BH<-mutate(Dec9_W1_test_BH,FieldType=rep("conditioned"))
```

```{r}
library(dplyr)
Dec9_W1_accl_NB<-rbind(L154Dec9_W1_accl,L159Dec9_W1_accl, L167Dec9_W1_accl)
Dec9_W1_test_NB<-rbind(L154Dec9_W1_test,L159Dec9_W1_test,L167Dec9_W1_test)
library(dplyr)
Dec9_W1_accl_NB<-mutate(Dec9_W1_accl_NB,Field=rep("NB"))
Dec9_W1_accl_NB<-mutate(Dec9_W1_accl_NB,TimePer=rep("accl"))
Dec9_W1_accl_NB<-mutate(Dec9_W1_accl_NB,FieldType=rep("control"))
Dec9_W1_test_NB<-mutate(Dec9_W1_test_NB,Field=rep("NB"))
Dec9_W1_test_NB<-mutate(Dec9_W1_test_NB,TimePer=rep("test"))
Dec9_W1_test_NB<-mutate(Dec9_W1_test_NB,FieldType=rep("control"))
```

##Master Data Sets
```{r}
library(dplyr)
Dec9_W1<-rbind(Dec9_W1_accl_BH,Dec9_W1_accl_NB,Dec9_W1_test_BH,Dec9_W1_test_NB)
Dec9_W1<-mutate(Dec9_W1,Date=rep("Dec9"))
Dec9_W1_BH<-rbind(Dec9_W1_accl_BH,Dec9_W1_test_BH)
Dec9_W1_NB<-rbind(Dec9_W1_accl_NB,Dec9_W1_test_NB)
```

```{r}
detach(package:plyr)
library(dplyr)
Dec9_W1<-Dec9_W1 %>% group_by(ID,TimePer,Observer,Field,FieldType,Date) %>% summarise(TotalTimeEl=sum(TimeEl)) 
Dec9_W1_test<-filter(Dec9_W1,TimePer=="test")
```
##good to here


#Dec 9 Second Analysis

```{r}
L153Dec9_W2<-read.csv("L153_Dec9_Waddle4.csv",skip=15,header=T)
L154Dec9_W2<-read.csv("L154_Dec9_Waddle4.csv",skip=15,header=T)
L156Dec9_W2<-read.csv("L156_Dec9_Waddle4.csv",skip=15,header=T)
L161Dec9_W2<-read.csv("L161_Dec9_Waddle4.csv",skip=15,header=T)
L165Dec9_W2<-read.csv("L165_Dec9_Waddle5.csv",skip=15,header=T)
L167Dec9_W2<-read.csv("L167_Dec9_Waddle4.csv",skip=15,header=T)
```

```{r}

L153Dec9_W2$ID<-rep(NA)
L153Dec9_W2ID<-L153Dec9_W2$ID[is.na(L153Dec9_W2$ID)]<- "L153"
L154Dec9_W2$ID<-rep(NA)
L154Dec9_W2$ID<-L154Dec9_W2$ID[is.na(L154Dec9_W2$ID)]<- "L154"
L156Dec9_W2$ID<-rep(NA)
L156Dec9_W2$ID<-L156Dec9_W2$ID[is.na(L156Dec9_W2$ID)]<- "L156"
#L159Dec_9W2$ID<-rep(NA)
#L159Dec_9W2$ID<-L159Dec9_W2$ID[is.na(L159Dec9_W2$ID)]<- "L159"
L161Dec9_W2$ID<-rep(NA)
L161Dec9_W2$ID<-L161Dec9_W2$ID[is.na(L161Dec9_W2$ID)]<- "L161"
#L162Dec9_W2$ID<-rep(NA)
#L162Dec9_W2$ID<-L162Dec9_W2$ID[is.na(L162Dec9_W2$ID)]<- "L162"
L165Dec9_W2$ID<-rep(NA)
L165Dec9_W2$ID<-L165Dec9_W2$ID[is.na(L165Dec9_W2$ID)]<- "L165"
L167Dec9_W2$ID<-rep(NA)
L167Dec9_W2$ID<-L167Dec9_W2$ID[is.na(L167Dec9_W2$ID)]<- "L167"
```

##Change Names in Files
```{r}
library(plyr)
dfs_Dec9_2<-list(L153Dec9_W2,L154Dec9_W2,L156Dec9_W2,L165Dec9_W2,L167Dec9_W2,L161Dec9_W2)

drops<-c("Total.length","FPS","Subject","Comment","Status")

DropFunction<- function(x) {
  x<-x[ , !(names(x) %in% drops)]
  return(x)
}

Dec9_Waddle2 = ldply(dfs_Dec9_2,DropFunction)

names(Dec9_Waddle2)<-c("Time","Observer", "Behavior", "Start_Stop","ID")

detach(package:plyr)
```

##Combine Data to get TimeEl
```{r}
Dec9_StartTimes2<-subset(Dec9_Waddle2,Start_Stop== "START")
names(Dec9_StartTimes2)<- c("StartTime","Observer", "Behavior","Start","ID")
Dec9_StopTimes2<-subset(Dec9_Waddle2,Start_Stop=="STOP")
names(Dec9_StopTimes2)<-c("StopTime","Observer", "Behavior","Stop","ID")
```
###lag

```{r}
Dec9_WaddleTimes2<-cbind(Dec9_StartTimes2,Dec9_StopTimes2)
names(Dec9_WaddleTimes2)<-c("StartTime","Observer", "Behavior","Start","ID","StopTime","Obs.2", "Beh.2","Stop","ID.2")
drops_doubles<-c("Start","Obs.2", "Beh.2","Stop","ID.2")
Dec9_WaddleTimes2<-Dec9_WaddleTimes2[ , !(names(Dec9_WaddleTimes2) %in% drops_doubles)]
Dec9_WaddleTimes2<-mutate(Dec9_WaddleTimes2,TimeEl=StopTime-StartTime)
Dec9_WaddleTimes2<-mutate(Dec9_WaddleTimes2,Minutes=StartTime/60)
Dec9_WaddleTimes2<-mutate(Dec9_WaddleTimes2,Date=rep("Dec9"))
```


##Subset Data by ID to set acclimation and test periods

```{r}
library(dplyr)
L153Dec9_W2<-filter(Dec9_WaddleTimes2,ID=="L153")
L153Dec9_W2$Observer<-rep(NA)
L153Dec9_W2$Observer<-L153Dec9_W2$Observer[is.na(L153Dec9_W2$Observer)]<- "AnJ"

L154Dec9_W2<-filter(Dec9_WaddleTimes2,ID=="L154")
L154Dec9_W2$Observer<-rep(NA)
L154Dec9_W2$Observer<-L154Dec9_W2$Observer[is.na(L154Dec9_W2$Observer)]<- "AnJ"

L156Dec9_W2<-filter(Dec9_WaddleTimes2,ID=="L156")
L156Dec9_W2$Observer<-rep(NA)
L156Dec9_W2$Observer<-L156Dec9_W2$Observer[is.na(L156Dec9_W2$Observer)]<- "KaG"

#L159Dec9_W3<-filter(Dec9_WaddleTimes3,ID=="L159")

L161Dec9_W2<-filter(Dec9_WaddleTimes2,ID=="L161")
L161Dec9_W2$Observer<-rep(NA)
L161Dec9_W2$Observer<-L161Dec9_W2$Observer[is.na(L161Dec9_W2$Observer)]<- "KaG" 

#L162Dec9_W3<-filter(Dec9_WaddleTimes,ID=="L162")



L165Dec9_W2<-filter(Dec9_WaddleTimes2,ID=="L165")
L165Dec9_W2$Observer<-rep(NA)
L165Dec9_W2$Observer<-L165Dec9_W2$Observer[is.na(L165Dec9_W2$Observer)]<- "MjH"


L167Dec9_W2<-filter(Dec9_WaddleTimes2,ID=="L167")
L167Dec9_W2$Observer<-rep(NA)
L167Dec9_W2$Observer<-L167Dec9_W2$Observer[is.na(L167Dec9_W2$Observer)]<- "EmT"

```

```{r}
library(dplyr)
L153Dec9_W2_accl<-filter(L153Dec9_W2,Minutes<=21)
L153Dec9_W2_test<-filter(L153Dec9_W2,Minutes>21 & Minutes<=41)
L154Dec9_W2_accl<-filter(L154Dec9_W2,Minutes<=22)
L154Dec9_W2_test<-filter(L154Dec9_W2,Minutes>22 & Minutes<=42)
L156Dec9_W2_accl<-filter(L156Dec9_W2,Minutes<=21)
L156Dec9_W2_test<-filter(L156Dec9_W2,Minutes>21 & Minutes<=41)
#L159Dec9_W3_accl<-filter(L159Dec9_W3,Minutes<=21)
#L159Dec9_W3_test<-filter(L159Dec9_W3,Minutes>21 & Minutes<=41)
L161Dec9_W2_accl<-filter(L161Dec9_W2,Minutes<=21)
L161Dec9_W2_test<-filter(L161Dec9_W2,Minutes>21 & Minutes<=41)
#L162Dec9_W3_accl<-filter(L162Dec9_W3,Minutes<=21)
#L162Dec9_W3_test<-filter(L162Dec9_W3,Minutes>21)
L165Dec9_W2_accl<-filter(L165Dec9_W2,Minutes<=22 & Minutes<=42)
L165Dec9_W2_test<-filter(L165Dec9_W2,Minutes>22 & Minutes<=41)
L167Dec9_W2_accl<-filter(L167Dec9_W2,Minutes<=21)
L167Dec9_W2_test<-filter(L167Dec9_W2,Minutes>21 & Minutes<=41)
```


Dec9 W2 five min test
```{r}
library(dplyr)
L153Dec9_W2_test5<-filter(L153Dec9_W2,Minutes>21 & Minutes<=26)

L154Dec9_W2_test5<-filter(L154Dec9_W2,Minutes>22 & Minutes<=27)

L156Dec9_W2_test5<-filter(L156Dec9_W2,Minutes>21 & Minutes<=26)

#L159Dec9_W2_test5<-filter(L159Dec9_W2,Minutes>21 & Minutes<=26)

L161Dec9_W2_test5<-filter(L161Dec9_W2,Minutes>21 & Minutes<=26)
#L162Dec9_W1_accl<-filter(L162Dec9_W1,Minutes<=21)
#L162Dec9_W1_test<-filter(L162Dec9_W1,Minutes>21 & Minutes<=41)

L165Dec9_W2_test5<-filter(L165Dec9_W2,Minutes>22 & Minutes<=27)

L167Dec9_W2_test5<-filter(L167Dec9_W2,Minutes>21 & Minutes<=26)

Dec9_W2_test5_BH<-rbind(L153Dec9_W2_test5,L156Dec9_W2_test5,L161Dec9_W2_test5,L165Dec9_W2_test5)
Dec9_W2_test5_BH<-mutate(Dec9_W2_test5_BH,FieldType=rep("conditioned"))
Dec9_W2_test5_NB<-rbind(L154Dec9_W2_test5,L167Dec9_W2_test5)
Dec9_W2_test5_NB<-mutate(Dec9_W2_test5_NB,FieldType=rep("control"))
Dec9_W2_test5<-rbind(Dec9_W2_test5_BH,Dec9_W2_test5_NB)

Dec9_W2_test5<-Dec9_W2_test5 %>% group_by(ID,Observer,FieldType) %>% summarise(TotalTimeEl=sum(TimeEl)) 
```

Dec9 W2 ten min test
```{r}
library(dplyr)
L153Dec9_W2_test10<-filter(L153Dec9_W2,Minutes>21 & Minutes<=31)

L154Dec9_W2_test10<-filter(L154Dec9_W2,Minutes>22 & Minutes<=32)

L156Dec9_W2_test10<-filter(L156Dec9_W2,Minutes>21 & Minutes<=31)

#L159Dec9_W2_test5<-filter(L159Dec9_W2,Minutes>21 & Minutes<=26)

L161Dec9_W2_test10<-filter(L161Dec9_W2,Minutes>21 & Minutes<=31)
#L162Dec9_W1_accl<-filter(L162Dec9_W1,Minutes<=21)
#L162Dec9_W1_test<-filter(L162Dec9_W1,Minutes>21 & Minutes<=41)

L165Dec9_W2_test10<-filter(L165Dec9_W2,Minutes>22 & Minutes<=32)

L167Dec9_W2_test10<-filter(L167Dec9_W2,Minutes>21 & Minutes<=31)

Dec9_W2_test10_BH<-rbind(L153Dec9_W2_test10,L156Dec9_W2_test10,L161Dec9_W2_test10,L165Dec9_W2_test10)
Dec9_W2_test10_BH<-mutate(Dec9_W2_test10_BH,FieldType=rep("conditioned"))
Dec9_W2_test10_NB<-rbind(L154Dec9_W2_test10,L167Dec9_W2_test10)
Dec9_W2_test10_NB<-mutate(Dec9_W2_test10_NB,FieldType=rep("control"))
Dec9_W2_test10<-rbind(Dec9_W2_test10_BH,Dec9_W2_test10_NB)

Dec9_W2_test10<-Dec9_W2_test10 %>% group_by(ID,Observer,FieldType) %>% summarise(TotalTimeEl=sum(TimeEl)) 
```

```{r}
Dec9_W2_accl_BH<-rbind(L153Dec9_W2_accl,L156Dec9_W2_accl,L165Dec9_W2_accl,L161Dec9_W2_accl)
Dec9_W2_test_BH<-rbind(L153Dec9_W2_test,L156Dec9_W2_test,L165Dec9_W2_test,L161Dec9_W2_test)
library(dplyr)
Dec9_W2_accl_BH<-mutate(Dec9_W2_accl_BH,Field=rep("BH"))
Dec9_W2_accl_BH<-mutate(Dec9_W2_accl_BH,TimePer=rep("accl"))
Dec9_W2_accl_BH<-mutate(Dec9_W2_accl_BH,FieldType=rep("conditioned"))
Dec9_W2_test_BH<-mutate(Dec9_W2_test_BH,Field=rep("BH"))
Dec9_W2_test_BH<-mutate(Dec9_W2_test_BH,TimePer=rep("test"))
Dec9_W2_test_BH<-mutate(Dec9_W2_test_BH,FieldType=rep("conditioned"))
```

```{r}
Dec9_W2_accl_NB<-rbind(L154Dec9_W2_accl,L167Dec9_W2_accl)
Dec9_W2_test_NB<-rbind(L154Dec9_W2_test,L167Dec9_W2_test)
library(dplyr)
Dec9_W2_accl_NB<-mutate(Dec9_W2_accl_NB,Field=rep("NB"))
Dec9_W2_accl_NB<-mutate(Dec9_W2_accl_NB,TimePer=rep("accl"))
Dec9_W2_accl_NB<-mutate(Dec9_W2_accl_NB,FieldType=rep("control"))
Dec9_W2_test_NB<-mutate(Dec9_W2_test_NB,Field=rep("NB"))
Dec9_W2_test_NB<-mutate(Dec9_W2_test_NB,TimePer=rep("test"))
Dec9_W2_test_NB<-mutate(Dec9_W2_test_NB,FieldType=rep("control"))
```


##Master Data Sets - Dec9 Analysis 2
```{r}
Dec9_W2<-rbind(Dec9_W2_accl_BH,Dec9_W2_accl_NB,Dec9_W2_test_BH,Dec9_W2_test_NB)
Dec9_W2<-mutate(Dec9_W2,Date=rep("Dec9"))
Dec9_W2_BH<-rbind(Dec9_W2_accl_BH,Dec9_W2_test_BH)
Dec9_W2_NB<-rbind(Dec9_W2_accl_NB,Dec9_W2_test_NB)
```

```{r}
library(dplyr)
Dec9_W2<-Dec9_W2 %>% group_by(ID,TimePer,Observer,Field,FieldType,Date) %>% summarise(TotalTimeEl=sum(TimeEl))
Dec9_W2_test<-filter(Dec9_W2,TimePer=="test")
```

#Dec9 Third Analysis
```{r}
L153Dec9W3<-read.csv("L153_Dec9_Waddle3.csv")
L154Dec9W3<-read.csv("L154_Dec9_Waddle3.csv")
L156Dec9W3<-read.csv("L156_Dec9_Waddle5.csv",skip=15,header=T)
#L159Dec9W3<-read.csv("L159_Dec9_Waddle3.csv")
L161Dec9W3<-read.csv("L161_Dec9_Waddle5.csv",skip=15,header=T)
L162Dec9W3<-read.csv("L162_Dec9_Waddle3.csv")
L165Dec9W3<-read.csv("L165_Dec9_Waddle3.csv")
L167Dec9W3<-read.csv("L167_Dec9_Waddle3.csv")
```


```{r}

L153Dec9W3$ID<-rep(NA)
L153Dec9W3$ID<-L153Dec9W3$ID[is.na(L153Dec9W3$ID)]<- "L153"
L154Dec9W3$ID<-rep(NA)
L154Dec9W3$ID<-L154Dec9W3$ID[is.na(L154Dec9W3$ID)]<- "L154"
L156Dec9W3$ID<-rep(NA)
L156Dec9W3$ID<-L156Dec9W3$ID[is.na(L156Dec9W3$ID)]<- "L156"
#L159Dec9W3$ID<-rep(NA)
#L159Dec9W3$ID<-L159Dec9W3$ID[is.na(L159Dec9W3$ID)]<- "L159"
L161Dec9W3$ID<-rep(NA)
L161Dec9W3$ID<-L161Dec9W3$ID[is.na(L161Dec9W3$ID)]<- "L161"
L162Dec9W3$ID<-rep(NA)
L162Dec9W3$ID<-L162Dec9W3$ID[is.na(L162Dec9W3$ID)]<- "L162"
L165Dec9W3$ID<-rep(NA)
L165Dec9W3$ID<-L165Dec9W3$ID[is.na(L165Dec9W3$ID)]<- "L165"
L167Dec9W3$ID<-rep(NA)
L167Dec9W3$ID<-L167Dec9W3$ID[is.na(L167Dec9W3$ID)]<- "L167"
```


##Change Names in Files
```{r}
library(plyr)
dfs_Dec9_3<-list(L153Dec9W3,L154Dec9W3,L156Dec9W3,L161Dec9W3,L162Dec9W3,L165Dec9W3,L167Dec9W3)

drops<-c("Total.length","FPS","Subject","Comment","Status")

DropFunction<- function(x) {
  x<-x[ , !(names(x) %in% drops)]
  return(x)
}

Dec9_Waddle3 = ldply(dfs_Dec9_3,DropFunction)

names(Dec9_Waddle3)<-c("Time","Observer", "Behavior", "Start_Stop","ID")

detach(package:plyr)
```

##Combine Data to get TimeEl
```{r}
Dec9_StartTimes3<-subset(Dec9_Waddle3,Start_Stop== "START")
names(Dec9_StartTimes3)<- c("StartTime","Observer", "Behavior","Start","ID")
Dec9_StopTimes3<-subset(Dec9_Waddle3,Start_Stop=="STOP")
names(Dec9_StopTimes3)<-c("StopTime","Observer", "Behavior","Stop","ID")
```


```{r}
Dec9_WaddleTimes3<-cbind(Dec9_StartTimes3,Dec9_StopTimes3)
names(Dec9_WaddleTimes3)<-c("StartTime","Observer", "Behavior","Start","ID","StopTime","Obs.2", "Beh.2","Stop","ID.2")
drops_doubles<-c("Start","Obs.2", "Beh.2","Stop","ID.2")
Dec9_WaddleTimes3<-Dec9_WaddleTimes3[ , !(names(Dec9_WaddleTimes3) %in% drops_doubles)]
Dec9_WaddleTimes3<-mutate(Dec9_WaddleTimes3,TimeEl=StopTime-StartTime)
Dec9_WaddleTimes3<-mutate(Dec9_WaddleTimes3,Minutes=StartTime/60)
Dec9_WaddleTimes3<-mutate(Dec9_WaddleTimes3,Date=rep("Dec9"))
```

##Subset Data by ID to set acclimation and test periods

```{r}
library(dplyr)
L153Dec9_W3<-filter(Dec9_WaddleTimes3,ID=="L153")
L153Dec9_W3$Observer<-rep(NA)
L153Dec9_W3$Observer<-L153Dec9_W3$Observer[is.na(L153Dec9_W3$Observer)]<- "MjH"

L154Dec9_W3<-filter(Dec9_WaddleTimes3,ID=="L154")
L154Dec9_W3$Observer<-rep(NA)
L154Dec9_W3$Observer<-L154Dec9_W3$Observer[is.na(L154Dec9_W3$Observer)]<- "MjH"

L156Dec9_W3<-filter(Dec9_WaddleTimes3,ID=="L156")
L156Dec9_W3$Observer<-rep(NA)
L156Dec9_W3$Observer<-L156Dec9_W3$Observer[is.na(L156Dec9_W3$Observer)]<- "NiI"

#L159Dec9_W3<-filter(Dec9_WaddleTimes3,ID=="L159")
L161Dec9_W3<-filter(Dec9_WaddleTimes3,ID=="L161")
L161Dec9_W3$Observer<-rep(NA)
L161Dec9_W3$Observer<-L161Dec9_W3$Observer[is.na(L161Dec9_W3$Observer)]<- "NaB"

L162Dec9_W3<-filter(Dec9_WaddleTimes,ID=="L162")
L162Dec9_W3$Observer<-rep(NA)
L162Dec9_W3$Observer<-L162Dec9_W3$Observer[is.na(L162Dec9_W3$Observer)]<- "NaB"


L165Dec9_W3<-filter(Dec9_WaddleTimes3,ID=="L165")
L165Dec9_W3$Observer<-rep(NA)
L165Dec9_W3$Observer<-L165Dec9_W3$Observer[is.na(L165Dec9_W3$Observer)]<- "KaG"


L167Dec9_W3<-filter(Dec9_WaddleTimes3,ID=="L167")
L167Dec9_W3$Observer<-rep(NA)
L167Dec9_W3$Observer<-L167Dec9_W3$Observer[is.na(L167Dec9_W3$Observer)]<- "MjH"

```

```{r}
library(dplyr)
L153Dec9_W3_accl<-filter(L153Dec9_W3,Minutes<=21)
L153Dec9_W3_test<-filter(L153Dec9_W3,Minutes>21 & Minutes<=41)
L154Dec9_W3_accl<-filter(L154Dec9_W3,Minutes<=22)
L154Dec9_W3_test<-filter(L154Dec9_W3,Minutes>22 & Minutes<=42)
L156Dec9_W3_accl<-filter(L156Dec9_W3,Minutes<=21)
L156Dec9_W3_test<-filter(L156Dec9_W3,Minutes>21 & Minutes<=41)
#L159Dec9_W3_accl<-filter(L159Dec9_W3,Minutes<=21)
#L159Dec9_W3_test<-filter(L159Dec9_W3,Minutes>21 & Minutes<=41)
L161Dec9_W3_accl<-filter(L161Dec9_W3,Minutes<=21)
L161Dec9_W3_test<-filter(L161Dec9_W3,Minutes>21 & Minutes<=41)
L162Dec9_W3_accl<-filter(L162Dec9_W3,Minutes<=21)
L162Dec9_W3_test<-filter(L162Dec9_W3,Minutes>21)
L165Dec9_W3_accl<-filter(L165Dec9_W3,Minutes<=22 & Minutes<=42)
L165Dec9_W3_test<-filter(L165Dec9_W3,Minutes>22 & Minutes<=41)
L167Dec9_W3_accl<-filter(L167Dec9_W3,Minutes<=21)
L167Dec9_W3_test<-filter(L167Dec9_W3,Minutes>21 & Minutes<=41)
```

Dec9 W3 Five mins

```{r}
library(dplyr)
L153Dec9_W3_test5<-filter(L153Dec9_W3,Minutes>21 & Minutes<=26)

L154Dec9_W3_test5<-filter(L154Dec9_W3,Minutes>22 & Minutes<=27)

L156Dec9_W3_test5<-filter(L156Dec9_W3,Minutes>21 & Minutes<=26)

#L159Dec9_W3_test5<-filter(L159Dec9_W3,Minutes>21 & Minutes<=26)

L161Dec9_W3_test5<-filter(L161Dec9_W3,Minutes>21 & Minutes<=26)

L162Dec9_W3_test5<-filter(L162Dec9_W3,Minutes>21 & Minutes<=26)

L165Dec9_W3_test5<-filter(L165Dec9_W3,Minutes>22 & Minutes<=27)

L167Dec9_W3_test5<-filter(L167Dec9_W3,Minutes>21 & Minutes<=26)

Dec9_W3_test5_BH<-rbind(L153Dec9_W3_test5,L156Dec9_W3_test5,L161Dec9_W3_test5,L165Dec9_W3_test5)
Dec9_W3_test5_BH<-mutate(Dec9_W3_test5_BH,FieldType=rep("conditioned"))
Dec9_W3_test5_NB<-rbind(L154Dec9_W3_test5,L162Dec9_W3_test5,L167Dec9_W3_test5)
Dec9_W3_test5_NB<-mutate(Dec9_W3_test5_NB,FieldType=rep("control"))
Dec9_W3_test5<-rbind(Dec9_W3_test5_BH,Dec9_W3_test5_NB)

Dec9_W3_test5<-Dec9_W3_test5 %>% group_by(ID,Observer,FieldType) %>% summarise(TotalTimeEl=sum(TimeEl)) 
```

Dec9 W3 ten mins

```{r}
library(dplyr)
L153Dec9_W3_test10<-filter(L153Dec9_W3,Minutes>21 & Minutes<=31)

L154Dec9_W3_test10<-filter(L154Dec9_W3,Minutes>22 & Minutes<=32)

L156Dec9_W3_test10<-filter(L156Dec9_W3,Minutes>21 & Minutes<=31)

#L159Dec9_W3_test5<-filter(L159Dec9_W3,Minutes>21 & Minutes<=26)

L161Dec9_W3_test10<-filter(L161Dec9_W3,Minutes>21 & Minutes<=31)

L162Dec9_W3_test10<-filter(L162Dec9_W3,Minutes>21 & Minutes<=31)

L165Dec9_W3_test10<-filter(L165Dec9_W3,Minutes>22 & Minutes<=32)

L167Dec9_W3_test10<-filter(L167Dec9_W3,Minutes>21 & Minutes<=31)

Dec9_W3_test10_BH<-rbind(L153Dec9_W3_test10,L156Dec9_W3_test10,L161Dec9_W3_test10,L165Dec9_W3_test10)
Dec9_W3_test10_BH<-mutate(Dec9_W3_test10_BH,FieldType=rep("conditioned"))
Dec9_W3_test10_NB<-rbind(L154Dec9_W3_test10,L162Dec9_W3_test10,L167Dec9_W3_test10)
Dec9_W3_test10_NB<-mutate(Dec9_W3_test10_NB,FieldType=rep("control"))
Dec9_W3_test10<-rbind(Dec9_W3_test10_BH,Dec9_W3_test10_NB)

Dec9_W3_test10<-Dec9_W3_test10 %>% group_by(ID,Observer,FieldType) %>% summarise(TotalTimeEl=sum(TimeEl)) 
```


```{r}
Dec9_W3_accl_BH<-rbind(L153Dec9_W3_accl,L156Dec9_W3_accl,L161Dec9_W3_accl,L165Dec9_W3_accl)
Dec9_W3_test_BH<-rbind(L153Dec9_W3_test,L156Dec9_W3_test,L161Dec9_W3_test,L165Dec9_W3_test)
library(dplyr)
Dec9_W3_accl_BH<-mutate(Dec9_W3_accl_BH,Field=rep("BH"))
Dec9_W3_accl_BH<-mutate(Dec9_W3_accl_BH,TimePer=rep("accl"))
Dec9_W3_accl_BH<-mutate(Dec9_W3_accl_BH,FieldType=rep("conditioned"))
Dec9_W3_test_BH<-mutate(Dec9_W3_test_BH,Field=rep("BH"))
Dec9_W3_test_BH<-mutate(Dec9_W3_test_BH,TimePer=rep("test"))
Dec9_W3_test_BH<-mutate(Dec9_W3_test_BH,FieldType=rep("conditioned"))
```

```{r}
Dec9_W3_accl_NB<-rbind(L154Dec9_W3_accl,L162Dec9_W3_accl,L167Dec9_W3_accl)
Dec9_W3_test_NB<-rbind(L154Dec9_W3_test,L162Dec9_W3_accl,L167Dec9_W3_test)
library(dplyr)
Dec9_W3_accl_NB<-mutate(Dec9_W3_accl_NB,Field=rep("NB"))
Dec9_W3_accl_NB<-mutate(Dec9_W3_accl_NB,TimePer=rep("accl"))
Dec9_W3_accl_NB<-mutate(Dec9_W3_accl_NB,FieldType=rep("control"))
Dec9_W3_test_NB<-mutate(Dec9_W3_test_NB,Field=rep("NB"))
Dec9_W3_test_NB<-mutate(Dec9_W3_test_NB,TimePer=rep("test"))
Dec9_W3_test_NB<-mutate(Dec9_W3_test_NB,FieldType=rep("control"))
```

##Master Data Sets 
```{r}
Dec9_W3<-rbind(Dec9_W3_accl_BH,Dec9_W3_accl_NB,Dec9_W3_test_BH,Dec9_W3_test_NB)
Dec9_W3<-mutate(Dec9_W3,Date=rep("Dec9"))
Dec9_W3_BH<-rbind(Dec9_W3_accl_BH,Dec9_W3_test_BH)
Dec9_W3_NB<-rbind(Dec9_W3_accl_NB,Dec9_W3_test_NB)
```

```{r}
library(dplyr)
Dec9_W3<-Dec9_W3 %>% group_by(ID,TimePer,Observer,Field,FieldType,Date) %>% summarise(TotalTimeEl=sum(TimeEl))
Dec9_W3_test<-filter(Dec9_W3,TimePer=="test")
```


##########################################################################

#December 10
```{r}
L155Dec10W<-read.csv("L155_Dec10_Waddle.csv")
L157Dec10W<-read.csv("L157_Dec10_Waddle.csv")
L158Dec10W<-read.csv("L158_Dec10_Waddle.csv")
L160Dec10W<-read.csv("L160_Dec10_Waddle5.csv",skip=15,header=T)
L163Dec10W<-read.csv("L163_Dec10_Waddle.csv")
L164Dec10W<-read.csv("L164_Dec10_Waddle.csv")
L166Dec10W<-read.csv("L166_Dec10_Waddle.csv")
L168Dec10W<-read.csv("L168_Dec10_Waddle.csv")
```

```{r}
L155Dec10W$ID<-rep(NA)
L155Dec10W$ID<-L155Dec10W$ID[is.na(L155Dec10W$ID)]<- "L155"
L157Dec10W$ID<-rep(NA)
L157Dec10W$ID<-L157Dec10W$ID[is.na(L157Dec10W$ID)]<- "L157"
L158Dec10W$ID<-rep(NA)
L158Dec10W$ID<-L158Dec10W$ID[is.na(L158Dec10W$ID)]<- "L158"
L160Dec10W$ID<-rep(NA)
L160Dec10W$ID<-L160Dec10W$ID[is.na(L160Dec10W$ID)]<- "L160"
L163Dec10W$ID<-rep(NA)
L163Dec10W$ID<-L163Dec10W$ID[is.na(L163Dec10W$ID)]<- "L163"
L164Dec10W$ID<-rep(NA)
L164Dec10W$ID<-L164Dec10W$ID[is.na(L164Dec10W$ID)]<- "L164"
L166Dec10W$ID<-rep(NA)
L166Dec10W$ID<-L166Dec10W$ID[is.na(L166Dec10W$ID)]<- "L166"
L168Dec10W$ID<-rep(NA)
L168Dec10W$ID<-L168Dec10W$ID[is.na(L168Dec10W$ID)]<- "L168"
```

```{r}
library(plyr)
dfs_Dec10<-list(L155Dec10W,L157Dec10W,L158Dec10W,L160Dec10W,L163Dec10W,L164Dec10W,L166Dec10W,L168Dec10W)

drops<-c("Total.length","FPS","Subject","Comment","Status")

DropFunction<- function(x) {
  x<-x[ , !(names(x) %in% drops)]
  return(x)
}

Dec10_Waddle = ldply(dfs_Dec10,DropFunction)

names(Dec10_Waddle)<-c("Time","Observer", "Behavior", "Start_Stop","ID")

detach(package:plyr)
```

```{r}
Dec10_StartTimes<-subset(Dec10_Waddle,Start_Stop== "START")
names(Dec10_StartTimes)<- c("StartTime","Observer", "Behavior","Start","ID")
Dec10_StopTimes<-subset(Dec10_Waddle,Start_Stop=="STOP")
names(Dec10_StopTimes)<-c("StopTime","Observer", "Behavior","Stop","ID")
Dec10_WaddleTimes<-cbind(Dec10_StartTimes,Dec10_StopTimes)
```

```{r}
names(Dec10_WaddleTimes)<-c("StartTime","Observer", "Behavior","Start","ID","StopTime","Obs.2", "Beh.2","Stop","ID.2")
drops_doubles<-c("Start","Obs.2", "Beh.2","Stop","ID.2")
Dec10_WaddleTimes<-Dec10_WaddleTimes[ , !(names(Dec10_WaddleTimes) %in% drops_doubles)]
Dec10_WaddleTimes<-mutate(Dec10_WaddleTimes,TimeEl=StopTime-StartTime)
Dec10_WaddleTimes<-mutate(Dec10_WaddleTimes,Minutes=StartTime/60)
```

##Subset Data by ID to set acclimation and test periods

```{r}
library(dplyr)
L155Dec10_W1<-filter(Dec10_WaddleTimes,ID=="L155")
L155Dec10_W1$Observer<-rep(NA)
L155Dec10_W1$Observer<-L155Dec10_W1$Observer[is.na(L155Dec10_W1$Observer)]<- "KaG"

L157Dec10_W1<-filter(Dec10_WaddleTimes,ID=="L157")
L157Dec10_W1$Observer<-rep(NA)
L157Dec10_W1$Observer<-L157Dec10_W1$Observer[is.na(L157Dec10_W1$Observer)]<- "KaG"

L158Dec10_W1<-filter(Dec10_WaddleTimes,ID=="L158")
L158Dec10_W1$Observer<-rep(NA)
L158Dec10_W1$Observer<-L158Dec10_W1$Observer[is.na(L158Dec10_W1$Observer)]<- "NaB"

L160Dec10_W1<-filter(Dec10_WaddleTimes,ID=="L160")
L160Dec10_W1$Observer<-rep(NA)
L160Dec10_W1$Observer<-L160Dec10_W1$Observer[is.na(L160Dec10_W1$Observer)]<- "AnJ"

L163Dec10_W1<-filter(Dec10_WaddleTimes,ID=="L163")
L163Dec10_W1$Observer<-rep(NA)
L163Dec10_W1$Observer<-L163Dec10_W1$Observer[is.na(L163Dec10_W1$Observer)]<- "MjH"

L164Dec10_W1<-filter(Dec10_WaddleTimes,ID=="L164")
L164Dec10_W1$Observer<-rep(NA)
L164Dec10_W1$Observer<-L164Dec10_W1$Observer[is.na(L164Dec10_W1$Observer)]<- "KaG"

L166Dec10_W1<-filter(Dec10_WaddleTimes,ID=="L166")
L166Dec10_W1$Observer<-rep(NA)
L166Dec10_W1$Observer<-L166Dec10_W1$Observer[is.na(L166Dec10_W1$Observer)]<- "NaB"

L168Dec10_W1<-filter(Dec10_WaddleTimes,ID=="L168")
L168Dec10_W1$Observer<-rep(NA)
L168Dec10_W1$Observer<-L168Dec10_W1$Observer[is.na(L168Dec10_W1$Observer)]<- "AnJ"

```

```{r}
library(dplyr)
L155Dec10_W1_accl<-filter(L155Dec10_W1,Minutes<=21)
L155Dec10_W1_test<-filter(L155Dec10_W1,Minutes>21 & Minutes<=41)
L157Dec10_W1_accl<-filter(L157Dec10_W1,Minutes<=21)
L157Dec10_W1_test<-filter(L157Dec10_W1,Minutes>21 & Minutes<=41)
L158Dec10_W1_accl<-filter(L158Dec10_W1,Minutes<=22)
L158Dec10_W1_test<-filter(L158Dec10_W1,Minutes>22 & Minutes<=42)
L160Dec10_W1_accl<-filter(L160Dec10_W1,Minutes<=20)
L160Dec10_W1_test<-filter(L160Dec10_W1,Minutes>20 & Minutes<=40)
L163Dec10_W1_accl<-filter(L163Dec10_W1,Minutes<=21)
L163Dec10_W1_test<-filter(L163Dec10_W1,Minutes>21 & Minutes<=41)
L164Dec10_W1_accl<-filter(L164Dec10_W1,Minutes<=22)
L164Dec10_W1_test<-filter(L164Dec10_W1,Minutes>22 & Minutes<=42)
L166Dec10_W1_accl<-filter(L166Dec10_W1,Minutes<=23)
L166Dec10_W1_test<-filter(L166Dec10_W1,Minutes>23 & Minutes<=43)
L168Dec10_W1_accl<-filter(L168Dec10_W1,Minutes<=24)
L168Dec10_W1_test<-filter(L168Dec10_W1,Minutes>24 & Minutes<=44)
```

Dec10 W five min test

```{r}
library(dplyr)
L155Dec10_W1_test5<-filter(L155Dec10_W1,Minutes>21 & Minutes<=26)

L157Dec10_W1_test5<-filter(L157Dec10_W1,Minutes>21 & Minutes<=26)

L158Dec10_W1_test5<-filter(L158Dec10_W1,Minutes>22 & Minutes<=27)

L160Dec10_W1_test5<-filter(L160Dec10_W1,Minutes>20 & Minutes<=25)

L163Dec10_W1_test5<-filter(L163Dec10_W1,Minutes>21 & Minutes<=26)

L164Dec10_W1_test5<-filter(L164Dec10_W1,Minutes>22 & Minutes<=27)

L166Dec10_W1_test5<-filter(L166Dec10_W1,Minutes>23 & Minutes<=28)

L168Dec10_W1_test5<-filter(L168Dec10_W1,Minutes>24 & Minutes<=29)

Dec10_W1_test5_BH<-rbind(L157Dec10_W1_test5,L160Dec10_W1_test5,L164Dec10_W1_test5,L168Dec10_W1_test5)
Dec10_W1_test5_BH<-mutate(Dec10_W1_test5_BH,FieldType=rep("control"))
Dec10_W1_test5_NB<-rbind(L155Dec10_W1_test5,L158Dec10_W1_test5,L163Dec10_W1_test5,L166Dec10_W1_test5)
Dec10_W1_test5_NB<-mutate(Dec10_W1_test5_NB,FieldType=rep("conditioned"))
Dec10_W1_test5<-rbind(Dec10_W1_test5_BH,Dec10_W1_test5_NB)

Dec10_W1_test5<-Dec10_W1_test5 %>% group_by(ID,Observer,FieldType) %>% summarise(TotalTimeEl=sum(TimeEl)) 
```

Dec10 Wten min test

```{r}
library(dplyr)
L155Dec10_W1_test10<-filter(L155Dec10_W1,Minutes>21 & Minutes<=31)

L157Dec10_W1_test10<-filter(L157Dec10_W1,Minutes>21 & Minutes<=31)

L158Dec10_W1_test10<-filter(L158Dec10_W1,Minutes>22 & Minutes<=32)

L160Dec10_W1_test10<-filter(L160Dec10_W1,Minutes>20 & Minutes<=30)

L163Dec10_W1_test10<-filter(L163Dec10_W1,Minutes>21 & Minutes<=31)

L164Dec10_W1_test10<-filter(L164Dec10_W1,Minutes>22 & Minutes<=32)

L166Dec10_W1_test10<-filter(L166Dec10_W1,Minutes>23 & Minutes<=33)

L168Dec10_W1_test10<-filter(L168Dec10_W1,Minutes>24 & Minutes<=34)

Dec10_W1_test10_BH<-rbind(L157Dec10_W1_test10,L160Dec10_W1_test10,L164Dec10_W1_test10,L168Dec10_W1_test10)
Dec10_W1_test10_BH<-mutate(Dec10_W1_test10_BH,FieldType=rep("control"))
Dec10_W1_test10_NB<-rbind(L155Dec10_W1_test10,L158Dec10_W1_test10,L163Dec10_W1_test10,L166Dec10_W1_test10)
Dec10_W1_test10_NB<-mutate(Dec10_W1_test10_NB,FieldType=rep("conditioned"))
Dec10_W1_test10<-rbind(Dec10_W1_test10_BH,Dec10_W1_test10_NB)

Dec10_W1_test10<-Dec10_W1_test10 %>% group_by(ID,Observer,FieldType) %>% summarise(TotalTimeEl=sum(TimeEl)) 
```

```{r}
Dec10_W1_accl_BH<-rbind(L157Dec10_W1_accl,L160Dec10_W1_accl,L164Dec10_W1_accl,L168Dec10_W1_accl)
Dec10_W1_test_BH<-rbind(L157Dec10_W1_test,L160Dec10_W1_test,L164Dec10_W1_test,L168Dec10_W1_test)
library(dplyr)
Dec10_W1_accl_BH<-mutate(Dec10_W1_accl_BH,Field=rep("BH"))
Dec10_W1_accl_BH<-mutate(Dec10_W1_accl_BH,TimePer=rep("accl"))
Dec10_W1_accl_BH<-mutate(Dec10_W1_accl_BH,FieldType=rep("control"))
Dec10_W1_test_BH<-mutate(Dec10_W1_test_BH,Field=rep("BH"))
Dec10_W1_test_BH<-mutate(Dec10_W1_test_BH,TimePer=rep("test"))
Dec10_W1_test_BH<-mutate(Dec10_W1_test_BH,FieldType=rep("control"))
```

```{r}
Dec10_W1_accl_NB<-rbind(L155Dec10_W1_accl,L158Dec10_W1_accl,L163Dec10_W1_accl,L166Dec10_W1_accl)
Dec10_W1_test_NB<-rbind(L155Dec10_W1_test,L158Dec10_W1_test,L163Dec10_W1_test,L166Dec10_W1_test)
library(dplyr)
Dec10_W1_accl_NB<-mutate(Dec10_W1_accl_NB,Field=rep("NB"))
Dec10_W1_accl_NB<-mutate(Dec10_W1_accl_NB,TimePer=rep("accl"))
Dec10_W1_accl_NB<-mutate(Dec10_W1_accl_NB,FieldType=rep("conditioned"))
Dec10_W1_test_NB<-mutate(Dec10_W1_test_NB,Field=rep("NB"))
Dec10_W1_test_NB<-mutate(Dec10_W1_test_NB,TimePer=rep("test"))
Dec10_W1_test_NB<-mutate(Dec10_W1_test_NB,FieldType=rep("conditioned"))
```

##Master Data Sets 
```{r}
Dec10_W1<-rbind(Dec10_W1_accl_BH,Dec10_W1_accl_NB,Dec10_W1_test_BH,Dec10_W1_test_NB)
Dec10_W1<-mutate(Dec10_W1,Date=rep("Dec10"))
Dec10_W1_BH<-rbind(Dec10_W1_accl_BH,Dec10_W1_test_BH)
Dec10_W1_NB<-rbind(Dec10_W1_accl_NB,Dec10_W1_test_NB)
```

```{r}
library(dplyr)
Dec10_W1<-Dec10_W1 %>% group_by(ID,TimePer,Observer,Field,FieldType,Date) %>% summarise(TotalTimeEl=sum(TimeEl))
Dec10_W1_test<-filter(Dec10_W1,TimePer=="test")
```

##T-tests ---- Significant
```{r}
t.test(TimeEl~TimePer,data=Dec10_W1_BH)
t.test(TimeEl~TimePer,data=Dec10_W1_NB)
t.test(TotalTimeEl~Field,data=Dec10_W1_test)
wilcox.test(TotalTimeEl~Field,data=Dec10_W1_test)
```


#Dec10 Second Analysis

```{r}
L155Dec10W2<-read.csv("L155_Dec10_Waddle2.csv")
L157Dec10W2<-read.csv("L157_Dec10_Waddle2.csv")
L158Dec10W2<-read.csv("L158_Dec10_Waddle2.csv")
L160Dec10W2<-read.csv("L160_Dec10_Waddle2.csv")
L163Dec10W2<-read.csv("L163_Dec10_Waddle2.csv")
L164Dec10W2<-read.csv("L164_Dec10_Waddle4.csv",skip=15,header=T)
L166Dec10W2<-read.csv("L166_Dec10_Waddle2.csv")
L168Dec10W2<-read.csv("L168_Dec10_Waddle2.csv")
```

```{r}
L155Dec10W2$ID<-rep(NA)
L155Dec10W2$ID<-L155Dec10W2$ID[is.na(L155Dec10W2$ID)]<- "L155"
L157Dec10W2$ID<-rep(NA)
L157Dec10W2$ID<-L157Dec10W2$ID[is.na(L157Dec10W2$ID)]<- "L157"
L158Dec10W2$ID<-rep(NA)
L158Dec10W2$ID<-L158Dec10W2$ID[is.na(L158Dec10W2$ID)]<- "L158"
L160Dec10W2$ID<-rep(NA)
L160Dec10W2$ID<-L160Dec10W2$ID[is.na(L160Dec10W2$ID)]<- "L160"
L163Dec10W2$ID<-rep(NA)
L163Dec10W2$ID<-L163Dec10W2$ID[is.na(L163Dec10W2$ID)]<- "L163"
L164Dec10W2$ID<-rep(NA)
L164Dec10W2$ID<-L164Dec10W2$ID[is.na(L164Dec10W2$ID)]<- "L164"
L166Dec10W2$ID<-rep(NA)
L166Dec10W2$ID<-L166Dec10W2$ID[is.na(L166Dec10W2$ID)]<- "L166"
L168Dec10W2$ID<-rep(NA)
L168Dec10W2$ID<-L168Dec10W2$ID[is.na(L168Dec10W2$ID)]<- "L168"
```

```{r}
library(plyr)
dfs_Dec10_2<-list(L155Dec10W2,L157Dec10W2,L158Dec10W2,L160Dec10W2,L163Dec10W2,L164Dec10W2,L166Dec10W2,L168Dec10W2)

drops<-c("Total.length","FPS","Subject","Comment","Status")

DropFunction<- function(x) {
  x<-x[ , !(names(x) %in% drops)]
  return(x)
}

Dec10_Waddle2 = ldply(dfs_Dec10_2,DropFunction)

names(Dec10_Waddle2)<-c("Time","Observer", "Behavior", "Start_Stop","ID")

detach(package:plyr)
```

```{r}
Dec10_StartTimes2<-subset(Dec10_Waddle2,Start_Stop== "START")
names(Dec10_StartTimes2)<- c("StartTime","Observer", "Behavior","Start","ID")
Dec10_StopTimes2<-subset(Dec10_Waddle2,Start_Stop=="STOP")
names(Dec10_StopTimes2)<-c("StopTime","Observer", "Behavior","Stop","ID")
Dec10_WaddleTimes2<-cbind(Dec10_StartTimes2,Dec10_StopTimes2)
```

```{r}
names(Dec10_WaddleTimes2)<-c("StartTime","Observer", "Behavior","Start","ID","StopTime","Obs.2", "Beh.2","Stop","ID.2")
drops_doubles<-c("Start","Obs.2", "Beh.2","Stop","ID.2")
Dec10_WaddleTimes2<-Dec10_WaddleTimes2[ , !(names(Dec10_WaddleTimes2) %in% drops_doubles)]
Dec10_WaddleTimes2<-mutate(Dec10_WaddleTimes2,TimeEl=StopTime-StartTime)
Dec10_WaddleTimes2<-mutate(Dec10_WaddleTimes2,Minutes=StartTime/60)
```

##Subset Data by ID to set acclimation and test periods

```{r}
library(dplyr)
L155Dec10_W2<-filter(Dec10_WaddleTimes2,ID=="L155")
L155Dec10_W2$Observer<-rep(NA)
L155Dec10_W2$Observer<-L155Dec10_W2$Observer[is.na(L155Dec10_W2$Observer)]<- "MjH"

L157Dec10_W2<-filter(Dec10_WaddleTimes2,ID=="L157")
L157Dec10_W2$Observer<-rep(NA)
L157Dec10_W2$Observer<-L157Dec10_W2$Observer[is.na(L157Dec10_W2$Observer)]<- "NaB"

L158Dec10_W2<-filter(Dec10_WaddleTimes2,ID=="L158")
L158Dec10_W2$Observer<-rep(NA)
L158Dec10_W2$Observer<-L158Dec10_W2$Observer[is.na(L158Dec10_W2$Observer)]<- "MjH"

L160Dec10_W2<-filter(Dec10_WaddleTimes2,ID=="L160")
L160Dec10_W2$Observer<-rep(NA)
L160Dec10_W2$Observer<-L160Dec10_W2$Observer[is.na(L160Dec10_W2$Observer)]<- "NaB"

L163Dec10_W2<-filter(Dec10_WaddleTimes2,ID=="L163")
L163Dec10_W2$Observer<-rep(NA)
L163Dec10_W2$Observer<-L163Dec10_W2$Observer[is.na(L163Dec10_W2$Observer)]<- "KaG"

L164Dec10_W2<-filter(Dec10_WaddleTimes2,ID=="L164")
L164Dec10_W2$Observer<-rep(NA)
L164Dec10_W2$Observer<-L164Dec10_W2$Observer[is.na(L164Dec10_W2$Observer)]<- "MjH"

L166Dec10_W2<-filter(Dec10_WaddleTimes2,ID=="L166")
L166Dec10_W2$Observer<-rep(NA)
L166Dec10_W2$Observer<-L166Dec10_W2$Observer[is.na(L166Dec10_W2$Observer)]<- "KaG"

L168Dec10_W2<-filter(Dec10_WaddleTimes2,ID=="L168")
L168Dec10_W2$Observer<-rep(NA)
L168Dec10_W2$Observer<-L168Dec10_W2$Observer[is.na(L168Dec10_W2$Observer)]<- "KaG"

```

```{r}
library(dplyr)
L155Dec10_W2_accl<-filter(L155Dec10_W2,Minutes<=21)
L155Dec10_W2_test<-filter(L155Dec10_W2,Minutes>21 & Minutes<=41)
L157Dec10_W2_accl<-filter(L157Dec10_W2,Minutes<=21)
L157Dec10_W2_test<-filter(L157Dec10_W2,Minutes>21 & Minutes<=41)
L158Dec10_W2_accl<-filter(L158Dec10_W2,Minutes<=22)
L158Dec10_W2_test<-filter(L158Dec10_W2,Minutes>22 & Minutes <=42)
L160Dec10_W2_accl<-filter(L160Dec10_W2,Minutes<=20)
L160Dec10_W2_test<-filter(L160Dec10_W2,Minutes>20 & Minutes <=40)
L163Dec10_W2_accl<-filter(L163Dec10_W2,Minutes<=21)
L163Dec10_W2_test<-filter(L163Dec10_W2,Minutes>21 & Minutes<=41)
L164Dec10_W2_accl<-filter(L164Dec10_W2,Minutes<=22)
L164Dec10_W2_test<-filter(L164Dec10_W2,Minutes>22 & Minutes<=42)
L166Dec10_W2_accl<-filter(L166Dec10_W2,Minutes<=23)
L166Dec10_W2_test<-filter(L166Dec10_W2,Minutes>23 & Minutes<=43)
L168Dec10_W2_accl<-filter(L168Dec10_W2,Minutes<=24)
L168Dec10_W2_test<-filter(L168Dec10_W2,Minutes>24 & Minutes<=44)
```

Dec10 W2 Test 5 mins 
```{r}
library(dplyr)
L155Dec10_W2_test5<-filter(L155Dec10_W2,Minutes>21 & Minutes<=26)

L157Dec10_W2_test5<-filter(L157Dec10_W2,Minutes>21 & Minutes<=26)

L158Dec10_W2_test5<-filter(L158Dec10_W2,Minutes>22 & Minutes<=27)

L160Dec10_W2_test5<-filter(L160Dec10_W2,Minutes>20 & Minutes<=25)

L163Dec10_W2_test5<-filter(L163Dec10_W2,Minutes>21 & Minutes<=26)

L164Dec10_W2_test5<-filter(L164Dec10_W2,Minutes>22 & Minutes<=27)

L166Dec10_W2_test5<-filter(L166Dec10_W2,Minutes>23 & Minutes<=28)

L168Dec10_W2_test5<-filter(L168Dec10_W2,Minutes>24 & Minutes<=29)

Dec10_W2_test5_BH<-rbind(L157Dec10_W2_test5,L160Dec10_W2_test5,L164Dec10_W2_test5,L168Dec10_W2_test5)
Dec10_W2_test5_BH<-mutate(Dec10_W2_test5_BH,FieldType=rep("control"))
Dec10_W2_test5_NB<-rbind(L155Dec10_W2_test5,L158Dec10_W2_test5,L163Dec10_W2_test5,L166Dec10_W2_test5)
Dec10_W2_test5_NB<-mutate(Dec10_W2_test5_NB,FieldType=rep("conditioned"))
Dec10_W2_test5<-rbind(Dec10_W2_test5_BH,Dec10_W2_test5_NB)

Dec10_W2_test5<-Dec10_W2_test5 %>% group_by(ID,Observer,FieldType) %>% summarise(TotalTimeEl=sum(TimeEl)) 
```


Dec10 W2 Test 10 mins 
```{r}
library(dplyr)
L155Dec10_W2_test10<-filter(L155Dec10_W2,Minutes>21 & Minutes<=31)

L157Dec10_W2_test10<-filter(L157Dec10_W2,Minutes>21 & Minutes<=31)

L158Dec10_W2_test10<-filter(L158Dec10_W2,Minutes>22 & Minutes<=32)

L160Dec10_W2_test10<-filter(L160Dec10_W2,Minutes>20 & Minutes<=30)

L163Dec10_W2_test10<-filter(L163Dec10_W2,Minutes>21 & Minutes<=31)

L164Dec10_W2_test10<-filter(L164Dec10_W2,Minutes>22 & Minutes<=32)

L166Dec10_W2_test10<-filter(L166Dec10_W2,Minutes>23 & Minutes<=33)

L168Dec10_W2_test10<-filter(L168Dec10_W2,Minutes>24 & Minutes<=34)

Dec10_W2_test10_BH<-rbind(L157Dec10_W2_test10,L160Dec10_W2_test10,L164Dec10_W2_test10,L168Dec10_W2_test10)
Dec10_W2_test10_BH<-mutate(Dec10_W2_test10_BH,FieldType=rep("control"))
Dec10_W2_test10_NB<-rbind(L155Dec10_W2_test10,L158Dec10_W2_test10,L163Dec10_W2_test10,L166Dec10_W2_test10)
Dec10_W2_test10_NB<-mutate(Dec10_W2_test10_NB,FieldType=rep("conditioned"))
Dec10_W2_test10<-rbind(Dec10_W2_test10_BH,Dec10_W2_test10_NB)

Dec10_W2_test10<-Dec10_W2_test10 %>% group_by(ID,Observer,FieldType) %>% summarise(TotalTimeEl=sum(TimeEl)) 
```


```{r}
Dec10_W2_accl_BH<-rbind(L157Dec10_W2_accl,L160Dec10_W2_accl,L164Dec10_W2_accl,L168Dec10_W2_accl)
Dec10_W2_test_BH<-rbind(L157Dec10_W2_test,L160Dec10_W2_test,L164Dec10_W2_test,L168Dec10_W2_test)
library(dplyr)
Dec10_W2_accl_BH<-mutate(Dec10_W2_accl_BH,Field=rep("BH"))
Dec10_W2_accl_BH<-mutate(Dec10_W2_accl_BH,TimePer=rep("accl"))
Dec10_W2_accl_BH<-mutate(Dec10_W2_accl_BH,FieldType=rep("control"))
Dec10_W2_test_BH<-mutate(Dec10_W2_test_BH,Field=rep("BH"))
Dec10_W2_test_BH<-mutate(Dec10_W2_test_BH,TimePer=rep("test"))
Dec10_W2_test_BH<-mutate(Dec10_W2_test_BH,FieldType=rep("control"))
```

```{r}
Dec10_W2_accl_NB<-rbind(L155Dec10_W2_accl,L158Dec10_W2_accl,L163Dec10_W2_accl,L166Dec10_W2_accl)
Dec10_W2_test_NB<-rbind(L155Dec10_W2_test,L158Dec10_W2_test,L163Dec10_W2_test,L166Dec10_W2_test)
library(dplyr)
Dec10_W2_accl_NB<-mutate(Dec10_W2_accl_NB,Field=rep("NB"))
Dec10_W2_accl_NB<-mutate(Dec10_W2_accl_NB,TimePer=rep("accl"))
Dec10_W2_accl_NB<-mutate(Dec10_W2_accl_NB,FieldType=rep("conditioned"))
Dec10_W2_test_NB<-mutate(Dec10_W2_test_NB,Field=rep("NB"))
Dec10_W2_test_NB<-mutate(Dec10_W2_test_NB,TimePer=rep("test"))
Dec10_W2_test_NB<-mutate(Dec10_W2_test_NB,FieldType=rep("conditioned"))
```

##Master Data Sets 
```{r}
Dec10_W2<-rbind(Dec10_W2_accl_BH,Dec10_W2_accl_NB,Dec10_W2_test_BH,Dec10_W2_test_NB)
Dec10_W2<-mutate(Dec10_W2,Date=rep("Dec10"))
Dec10_W2_BH<-rbind(Dec10_W2_accl_BH,Dec10_W2_test_BH)
Dec10_W2_NB<-rbind(Dec10_W2_accl_NB,Dec10_W2_test_NB)
```

```{r}
library(dplyr)
Dec10_W2<-Dec10_W2 %>% group_by(ID,TimePer,Observer,Field,FieldType,Date) %>% summarise(TotalTimeEl=sum(TimeEl))
Dec10_W2_test<-filter(Dec10_W2,TimePer=="test")
```


#December10 Third Analysis

```{r}
L155Dec10_W3<-read.csv("L155_Dec10_Waddle3.csv",skip=15,header=T)
L157Dec10_W3<-read.csv("L157_Dec10_Waddle3.csv",skip=15,header=T)
L158Dec10_W3<-read.csv("L158_Dec10_Waddle3.csv",skip=15,header=T)
L160Dec10_W3<-read.csv("L160_Dec10_Waddle4.csv",skip=15,header=T)
L163Dec10_W3<-read.csv("L163_Dec10_Waddle3.csv",skip=15,header=T)
L164Dec10_W3<-read.csv("L164_Dec10_Waddle3.csv",skip=15,header=T)
L166Dec10_W3<-read.csv("L166_Dec10_Waddle3.csv",skip=15,header=T)
L168Dec10_W3<-read.csv("L168_Dec10_Waddle3.csv",skip=15,header=T)
```

```{r}
L155Dec10_W3$ID<-rep(NA)
L155Dec10_W3$ID<-L155Dec10_W3$ID[is.na(L155Dec10_W3$ID)]<- "L155"
L157Dec10_W3$ID<-rep(NA)
L157Dec10_W3$ID<-L157Dec10_W3$ID[is.na(L157Dec10_W3$ID)]<- "L157"
L158Dec10_W3$ID<-rep(NA)
L158Dec10_W3$ID<-L158Dec10_W3$ID[is.na(L158Dec10_W3$ID)]<- "L158"
L160Dec10_W3$ID<-rep(NA)
L160Dec10_W3$ID<-L160Dec10_W3$ID[is.na(L160Dec10_W3$ID)]<- "L160"
L163Dec10_W3$ID<-rep(NA)
L163Dec10_W3$ID<-L163Dec10_W3$ID[is.na(L163Dec10_W3$ID)]<- "L163"
L164Dec10_W3$ID<-rep(NA)
L164Dec10_W3$ID<-L164Dec10_W3$ID[is.na(L164Dec10_W3$ID)]<- "L164"
L166Dec10_W3$ID<-rep(NA)
L166Dec10_W3$ID<-L166Dec10_W3$ID[is.na(L166Dec10_W3$ID)]<- "L166"
L168Dec10_W3$ID<-rep(NA)
L168Dec10_W3$ID<-L168Dec10_W3$ID[is.na(L168Dec10_W3$ID)]<- "L168"
```

```{r}
library(plyr)
dfs_Dec10_3<-list(L155Dec10_W3,L157Dec10_W3,L158Dec10_W3,L160Dec10_W3,L164Dec10_W3,L168Dec10_W3,L163Dec10_W3,L166Dec10_W3)#L163,L166

drops<-c("Total.length","FPS","Subject","Comment","Status")

DropFunction<- function(x) {
  x<-x[ , !(names(x) %in% drops)]
  return(x)
}

Dec10_Waddle3 = ldply(dfs_Dec10_3,DropFunction)

names(Dec10_Waddle3)<-c("Time","Observer", "Behavior", "Start_Stop","ID")

detach(package:plyr)
```

```{r}
Dec10_StartTimes3<-subset(Dec10_Waddle3,Start_Stop== "START")
names(Dec10_StartTimes3)<- c("StartTime","Observer", "Behavior","Start","ID")
Dec10_StopTimes3<-subset(Dec10_Waddle3,Start_Stop=="STOP")
names(Dec10_StopTimes3)<-c("StopTime","Observer", "Behavior","Stop","ID")
Dec10_WaddleTimes3<-cbind(Dec10_StartTimes3,Dec10_StopTimes3)
```

```{r}
names(Dec10_WaddleTimes3)<-c("StartTime","Observer", "Behavior","Start","ID","StopTime","Obs.2", "Beh.2","Stop","ID.2")
drops_doubles<-c("Start","Obs.2", "Beh.2","Stop","ID.2")
Dec10_WaddleTimes3<-Dec10_WaddleTimes3[ , !(names(Dec10_WaddleTimes3) %in% drops_doubles)]
Dec10_WaddleTimes3<-mutate(Dec10_WaddleTimes3,TimeEl=StopTime-StartTime)
Dec10_WaddleTimes3<-mutate(Dec10_WaddleTimes3,Minutes=StartTime/60)
```

##Subset Data by ID to set acclimation and test periods

```{r}
library(dplyr)
L155Dec10_W3<-filter(Dec10_WaddleTimes3,ID=="L155")
L155Dec10_W3$Observer<-rep(NA)
L155Dec10_W3$Observer<-L155Dec10_W3$Observer[is.na(L155Dec10_W3$Observer)]<- "AnJ"

L157Dec10_W3<-filter(Dec10_WaddleTimes3,ID=="L157")
L157Dec10_W3$Observer<-rep(NA)
L157Dec10_W3$Observer<-L157Dec10_W3$Observer[is.na(L157Dec10_W3$Observer)]<- "EmT"

L158Dec10_W3<-filter(Dec10_WaddleTimes3,ID=="L158")
L158Dec10_W3$Observer<-rep(NA)
L158Dec10_W3$Observer<-L158Dec10_W3$Observer[is.na(L158Dec10_W3$Observer)]<- "KaG"

L160Dec10_W3<-filter(Dec10_WaddleTimes3,ID=="L160")
L160Dec10_W3$Observer<-rep(NA)
L160Dec10_W3$Observer<-L160Dec10_W3$Observer[is.na(L160Dec10_W3$Observer)]<- "KaG"

L163Dec10_W3<-filter(Dec10_WaddleTimes3,ID=="L163")
L163Dec10_W3$Observer<-rep(NA)
L163Dec10_W3$Observer<-L163Dec10_W3$Observer[is.na(L163Dec10_W3$Observer)]<- "AnJ"

L164Dec10_W3<-filter(Dec10_WaddleTimes3,ID=="L164")
L164Dec10_W3$Observer<-rep(NA)
L164Dec10_W3$Observer<-L164Dec10_W3$Observer[is.na(L164Dec10_W3$Observer)]<- "EmT"

L166Dec10_W3<-filter(Dec10_WaddleTimes3,ID=="L166")
L166Dec10_W3$Observer<-rep(NA)
L166Dec10_W3$Observer<-L166Dec10_W3$Observer[is.na(L166Dec10_W3$Observer)]<- "NiI"

L168Dec10_W3<-filter(Dec10_WaddleTimes3,ID=="L168")
L168Dec10_W3$Observer<-rep(NA)
L168Dec10_W3$Observer<-L168Dec10_W3$Observer[is.na(L168Dec10_W3$Observer)]<- "NaB"

```

```{r}
library(dplyr)
L155Dec10_W3_accl<-filter(L155Dec10_W3,Minutes<=21)
L155Dec10_W3_test<-filter(L155Dec10_W3,Minutes>21 & Minutes<=41)
L157Dec10_W3_accl<-filter(L157Dec10_W3,Minutes<=21)
L157Dec10_W3_test<-filter(L157Dec10_W3,Minutes>21 & Minutes<=41)
L158Dec10_W3_accl<-filter(L158Dec10_W3,Minutes<=22)
L158Dec10_W3_test<-filter(L158Dec10_W3,Minutes>22 & Minutes <=42)
L160Dec10_W3_accl<-filter(L160Dec10_W3,Minutes<=20)
L160Dec10_W3_test<-filter(L160Dec10_W3,Minutes>20 & Minutes <=40)
L163Dec10_W3_accl<-filter(L163Dec10_W3,Minutes<=21)
L163Dec10_W3_test<-filter(L163Dec10_W3,Minutes>21 & Minutes<=41)
L164Dec10_W3_accl<-filter(L164Dec10_W3,Minutes<=22)
L164Dec10_W3_test<-filter(L164Dec10_W3,Minutes>22 & Minutes<=42)
L166Dec10_W3_accl<-filter(L166Dec10_W3,Minutes<=23)
L166Dec10_W3_test<-filter(L166Dec10_W3,Minutes>23 & Minutes<=43)
L168Dec10_W3_accl<-filter(L168Dec10_W3,Minutes<=24)
L168Dec10_W3_test<-filter(L168Dec10_W3,Minutes>24 & Minutes<=44)
```

Dec10 W3 test 5 mins

```{r}
library(dplyr)
L155Dec10_W3_test5<-filter(L155Dec10_W3,Minutes>21 & Minutes<=26)

L157Dec10_W3_test5<-filter(L157Dec10_W3,Minutes>21 & Minutes<=26)

L158Dec10_W3_test5<-filter(L158Dec10_W3,Minutes>22 & Minutes<=27)

L160Dec10_W3_test5<-filter(L160Dec10_W3,Minutes>20 & Minutes<=25)

L163Dec10_W3_test5<-filter(L163Dec10_W3,Minutes>21 & Minutes<=26)

L164Dec10_W3_test5<-filter(L164Dec10_W3,Minutes>22 & Minutes<=27)

L166Dec10_W3_test5<-filter(L166Dec10_W3,Minutes>23 & Minutes<=28)

L168Dec10_W3_test5<-filter(L168Dec10_W3,Minutes>24 & Minutes<=29)

Dec10_W3_test5_BH<-rbind(L157Dec10_W3_test5,L160Dec10_W3_test5,L164Dec10_W3_test5,L168Dec10_W3_test5)
Dec10_W3_test5_BH<-mutate(Dec10_W3_test5_BH,FieldType=rep("control"))
Dec10_W3_test5_NB<-rbind(L155Dec10_W3_test5,L158Dec10_W3_test5,L163Dec10_W3_test5,L166Dec10_W3_test5)
Dec10_W3_test5_NB<-mutate(Dec10_W3_test5_NB,FieldType=rep("conditioned"))
Dec10_W3_test5<-rbind(Dec10_W3_test5_BH,Dec10_W3_test5_NB)

Dec10_W3_test5<-Dec10_W3_test5 %>% group_by(ID,Observer,FieldType) %>% summarise(TotalTimeEl=sum(TimeEl)) 
```

Dec10 W3 test 10 mins

```{r}
library(dplyr)
L155Dec10_W3_test10<-filter(L155Dec10_W3,Minutes>21 & Minutes<=31)

L157Dec10_W3_test10<-filter(L157Dec10_W3,Minutes>21 & Minutes<=31)

L158Dec10_W3_test10<-filter(L158Dec10_W3,Minutes>22 & Minutes<=32)

L160Dec10_W3_test10<-filter(L160Dec10_W3,Minutes>20 & Minutes<=30)

L163Dec10_W3_test10<-filter(L163Dec10_W3,Minutes>21 & Minutes<=31)

L164Dec10_W3_test10<-filter(L164Dec10_W3,Minutes>22 & Minutes<=32)

L166Dec10_W3_test10<-filter(L166Dec10_W3,Minutes>23 & Minutes<=33)

L168Dec10_W3_test10<-filter(L168Dec10_W3,Minutes>24 & Minutes<=34)

Dec10_W3_test10_BH<-rbind(L157Dec10_W3_test10,L160Dec10_W3_test10,L164Dec10_W3_test10,L168Dec10_W3_test10)
Dec10_W3_test10_BH<-mutate(Dec10_W3_test10_BH,FieldType=rep("control"))
Dec10_W3_test10_NB<-rbind(L155Dec10_W3_test10,L158Dec10_W3_test10,L163Dec10_W3_test10,L166Dec10_W3_test10)
Dec10_W3_test10_NB<-mutate(Dec10_W3_test10_NB,FieldType=rep("conditioned"))
Dec10_W3_test10<-rbind(Dec10_W3_test10_BH,Dec10_W3_test5_NB)

Dec10_W3_test10<-Dec10_W3_test10 %>% group_by(ID,Observer,FieldType) %>% summarise(TotalTimeEl=sum(TimeEl)) 
```


```{r}
Dec10_W3_accl_BH<-rbind(L157Dec10_W3_accl,L160Dec10_W3_accl,L164Dec10_W3_accl,L168Dec10_W3_accl)
Dec10_W3_test_BH<-rbind(L157Dec10_W3_test,L160Dec10_W3_test,L164Dec10_W3_test,L168Dec10_W3_test)
library(dplyr)
Dec10_W3_accl_BH<-mutate(Dec10_W3_accl_BH,Field=rep("BH"))
Dec10_W3_accl_BH<-mutate(Dec10_W3_accl_BH,TimePer=rep("accl"))
Dec10_W3_accl_BH<-mutate(Dec10_W3_accl_BH,FieldType=rep("control"))
Dec10_W3_test_BH<-mutate(Dec10_W3_test_BH,Field=rep("BH"))
Dec10_W3_test_BH<-mutate(Dec10_W3_test_BH,TimePer=rep("test"))
Dec10_W3_test_BH<-mutate(Dec10_W3_test_BH,FieldType=rep("control"))
```

```{r}
Dec10_W3_accl_NB<-rbind(L155Dec10_W3_accl,L158Dec10_W3_accl,L163Dec10_W3_accl,L166Dec10_W3_accl)
Dec10_W3_test_NB<-rbind(L155Dec10_W3_test,L158Dec10_W3_test,L163Dec10_W3_test,L166Dec10_W3_test)
library(dplyr)
Dec10_W3_accl_NB<-mutate(Dec10_W3_accl_NB,Field=rep("NB"))
Dec10_W3_accl_NB<-mutate(Dec10_W3_accl_NB,TimePer=rep("accl"))
Dec10_W3_accl_NB<-mutate(Dec10_W3_accl_NB,FieldType=rep("conditioned"))
Dec10_W3_test_NB<-mutate(Dec10_W3_test_NB,Field=rep("NB"))
Dec10_W3_test_NB<-mutate(Dec10_W3_test_NB,TimePer=rep("test"))
Dec10_W3_test_NB<-mutate(Dec10_W3_test_NB,FieldType=rep("conditioned"))
```

##Master Data Sets 
```{r}
Dec10_W3<-rbind(Dec10_W3_accl_BH,Dec10_W3_accl_NB,Dec10_W3_test_BH,Dec10_W3_test_NB)
Dec10_W3<-mutate(Dec10_W3,Date=rep("Dec10"))
Dec10_W3_BH<-rbind(Dec10_W3_accl_BH,Dec10_W3_test_BH)
Dec10_W3_NB<-rbind(Dec10_W3_accl_NB,Dec10_W3_test_NB)
```

```{r}
library(dplyr)
Dec10_W3<-Dec10_W3 %>% group_by(ID,TimePer,Observer,Field,FieldType,Date) %>% summarise(TotalTimeEl=sum(TimeEl))
Dec10_W3_test<-filter(Dec10_W3,TimePer=="test")
```


################################################################

#December 11
```{r}
L153Dec11W<-read.csv("L153_Dec11_Waddle.csv")
L154Dec11W<-read.csv("L154_Dec11_Waddle.csv")
L156Dec11W<-read.csv("L156_Dec11_Waddle.csv")
L159Dec11W<-read.csv("L159_Dec11_Waddle.csv")
L161Dec11W<-read.csv("L161_Dec11_Waddle.csv")
L162Dec11W<-read.csv("L162_Dec11_Waddle.csv")
L165Dec11W<-read.csv("L165_Dec11_Waddle.csv")
L167Dec11W<-read.csv("L167_Dec11_Waddle.csv")
```


```{r}
L153Dec11W$ID<-rep(NA)
L153Dec11W$ID<-L153Dec11W$ID[is.na(L153Dec11W$ID)]<- "L153"
L154Dec11W$ID<-rep(NA)
L154Dec11W$ID<-L154Dec11W$ID[is.na(L154Dec11W$ID)]<- "L154"
L156Dec11W$ID<-rep(NA)
L156Dec11W$ID<-L156Dec11W$ID[is.na(L156Dec11W$ID)]<- "L156"
L159Dec11W$ID<-rep(NA)
L159Dec11W$ID<-L159Dec11W$ID[is.na(L159Dec11W$ID)]<- "L159"
L161Dec11W$ID<-rep(NA)
L161Dec11W$ID<-L161Dec11W$ID[is.na(L161Dec11W$ID)]<- "L161"
L162Dec11W$ID<-rep(NA)
L162Dec11W$ID<-L162Dec11W$ID[is.na(L162Dec11W$ID)]<- "L162"
L165Dec11W$ID<-rep(NA)
L165Dec11W$ID<-L165Dec11W$ID[is.na(L165Dec11W$ID)]<- "L165"
L167Dec11W$ID<-rep(NA)
L167Dec11W$ID<-L167Dec11W$ID[is.na(L167Dec11W$ID)]<- "L167"
```

```{r}
library(plyr)
dfs_Dec11<-list(L153Dec11W,L154Dec11W,L156Dec11W,L159Dec11W,L161Dec11W,L162Dec11W,L165Dec11W,L167Dec11W)

drops<-c("Total.length","FPS","Subject","Comment","Status")

DropFunction<- function(x) {
  x<-x[ , !(names(x) %in% drops)]
  return(x)
}

Dec11_Waddle = ldply(dfs_Dec11,DropFunction)

names(Dec11_Waddle)<-c("Time","Observer", "Behavior", "Start_Stop","ID")

detach(package:plyr)
```



```{r}
Dec11_StartTimes<-subset(Dec11_Waddle,Start_Stop== "START")
names(Dec11_StartTimes)<- c("StartTime","Observer", "Behavior","Start","ID")
Dec11_StopTimes<-subset(Dec11_Waddle,Start_Stop=="STOP")
names(Dec11_StopTimes)<-c("StopTime","Observer", "Behavior","Stop","ID")
Dec11_WaddleTimes<-cbind(Dec11_StartTimes,Dec11_StopTimes)
```

```{r}
names(Dec11_WaddleTimes)<-c("StartTime","Observer", "Behavior","Start","ID","StopTime","Obs.2", "Beh.2","Stop","ID.2")
drops_doubles<-c("Start","Obs.2", "Beh.2","Stop","ID.2")
Dec11_WaddleTimes<-Dec11_WaddleTimes[ , !(names(Dec11_WaddleTimes) %in% drops_doubles)]
Dec11_WaddleTimes<-mutate(Dec11_WaddleTimes,TimeEl=StopTime-StartTime)
Dec11_WaddleTimes<-mutate(Dec11_WaddleTimes,Minutes=StartTime/60)
```

##Subset Data by ID to set acclimation and test periods 

```{r}
library(dplyr)
L153Dec11_W1<-filter(Dec11_WaddleTimes,ID=="L153")
L153Dec11_W1$Observer<-rep(NA)
L153Dec11_W1$Observer<-L153Dec11_W1$Observer[is.na(L153Dec11_W1$Observer)]<- "KaG"

L154Dec11_W1<-filter(Dec11_WaddleTimes,ID=="L154")
L154Dec11_W1$Observer<-rep(NA)
L154Dec11_W1$Observer<-L154Dec11_W1$Observer[is.na(L154Dec11_W1$Observer)]<- "KaG"

L156Dec11_W1<-filter(Dec11_WaddleTimes,ID=="L156")
L156Dec11_W1$Observer<-rep(NA)
L156Dec11_W1$Observer<-L156Dec11_W1$Observer[is.na(L156Dec11_W1$Observer)]<- "AnJ"

L159Dec11_W1<-filter(Dec11_WaddleTimes,ID=="L159")
L159Dec11_W1$Observer<-rep(NA)
L159Dec11_W1$Observer<-L159Dec11_W1$Observer[is.na(L159Dec11_W1$Observer)]<- "AnJ"


L161Dec11_W1<-filter(Dec11_WaddleTimes,ID=="L161")
L161Dec11_W1$Observer<-rep(NA)
L161Dec11_W1$Observer<-L161Dec11_W1$Observer[is.na(L161Dec11_W1$Observer)]<- "NaB"

L162Dec11_W1<-filter(Dec11_WaddleTimes,ID=="L162")
L162Dec11_W1$Observer<-rep(NA)
L162Dec11_W1$Observer<-L162Dec11_W1$Observer[is.na(L162Dec11_W1$Observer)]<- "NaB"

L165Dec11_W1<-filter(Dec11_WaddleTimes,ID=="L165")
L165Dec11_W1$Observer<-rep(NA)
L165Dec11_W1$Observer<-L165Dec11_W1$Observer[is.na(L165Dec11_W1$Observer)]<- "NiI"

L167Dec11_W1<-filter(Dec11_WaddleTimes,ID=="L167")
L167Dec11_W1$Observer<-rep(NA)
L167Dec11_W1$Observer<-L167Dec11_W1$Observer[is.na(L167Dec11_W1$Observer)]<- "NiI"
```

```{r}
library(dplyr)
L153Dec11_W1_accl<-filter(L153Dec11_W1,Minutes<=22)
L153Dec11_W1_test<-filter(L153Dec11_W1,Minutes>22 & Minutes<=42)
L154Dec11_W1_accl<-filter(L154Dec11_W1,Minutes<=22)
L154Dec11_W1_test<-filter(L154Dec11_W1,Minutes>22 & Minutes<=42)
L156Dec11_W1_accl<-filter(L156Dec11_W1,Minutes<=21)
L156Dec11_W1_test<-filter(L156Dec11_W1,Minutes>21 & Minutes<=41)
L159Dec11_W1_accl<-filter(L159Dec11_W1,Minutes<=23)
L159Dec11_W1_test<-filter(L159Dec11_W1,Minutes>23 & Minutes<=43)
L161Dec11_W1_accl<-filter(L161Dec11_W1,Minutes<=23)
L161Dec11_W1_test<-filter(L161Dec11_W1,Minutes>23 & Minutes<=43)
L162Dec11_W1_accl<-filter(L162Dec11_W1,Minutes<=24)
L162Dec11_W1_test<-filter(L162Dec11_W1,Minutes>24 & Minutes<=44)
L165Dec11_W1_accl<-filter(L165Dec11_W1,Minutes<=21)
L165Dec11_W1_test<-filter(L165Dec11_W1,Minutes>21 & Minutes<=41)
L167Dec11_W1_accl<-filter(L167Dec11_W1,Minutes<=21)
L167Dec11_W1_test<-filter(L167Dec11_W1,Minutes>21 & Minutes<=41)
```

Dec11 W1 test 5 mins

```{r}
library(dplyr)
L153Dec11_W1_test5<-filter(L153Dec11_W1,Minutes>22 & Minutes<=27)

L154Dec11_W1_test5<-filter(L154Dec11_W1,Minutes>22 & Minutes<=27)

L156Dec11_W1_test5<-filter(L156Dec11_W1,Minutes>21 & Minutes<=26)

L159Dec11_W1_test5<-filter(L159Dec11_W1,Minutes>23 & Minutes<=28)

L161Dec11_W1_test5<-filter(L161Dec11_W1,Minutes>23 & Minutes<=28)

L162Dec11_W1_test5<-filter(L162Dec11_W1,Minutes>24 & Minutes<=29)

L165Dec11_W1_test5<-filter(L165Dec11_W1,Minutes>21 & Minutes<=26)

L167Dec11_W1_test5<-filter(L167Dec11_W1,Minutes>21 & Minutes<=26)

Dec11_W1_test5_BH<-rbind(L154Dec11_W1_test5,L159Dec11_W1_test5,L162Dec11_W1_test5,L167Dec11_W1_test5)
Dec11_W1_test5_BH<-mutate(Dec11_W1_test5_BH,FieldType=rep("conditioned"))
Dec11_W1_test5_NB<-rbind(L153Dec11_W1_test5,L156Dec11_W1_test5,L161Dec11_W1_test5,L165Dec11_W1_test5)
Dec11_W1_test5_NB<-mutate(Dec11_W1_test5_NB,FieldType=rep("control"))
Dec11_W1_test5<-rbind(Dec11_W1_test5_BH,Dec11_W1_test5_NB)

Dec11_W1_test5<-Dec11_W1_test5 %>% group_by(ID,Observer,FieldType) %>% summarise(TotalTimeEl=sum(TimeEl)) 
```


Dec11 W1 test 10 mins

```{r}
library(dplyr)
L153Dec11_W1_test10<-filter(L153Dec11_W1,Minutes>22 & Minutes<=27)

L154Dec11_W1_test10<-filter(L154Dec11_W1,Minutes>22 & Minutes<=27)

L156Dec11_W1_test10<-filter(L156Dec11_W1,Minutes>21 & Minutes<=26)

L159Dec11_W1_test10<-filter(L159Dec11_W1,Minutes>23 & Minutes<=28)

L161Dec11_W1_test10<-filter(L161Dec11_W1,Minutes>23 & Minutes<=28)

L162Dec11_W1_test10<-filter(L162Dec11_W1,Minutes>24 & Minutes<=29)

L165Dec11_W1_test10<-filter(L165Dec11_W1,Minutes>21 & Minutes<=26)

L167Dec11_W1_test10<-filter(L167Dec11_W1,Minutes>21 & Minutes<=26)

Dec11_W1_test10_BH<-rbind(L154Dec11_W1_test10,L159Dec11_W1_test10,L162Dec11_W1_test10,L167Dec11_W1_test10)
Dec11_W1_test10_BH<-mutate(Dec11_W1_test10_BH,FieldType=rep("conditioned"))
Dec11_W1_test10_NB<-rbind(L153Dec11_W1_test10,L156Dec11_W1_test10,L161Dec11_W1_test10,L165Dec11_W1_test10)
Dec11_W1_test10_NB<-mutate(Dec11_W1_test10_NB,FieldType=rep("control"))
Dec11_W1_test10<-rbind(Dec11_W1_test10_BH,Dec11_W1_test10_NB)

Dec11_W1_test5<-Dec11_W1_test5 %>% group_by(ID,Observer,FieldType) %>% summarise(TotalTimeEl=sum(TimeEl)) 
```

```{r}
Dec11_W1_accl_BH<-rbind(L154Dec11_W1_accl,L159Dec11_W1_accl,L162Dec11_W1_accl,L167Dec11_W1_accl)
Dec11_W1_test_BH<-rbind(L154Dec11_W1_test,L159Dec11_W1_test,L162Dec11_W1_test,L167Dec11_W1_test)
library(dplyr)
Dec11_W1_accl_BH<-mutate(Dec11_W1_accl_BH,Field=rep("BH"))
Dec11_W1_accl_BH<-mutate(Dec11_W1_accl_BH,TimePer=rep("accl"))
Dec11_W1_accl_BH<-mutate(Dec11_W1_accl_BH,FieldType=rep("conditioned"))
Dec11_W1_test_BH<-mutate(Dec11_W1_test_BH,Field=rep("BH"))
Dec11_W1_test_BH<-mutate(Dec11_W1_test_BH,TimePer=rep("test"))
Dec11_W1_test_BH<-mutate(Dec11_W1_test_BH,FieldType=rep("conditioned"))
```

```{r}
Dec11_W1_accl_NB<-rbind(L153Dec11_W1_accl,L156Dec11_W1_accl,L161Dec11_W1_accl,L165Dec11_W1_accl)
Dec11_W1_test_NB<-rbind(L153Dec11_W1_test,L156Dec11_W1_test,L161Dec11_W1_test,L165Dec11_W1_test)
library(dplyr)
Dec11_W1_accl_NB<-mutate(Dec11_W1_accl_NB,Field=rep("NB"))
Dec11_W1_accl_NB<-mutate(Dec11_W1_accl_NB,TimePer=rep("accl"))
Dec11_W1_accl_NB<-mutate(Dec11_W1_accl_NB,FieldType=rep("control"))
Dec11_W1_test_NB<-mutate(Dec11_W1_test_NB,Field=rep("NB"))
Dec11_W1_test_NB<-mutate(Dec11_W1_test_NB,TimePer=rep("test"))
Dec11_W1_test_NB<-mutate(Dec11_W1_test_NB,FieldType=rep("control"))
```

##Master Data Sets
```{r}
Dec11_W1<-rbind(Dec11_W1_accl_BH,Dec11_W1_accl_NB,Dec11_W1_test_BH,Dec11_W1_test_NB)
Dec11_W1<-mutate(Dec11_W1,Date=rep("Dec11"))
Dec11_W1_BH<-rbind(Dec11_W1_accl_BH,Dec11_W1_test_BH)
Dec11_W1_NB<-rbind(Dec11_W1_accl_NB,Dec11_W1_test_NB)
```

```{r}
library(dplyr)
Dec11_W1<-Dec11_W1 %>% group_by(ID,TimePer,Observer,Field,FieldType,Date) %>% summarise(TotalTimeEl=sum(TimeEl))
Dec11_W1_test<-filter(Dec11_W1,TimePer=="test")
```



#December 11 Analysis 2###############################

```{r}
L153Dec11W2<-read.csv("L153_Dec11_Waddle2.csv")
L154Dec11W2<-read.csv("L154_Dec11_Waddle2.csv")
L156Dec11W2<-read.csv("L156_Dec11_Waddle2.csv")
L159Dec11W2<-read.csv("L159_Dec11_Waddle2.csv")
L161Dec11W2<-read.csv("L161_Dec11_Waddle2.csv")
L162Dec11W2<-read.csv("L162_Dec11_Waddle2.csv")
L165Dec11W2<-read.csv("L165_Dec11_Waddle2.csv")
L167Dec11W2<-read.csv("L167_Dec11_Waddle2.csv")
```

```{r}
L153Dec11W2$ID<-rep(NA)
L153Dec11W2$ID<-L153Dec11W2$ID[is.na(L153Dec11W2$ID)]<- "L153"
L154Dec11W2$ID<-rep(NA)
L154Dec11W2$ID<-L154Dec11W2$ID[is.na(L154Dec11W2$ID)]<- "L154"
L156Dec11W2$ID<-rep(NA)
L156Dec11W2$ID<-L156Dec11W2$ID[is.na(L156Dec11W2$ID)]<- "L156"
L159Dec11W2$ID<-rep(NA)
L159Dec11W2$ID<-L159Dec11W2$ID[is.na(L159Dec11W2$ID)]<- "L159"
L161Dec11W2$ID<-rep(NA)
L161Dec11W2$ID<-L161Dec11W2$ID[is.na(L161Dec11W2$ID)]<- "L161"
L162Dec11W2$ID<-rep(NA)
L162Dec11W2$ID<-L162Dec11W2$ID[is.na(L162Dec11W2$ID)]<- "L162"
L165Dec11W2$ID<-rep(NA)
L165Dec11W2$ID<-L165Dec11W2$ID[is.na(L165Dec11W2$ID)]<- "L165"
L167Dec11W2$ID<-rep(NA)
L167Dec11W2$ID<-L167Dec11W2$ID[is.na(L167Dec11W2$ID)]<- "L167"
```

```{r}
library(plyr)
dfs_Dec11_2<-list(L153Dec11W2,L154Dec11W2,L156Dec11W2,L159Dec11W2,L161Dec11W2,L162Dec11W2,L165Dec11W2,L167Dec11W2)

drops<-c("Total.length","FPS","Subject","Comment","Status")

DropFunction<- function(x) {
  x<-x[ , !(names(x) %in% drops)]
  return(x)
}

Dec11_Waddle2 = ldply(dfs_Dec11_2,DropFunction)

names(Dec11_Waddle2)<-c("Time","Observer", "Behavior", "Start_Stop","ID")

detach(package:plyr)
```

```{r}
Dec11_StartTimes2<-subset(Dec11_Waddle2,Start_Stop== "START")
names(Dec11_StartTimes2)<- c("StartTime","Observer", "Behavior","Start","ID")
Dec11_StopTimes2<-subset(Dec11_Waddle2,Start_Stop=="STOP")
names(Dec11_StopTimes2)<-c("StopTime","Observer", "Behavior","Stop","ID")
Dec11_WaddleTimes2<-cbind(Dec11_StartTimes2,Dec11_StopTimes2)
```

```{r}
names(Dec11_WaddleTimes2)<-c("StartTime","Observer", "Behavior","Start","ID","StopTime","Obs.2", "Beh.2","Stop","ID.2")
drops_doubles<-c("Start","Obs.2", "Beh.2","Stop","ID.2")
Dec11_WaddleTimes2<-Dec11_WaddleTimes2[ , !(names(Dec11_WaddleTimes2) %in% drops_doubles)]
Dec11_WaddleTimes2<-mutate(Dec11_WaddleTimes2,TimeEl=StopTime-StartTime)
Dec11_WaddleTimes2<-mutate(Dec11_WaddleTimes2,Minutes=StartTime/60)
```

##Subset Data by ID to set acclimation and test periods 

```{r}
library(dplyr)
L153Dec11_W2<-filter(Dec11_WaddleTimes2,ID=="L153")
L153Dec11_W2$Observer<-rep(NA)
L153Dec11_W2$Observer<-L153Dec11_W2$Observer[is.na(L153Dec11_W2$Observer)]<- "AnJ"

L154Dec11_W2<-filter(Dec11_WaddleTimes2,ID=="L154")
L154Dec11_W2$Observer<-rep(NA)
L154Dec11_W2$Observer<-L154Dec11_W2$Observer[is.na(L154Dec11_W2$Observer)]<- "AnJ"

L156Dec11_W2<-filter(Dec11_WaddleTimes2,ID=="L156")
L156Dec11_W2$Observer<-rep(NA)
L156Dec11_W2$Observer<-L156Dec11_W2$Observer[is.na(L156Dec11_W2$Observer)]<- "NaB"

L159Dec11_W2<-filter(Dec11_WaddleTimes2,ID=="L159")
L159Dec11_W2$Observer<-rep(NA)
L159Dec11_W2$Observer<-L159Dec11_W2$Observer[is.na(L159Dec11_W2$Observer)]<- "NaB"

L161Dec11_W2<-filter(Dec11_WaddleTimes2,ID=="L161")
L161Dec11_W2$Observer<-rep(NA)
L161Dec11_W2$Observer<-L161Dec11_W2$Observer[is.na(L161Dec11_W2$Observer)]<- "AnJ"


L162Dec11_W2<-filter(Dec11_WaddleTimes2,ID=="L162")
L162Dec11_W2$Observer<-rep(NA)
L162Dec11_W2$Observer<-L162Dec11_W2$Observer[is.na(L162Dec11_W2$Observer)]<- "AnJ"

L165Dec11_W2<-filter(Dec11_WaddleTimes2,ID=="L165")
L165Dec11_W2$Observer<-rep(NA)
L165Dec11_W2$Observer<-L165Dec11_W2$Observer[is.na(L165Dec11_W2$Observer)]<- "NaB"

L167Dec11_W2<-filter(Dec11_WaddleTimes2,ID=="L167")
L167Dec11_W2$Observer<-rep(NA)
L167Dec11_W2$Observer<-L167Dec11_W2$Observer[is.na(L167Dec11_W2$Observer)]<- "KaG"

```

```{r}
library(dplyr)
L153Dec11_W2_accl<-filter(L153Dec11_W2,Minutes<=22)
L153Dec11_W2_test<-filter(L153Dec11_W2,Minutes>22 & Minutes<=42)
L154Dec11_W2_accl<-filter(L154Dec11_W2,Minutes<=22)
L154Dec11_W2_test<-filter(L154Dec11_W2,Minutes>22 & Minutes<=42)
L156Dec11_W2_accl<-filter(L156Dec11_W2,Minutes<=21)
L156Dec11_W2_test<-filter(L156Dec11_W2,Minutes>21 & Minutes<=41)
L159Dec11_W2_accl<-filter(L159Dec11_W2,Minutes<=23)
L159Dec11_W2_test<-filter(L159Dec11_W2,Minutes>23 & Minutes<=43)
L161Dec11_W2_accl<-filter(L161Dec11_W2,Minutes<=23)
L161Dec11_W2_test<-filter(L161Dec11_W2,Minutes>23 & Minutes<=43)
L162Dec11_W2_accl<-filter(L162Dec11_W2,Minutes<=24)
L162Dec11_W2_test<-filter(L162Dec11_W2,Minutes>24 & Minutes<=44)
L165Dec11_W2_accl<-filter(L165Dec11_W2,Minutes<=21)
L165Dec11_W2_test<-filter(L165Dec11_W2,Minutes>21 & Minutes<=41)
L167Dec11_W2_accl<-filter(L167Dec11_W2,Minutes<=21)
L167Dec11_W2_test<-filter(L167Dec11_W2,Minutes>21 & Minutes<=41)
```


Dec11 W2 test 5 mins

```{r}
library(dplyr)
L153Dec11_W2_test5<-filter(L153Dec11_W2,Minutes>22 & Minutes<=27)

L154Dec11_W2_test5<-filter(L154Dec11_W2,Minutes>22 & Minutes<=27)

L156Dec11_W2_test5<-filter(L156Dec11_W2,Minutes>21 & Minutes<=26)

L159Dec11_W2_test5<-filter(L159Dec11_W2,Minutes>23 & Minutes<=28)

L161Dec11_W2_test5<-filter(L161Dec11_W2,Minutes>23 & Minutes<=28)

L162Dec11_W2_test5<-filter(L162Dec11_W2,Minutes>24 & Minutes<=29)

L165Dec11_W2_test5<-filter(L165Dec11_W2,Minutes>21 & Minutes<=26)

L167Dec11_W2_test5<-filter(L167Dec11_W2,Minutes>21 & Minutes<=26)

Dec11_W2_test5_BH<-rbind(L154Dec11_W2_test5,L159Dec11_W2_test5,L162Dec11_W2_test5,L167Dec11_W2_test5)
Dec11_W2_test5_BH<-mutate(Dec11_W2_test5_BH,FieldType=rep("conditioned"))
Dec11_W2_test5_NB<-rbind(L153Dec11_W2_test5,L156Dec11_W2_test5,L161Dec11_W2_test5,L165Dec11_W2_test5)
Dec11_W2_test5_NB<-mutate(Dec11_W2_test5_NB,FieldType=rep("control"))
Dec11_W2_test5<-rbind(Dec11_W2_test5_BH,Dec11_W2_test5_NB)

Dec11_W2_test5<-Dec11_W2_test5 %>% group_by(ID,Observer,FieldType) %>% summarise(TotalTimeEl=sum(TimeEl)) 
```


```{r}
Dec11_W2_accl_BH<-rbind(L154Dec11_W2_accl,L159Dec11_W2_accl,L162Dec11_W2_accl,L167Dec11_W2_accl)
Dec11_W2_test_BH<-rbind(L154Dec11_W2_test,L159Dec11_W2_test,L162Dec11_W2_test,L167Dec11_W2_test)
library(dplyr)
Dec11_W2_accl_BH<-mutate(Dec11_W2_accl_BH,Field=rep("BH"))
Dec11_W2_accl_BH<-mutate(Dec11_W2_accl_BH,TimePer=rep("accl"))
Dec11_W2_accl_BH<-mutate(Dec11_W2_accl_BH,FieldType=rep("conditioned"))
Dec11_W2_test_BH<-mutate(Dec11_W2_test_BH,Field=rep("BH"))
Dec11_W2_test_BH<-mutate(Dec11_W2_test_BH,TimePer=rep("test"))
Dec11_W2_test_BH<-mutate(Dec11_W2_test_BH,FieldType=rep("conditioned"))
```

```{r}
Dec11_W2_accl_NB<-rbind(L153Dec11_W2_accl,L156Dec11_W2_accl,L161Dec11_W2_accl,L165Dec11_W2_accl)
Dec11_W2_test_NB<-rbind(L153Dec11_W2_test,L156Dec11_W2_test,L161Dec11_W2_test,L165Dec11_W2_test)
library(dplyr)
Dec11_W2_accl_NB<-mutate(Dec11_W2_accl_NB,Field=rep("NB"))
Dec11_W2_accl_NB<-mutate(Dec11_W2_accl_NB,TimePer=rep("accl"))
Dec11_W2_accl_NB<-mutate(Dec11_W2_accl_NB,FieldType=rep("control"))
Dec11_W2_test_NB<-mutate(Dec11_W2_test_NB,Field=rep("NB"))
Dec11_W2_test_NB<-mutate(Dec11_W2_test_NB,TimePer=rep("test"))
Dec11_W2_test_NB<-mutate(Dec11_W2_test_NB,FieldType=rep("control"))
```

##Master Data Sets  
```{r}
Dec11_W2<-rbind(Dec11_W2_accl_BH,Dec11_W2_accl_NB,Dec11_W2_test_BH,Dec11_W2_test_NB)
Dec11_W2<-mutate(Dec11_W2,Date=rep("Dec11"))
Dec11_W2_BH<-rbind(Dec11_W2_accl_BH,Dec11_W2_test_BH)
Dec11_W2_NB<-rbind(Dec11_W2_accl_NB,Dec11_W2_test_NB)
```

```{r}
library(dplyr)
Dec11_W2<-Dec11_W2 %>% group_by(ID,TimePer,Observer,Field,FieldType,Date) %>% summarise(TotalTimeEl=sum(TimeEl))
Dec11_W2_test<-filter(Dec11_W2,TimePer=="test")
```


#December 11 Third Analysis##############################


```{r}
L153Dec11W3<-read.csv("L153_Dec11_Waddle3.csv",skip=15,header=T)
L154Dec11W3<-read.csv("L154_Dec11_Waddle3.csv",skip=15,header=T)
#L156Dec11W3<-read.csv("L156_Dec11_Waddle3.csv",skip=15,header=T)
L159Dec11W3<-read.csv("L159_Dec11_Waddle3.csv",skip=15,header=T)
L161Dec11W3<-read.csv("L161_Dec11_Waddle3.csv",skip=15,header=T)
L162Dec11W3<-read.csv("L162_Dec11_Waddle3.csv",skip=15,header=T)
L165Dec11W3<-read.csv("L165_Dec11_Waddle3.csv",skip=15,header=T)
L167Dec11W3<-read.csv("L167_Dec11_Waddle3.csv",skip=15,header=T)
```

```{r}
L153Dec11W3$ID<-rep(NA)
L153Dec11W3$ID<-L153Dec11W3$ID[is.na(L153Dec11W3$ID)]<- "L153"
L154Dec11W3$ID<-rep(NA)
L154Dec11W3$ID<-L154Dec11W3$ID[is.na(L154Dec11W3$ID)]<- "L154"
#L156Dec11W3$ID<-rep(NA)
#L156Dec11W3$ID<-L156Dec11W3$ID[is.na(L156Dec11W3$ID)]<- "L156"
L159Dec11W3$ID<-rep(NA)
L159Dec11W3$ID<-L159Dec11W3$ID[is.na(L159Dec11W3$ID)]<- "L159"
L161Dec11W3$ID<-rep(NA)
L161Dec11W3$ID<-L161Dec11W3$ID[is.na(L161Dec11W3$ID)]<- "L161"
L162Dec11W3$ID<-rep(NA)
L162Dec11W3$ID<-L162Dec11W3$ID[is.na(L162Dec11W3$ID)]<- "L162"
L165Dec11W3$ID<-rep(NA)
L165Dec11W3$ID<-L165Dec11W3$ID[is.na(L165Dec11W3$ID)]<- "L165"
L167Dec11W3$ID<-rep(NA)
L167Dec11W3$ID<-L167Dec11W3$ID[is.na(L167Dec11W3$ID)]<- "L167"
```

```{r}
library(plyr)
dfs_Dec11_3<-list(L153Dec11W3,L154Dec11W3,L159Dec11W3,L161Dec11W3,L162Dec11W3,L167Dec11W3,L165Dec11W3) #L165

drops<-c("Total.length","FPS","Subject","Comment","Status")

DropFunction<- function(x) {
  x<-x[ , !(names(x) %in% drops)]
  return(x)
}

Dec11_Waddle3 = ldply(dfs_Dec11_3,DropFunction)

names(Dec11_Waddle3)<-c("Time","Observer", "Behavior", "Start_Stop","ID")

detach(package:plyr)
```

```{r}
Dec11_StartTimes3<-subset(Dec11_Waddle3,Start_Stop== "START")
names(Dec11_StartTimes3)<- c("StartTime","Observer", "Behavior","Start","ID")
Dec11_StopTimes3<-subset(Dec11_Waddle3,Start_Stop=="STOP")
names(Dec11_StopTimes3)<-c("StopTime","Observer", "Behavior","Stop","ID")
Dec11_WaddleTimes3<-cbind(Dec11_StartTimes3,Dec11_StopTimes3)
```

```{r}
names(Dec11_WaddleTimes3)<-c("StartTime","Observer", "Behavior","Start","ID","StopTime","Obs.2", "Beh.2","Stop","ID.2")
drops_doubles<-c("Start","Obs.2", "Beh.2","Stop","ID.2")
Dec11_WaddleTimes3<-Dec11_WaddleTimes3[ , !(names(Dec11_WaddleTimes3) %in% drops_doubles)]
Dec11_WaddleTimes3<-mutate(Dec11_WaddleTimes3,TimeEl=StopTime-StartTime)
Dec11_WaddleTimes3<-mutate(Dec11_WaddleTimes3,Minutes=StartTime/60)
```

##Subset Data by ID to set acclimation and test periods 

```{r}
library(dplyr)
L153Dec11_W3<-filter(Dec11_WaddleTimes3,ID=="L153")
L153Dec11_W3$Observer<-rep(NA)
L153Dec11_W3$Observer<-L153Dec11_W3$Observer[is.na(L153Dec11_W3$Observer)]<- "NaB"

L154Dec11_W3<-filter(Dec11_WaddleTimes3,ID=="L154")
L154Dec11_W3$Observer<-rep(NA)
L154Dec11_W3$Observer<-L154Dec11_W3$Observer[is.na(L154Dec11_W3$Observer)]<- "NaB"

#L156Dec11_W3<-filter(Dec11_WaddleTimes3,ID=="L156")
#L156Dec11_W3$Observer<-rep(NA)
#L156Dec11_W3$Observer<-L156Dec11_W3$Observer[is.na(L156Dec11_W3$Observer)]<- "NaB"

L159Dec11_W3<-filter(Dec11_WaddleTimes3,ID=="L159")
L159Dec11_W3$Observer<-rep(NA)
L159Dec11_W3$Observer<-L159Dec11_W3$Observer[is.na(L159Dec11_W3$Observer)]<- "EmT"

L161Dec11_W3<-filter(Dec11_WaddleTimes3,ID=="L161")
L161Dec11_W3$Observer<-rep(NA)
L161Dec11_W3$Observer<-L161Dec11_W3$Observer[is.na(L161Dec11_W3$Observer)]<- "NiI"


L162Dec11_W3<-filter(Dec11_WaddleTimes3,ID=="L162")
L162Dec11_W3$Observer<-rep(NA)
L162Dec11_W3$Observer<-L162Dec11_W3$Observer[is.na(L162Dec11_W3$Observer)]<- "NiI"

L165Dec11_W3<-filter(Dec11_WaddleTimes3,ID=="L165")
L165Dec11_W3$Observer<-rep(NA)
L165Dec11_W3$Observer<-L165Dec11_W3$Observer[is.na(L165Dec11_W3$Observer)]<- "KaG"

L167Dec11_W3<-filter(Dec11_WaddleTimes3,ID=="L167")
L167Dec11_W3$Observer<-rep(NA)
L167Dec11_W3$Observer<-L167Dec11_W3$Observer[is.na(L167Dec11_W3$Observer)]<- "MjH"

```

```{r}
library(dplyr)
L153Dec11_W3_accl<-filter(L153Dec11_W3,Minutes<=22)
L153Dec11_W3_test<-filter(L153Dec11_W3,Minutes>22 & Minutes<=42)
L154Dec11_W3_accl<-filter(L154Dec11_W3,Minutes<=22)
L154Dec11_W3_test<-filter(L154Dec11_W3,Minutes>22 & Minutes<=42)
#L156Dec11_W3_accl<-filter(L156Dec11_W3,Minutes<=21)
#L156Dec11_W3_test<-filter(L156Dec11_W3,Minutes>21 & Minutes<=41)
L159Dec11_W3_accl<-filter(L159Dec11_W3,Minutes<=23)
L159Dec11_W3_test<-filter(L159Dec11_W3,Minutes>23 & Minutes<=43)
L161Dec11_W3_accl<-filter(L161Dec11_W3,Minutes<=23)
L161Dec11_W3_test<-filter(L161Dec11_W3,Minutes>23 & Minutes<=43)
L162Dec11_W3_accl<-filter(L162Dec11_W3,Minutes<=24)
L162Dec11_W3_test<-filter(L162Dec11_W3,Minutes>24 & Minutes<=44)
L165Dec11_W3_accl<-filter(L165Dec11_W3,Minutes<=21)
L165Dec11_W3_test<-filter(L165Dec11_W3,Minutes>21 & Minutes<=41)
L167Dec11_W3_accl<-filter(L167Dec11_W3,Minutes<=21)
L167Dec11_W3_test<-filter(L167Dec11_W3,Minutes>21 & Minutes<=41)
```


Dec11 W3 test 5 mins

```{r}
library(dplyr)
L153Dec11_W3_test5<-filter(L153Dec11_W3,Minutes>22 & Minutes<=27)

L154Dec11_W3_test5<-filter(L154Dec11_W3,Minutes>22 & Minutes<=27)

#L156Dec11_W3_test5<-filter(L156Dec11_W3,Minutes>21 & Minutes<=26)

L159Dec11_W3_test5<-filter(L159Dec11_W3,Minutes>23 & Minutes<=28)

L161Dec11_W3_test5<-filter(L161Dec11_W3,Minutes>23 & Minutes<=28)

L162Dec11_W3_test5<-filter(L162Dec11_W3,Minutes>24 & Minutes<=29)

L165Dec11_W3_test5<-filter(L165Dec11_W3,Minutes>21 & Minutes<=26)

L167Dec11_W3_test5<-filter(L167Dec11_W3,Minutes>21 & Minutes<=26)

Dec11_W3_test5_BH<-rbind(L154Dec11_W3_test5,L159Dec11_W3_test5,L162Dec11_W3_test5,L167Dec11_W3_test5)
Dec11_W3_test5_BH<-mutate(Dec11_W3_test5_BH,FieldType=rep("conditioned"))
Dec11_W3_test5_NB<-rbind(L153Dec11_W3_test5,L161Dec11_W3_test5,L165Dec11_W3_test5)
Dec11_W3_test5_NB<-mutate(Dec11_W3_test5_NB,FieldType=rep("control"))
Dec11_W3_test5<-rbind(Dec11_W3_test5_BH,Dec11_W3_test5_NB)

Dec11_W3_test5<-Dec11_W3_test5 %>% group_by(ID,Observer,FieldType) %>% summarise(TotalTimeEl=sum(TimeEl)) 
```


```{r}
Dec11_W3_accl_BH<-rbind(L154Dec11_W3_accl,L159Dec11_W3_accl,L162Dec11_W3_accl,L167Dec11_W3_accl)
Dec11_W3_test_BH<-rbind(L154Dec11_W3_test,L159Dec11_W3_test,L162Dec11_W3_test,L167Dec11_W3_test)
library(dplyr)
Dec11_W3_accl_BH<-mutate(Dec11_W3_accl_BH,Field=rep("BH"))
Dec11_W3_accl_BH<-mutate(Dec11_W3_accl_BH,TimePer=rep("accl"))
Dec11_W3_accl_BH<-mutate(Dec11_W3_accl_BH,FieldType=rep("conditioned"))
Dec11_W3_test_BH<-mutate(Dec11_W3_test_BH,Field=rep("BH"))
Dec11_W3_test_BH<-mutate(Dec11_W3_test_BH,TimePer=rep("test"))
Dec11_W3_test_BH<-mutate(Dec11_W3_test_BH,FieldType=rep("conditioned"))
```

```{r}
Dec11_W3_accl_NB<-rbind(L153Dec11_W3_accl,L161Dec11_W3_accl,L165Dec11_W3_accl)
Dec11_W3_test_NB<-rbind(L153Dec11_W3_test,L161Dec11_W3_test,L165Dec11_W3_test)
library(dplyr)
Dec11_W3_accl_NB<-mutate(Dec11_W3_accl_NB,Field=rep("NB"))
Dec11_W3_accl_NB<-mutate(Dec11_W3_accl_NB,TimePer=rep("accl"))
Dec11_W3_accl_NB<-mutate(Dec11_W3_accl_NB,FieldType=rep("control"))
Dec11_W3_test_NB<-mutate(Dec11_W3_test_NB,Field=rep("NB"))
Dec11_W3_test_NB<-mutate(Dec11_W3_test_NB,TimePer=rep("test"))
Dec11_W3_test_NB<-mutate(Dec11_W3_test_NB,FieldType=rep("control"))
```

##Master Data Sets  
```{r}
Dec11_W3<-rbind(Dec11_W3_accl_BH,Dec11_W3_accl_NB,Dec11_W3_test_BH,Dec11_W3_test_NB)
Dec11_W3<-mutate(Dec11_W3,Date=rep("Dec11"))
Dec11_W3_BH<-rbind(Dec11_W3_accl_BH,Dec11_W3_test_BH)
Dec11_W3_NB<-rbind(Dec11_W3_accl_NB,Dec11_W3_test_NB)
```

```{r}
library(dplyr)
Dec11_W3<-Dec11_W3 %>% group_by(ID,TimePer,Observer,Field,FieldType,Date) %>% summarise(TotalTimeEl=sum(TimeEl))
Dec11_W3_test<-filter(Dec11_W3,TimePer=="test")
```


######################################################################################



#December 12

```{r}
L155Dec12W<-read.csv("L155_Dec12_Waddle.csv")
L157Dec12W<-read.csv("L157_Dec12_Waddle.csv")
#L158Dec12W<-read.csv("L158_Dec12_Waddle.csv")
L160Dec12W<-read.csv("L160_Dec12_Waddle.csv")
L163Dec12W<-read.csv("L163_Dec12_Waddle.csv")
L164Dec12W<-read.csv("L164_Dec12_Waddle.csv")
L166Dec12W<-read.csv("L166_Dec12_Waddle.csv")
L168Dec12W<-read.csv("L168_Dec12_Waddle.csv")
```

```{r}
#L158Dec12W$Time<-L158Dec12W$Time[is.na(L158Dec12W$Time)]<-0
```

```{r}
L155Dec12W$ID<-rep(NA)
L155Dec12W$ID<-L155Dec12W$ID[is.na(L155Dec12W$ID)]<- "L155"
L157Dec12W$ID<-rep(NA)
L157Dec12W$ID<-L157Dec12W$ID[is.na(L157Dec12W$ID)]<- "L157"
#L158Dec12W$ID<-rep(NA)
#L158Dec12W$ID<-L158Dec12W$ID[is.na(L158Dec12W$ID)]<- "L158"
L160Dec12W$ID<-rep(NA)
L160Dec12W$ID<-L160Dec12W$ID[is.na(L160Dec12W$ID)]<- "L160"
L163Dec12W$ID<-rep(NA)
L163Dec12W$ID<-L163Dec12W$ID[is.na(L163Dec12W$ID)]<- "L163"
L164Dec12W$ID<-rep(NA)
L164Dec12W$ID<-L164Dec12W$ID[is.na(L164Dec12W$ID)]<- "L164"
L166Dec12W$ID<-rep(NA)
L166Dec12W$ID<-L166Dec12W$ID[is.na(L166Dec12W$ID)]<- "L166"
L168Dec12W$ID<-rep(NA)
L168Dec12W$ID<-L168Dec12W$ID[is.na(L168Dec12W$ID)]<- "L168"
```

```{r}
library(plyr)
dfs_Dec12<-list(L155Dec12W,L157Dec12W,L160Dec12W,L163Dec12W,L164Dec12W,L166Dec12W,L168Dec12W)

drops<-c("Total.length","FPS","Subject","Comment","Status")

DropFunction<- function(x) {
  x<-x[ , !(names(x) %in% drops)]
  return(x)
}

Dec12_Waddle = ldply(dfs_Dec12,DropFunction)

names(Dec12_Waddle)<-c("Time","Observer", "Behavior", "Start_Stop","ID")

detach(package:plyr)
```


```{r}
Dec12_StartTimes<-subset(Dec12_Waddle,Start_Stop== "START")
names(Dec12_StartTimes)<- c("StartTime","Observer", "Behavior","Start","ID")
Dec12_StopTimes<-subset(Dec12_Waddle,Start_Stop=="STOP")
names(Dec12_StopTimes)<-c("StopTime","Observer", "Behavior","Stop","ID")
Dec12_WaddleTimes<-cbind(Dec12_StartTimes,Dec12_StopTimes)
```

```{r}
names(Dec12_WaddleTimes)<-c("StartTime","Observer", "Behavior","Start","ID","StopTime","Obs.2", "Beh.2","Stop","ID.2")
drops_doubles<-c("Start", "Obs.2"," Beh.2","Stop","ID.2")
Dec12_WaddleTimes<-Dec12_WaddleTimes[ , !(names(Dec12_WaddleTimes) %in% drops_doubles)]
Dec12_WaddleTimes<-mutate(Dec12_WaddleTimes,TimeEl=StopTime-StartTime)
Dec12_WaddleTimes<-mutate(Dec12_WaddleTimes,Minutes=StartTime/60)
```


##Subset Data by ID to set acclimation and test periods

```{r}
library(dplyr)
L155Dec12_W1<-filter(Dec12_WaddleTimes,ID=="L155")
L155Dec12_W1$Observer<-rep(NA)
L155Dec12_W1$Observer<-L155Dec12_W1$Observer[is.na(L155Dec12_W1$Observer)]<- "KaG"

L157Dec12_W1<-filter(Dec12_WaddleTimes,ID=="L157")
L157Dec12_W1$Observer<-rep(NA)
L157Dec12_W1$Observer<-L157Dec12_W1$Observer[is.na(L157Dec12_W1$Observer)]<- "KaG"

#L158Dec12_W1<-filter(Dec12_WaddleTimes,ID=="L158")
L160Dec12_W1<-filter(Dec12_WaddleTimes,ID=="L160")
L160Dec12_W1$Observer<-rep(NA)
L160Dec12_W1$Observer<-L160Dec12_W1$Observer[is.na(L160Dec12_W1$Observer)]<- "KaG"

L163Dec12_W1<-filter(Dec12_WaddleTimes,ID=="L163")
L163Dec12_W1$Observer<-rep(NA)
L163Dec12_W1$Observer<-L163Dec12_W1$Observer[is.na(L163Dec12_W1$Observer)]<- "NiI"

L164Dec12_W1<-filter(Dec12_WaddleTimes,ID=="L164")
L164Dec12_W1$Observer<-rep(NA)
L164Dec12_W1$Observer<-L164Dec12_W1$Observer[is.na(L164Dec12_W1$Observer)]<- "AnJ"

L166Dec12_W1<-filter(Dec12_WaddleTimes,ID=="L166")
L166Dec12_W1$Observer<-rep(NA)
L166Dec12_W1$Observer<-L166Dec12_W1$Observer[is.na(L166Dec12_W1$Observer)]<- "AnJ"

L168Dec12_W1<-filter(Dec12_WaddleTimes,ID=="L168")
L168Dec12_W1$Observer<-rep(NA)
L168Dec12_W1$Observer<-L168Dec12_W1$Observer[is.na(L168Dec12_W1$Observer)]<- "KaG"

```

```{r}
library(dplyr)
L155Dec12_W1_accl<-filter(L155Dec12_W1,Minutes<=22)
L155Dec12_W1_test<-filter(L155Dec12_W1,Minutes>22 & Minutes<=42)
L157Dec12_W1_accl<-filter(L157Dec12_W1,Minutes<=22)
L157Dec12_W1_test<-filter(L157Dec12_W1,Minutes>22 & Minutes<=42)
#L158Dec12_W1_accl<-filter(L158Dec12_W1,Minutes<=21)
#L158Dec12_W1_test<-filter(L158Dec12_W1,Minutes>21 & Minutes <=41)
L160Dec12_W1_accl<-filter(L160Dec12_W1,Minutes<=21)
L160Dec12_W1_test<-filter(L160Dec12_W1,Minutes>21 & Minutes <=41)
L163Dec12_W1_accl<-filter(L163Dec12_W1,Minutes<=20)
L163Dec12_W1_test<-filter(L163Dec12_W1,Minutes>20 & Minutes<=40)
L164Dec12_W1_accl<-filter(L164Dec12_W1,Minutes<=21)
L164Dec12_W1_test<-filter(L164Dec12_W1,Minutes>21 & Minutes<=41)
L166Dec12_W1_accl<-filter(L166Dec12_W1,Minutes<=25)
L166Dec12_W1_test<-filter(L166Dec12_W1,Minutes>25 & Minutes<=45)
L168Dec12_W1_accl<-filter(L168Dec12_W1,Minutes<=22)
L168Dec12_W1_test<-filter(L168Dec12_W1,Minutes>22 & Minutes<=42)
```


Dec12 W1 test 5 mins

```{r}
library(dplyr)
L155Dec12_W1_test5<-filter(L155Dec12_W1,Minutes>22 & Minutes<=27)

L157Dec12_W1_test5<-filter(L157Dec12_W1,Minutes>22 & Minutes<=27)

#L158Dec12_W1_test5<-filter(L158Dec12_W1,Minutes>21 & Minutes<=26)

L160Dec12_W1_test5<-filter(L160Dec12_W1,Minutes>21 & Minutes<=26)

L163Dec12_W1_test5<-filter(L163Dec12_W1,Minutes>20 & Minutes<=25)

L164Dec12_W1_test5<-filter(L164Dec12_W1,Minutes>21 & Minutes<=26)

L166Dec12_W1_test5<-filter(L166Dec12_W1,Minutes>25 & Minutes<=30)

L168Dec12_W1_test5<-filter(L168Dec12_W1,Minutes>22 & Minutes<=27)

Dec12_W1_test5_BH<-rbind(L155Dec12_W1_test5,L163Dec12_W1_test5,L166Dec12_W1_test5)
Dec12_W1_test5_BH<-mutate(Dec12_W1_test5_BH,FieldType=rep("control"))
Dec12_W1_test5_NB<-rbind(L157Dec12_W1_test5,L160Dec12_W1_test5,L164Dec12_W1_test5,L168Dec12_W1_test5)
Dec12_W1_test5_NB<-mutate(Dec12_W1_test5_NB,FieldType=rep("conditioned"))
Dec12_W1_test5<-rbind(Dec12_W1_test5_BH,Dec12_W1_test5_NB)

Dec12_W1_test5<-Dec12_W1_test5 %>% group_by(ID,Observer,FieldType) %>% summarise(TotalTimeEl=sum(TimeEl)) 
```


```{r}
Dec12_W1_accl_BH<-rbind(L155Dec12_W1_accl,L163Dec12_W1_accl,L166Dec12_W1_accl)
Dec12_W1_test_BH<-rbind(L155Dec12_W1_test,L163Dec12_W1_test,L166Dec12_W1_test)
library(dplyr)
Dec12_W1_accl_BH<-mutate(Dec12_W1_accl_BH,Field=rep("BH"))
Dec12_W1_accl_BH<-mutate(Dec12_W1_accl_BH,TimePer=rep("accl"))
Dec12_W1_accl_BH<-mutate(Dec12_W1_accl_BH,FieldType=rep("control"))
Dec12_W1_test_BH<-mutate(Dec12_W1_test_BH,Field=rep("BH"))
Dec12_W1_test_BH<-mutate(Dec12_W1_test_BH,TimePer=rep("test"))
Dec12_W1_test_BH<-mutate(Dec12_W1_test_BH,FieldType=rep("control"))
```

```{r}
Dec12_W1_accl_NB<-rbind(L157Dec12_W1_accl,L160Dec12_W1_accl,L164Dec12_W1_accl,L168Dec12_W1_accl)
Dec12_W1_test_NB<-rbind(L157Dec12_W1_test,L160Dec12_W1_test,L164Dec12_W1_test,L168Dec12_W1_test)
library(dplyr)
Dec12_W1_accl_NB<-mutate(Dec12_W1_accl_NB,Field=rep("NB"))
Dec12_W1_accl_NB<-mutate(Dec12_W1_accl_NB,TimePer=rep("accl"))
Dec12_W1_accl_NB<-mutate(Dec12_W1_accl_NB,FieldType=rep("conditioned"))
Dec12_W1_test_NB<-mutate(Dec12_W1_test_NB,Field=rep("NB"))
Dec12_W1_test_NB<-mutate(Dec12_W1_test_NB,TimePer=rep("test"))
Dec12_W1_test_NB<-mutate(Dec12_W1_test_NB,FieldType=rep("conditioned"))
```

##Master Data Sets 
```{r}
Dec12_W1<-rbind(Dec12_W1_accl_BH,Dec12_W1_accl_NB,Dec12_W1_test_BH,Dec12_W1_test_NB)
Dec12_W1<-mutate(Dec12_W1,Date=rep("Dec12"))
Dec12_W1_BH<-rbind(Dec12_W1_accl_BH,Dec12_W1_test_BH)
Dec12_W1_NB<-rbind(Dec12_W1_accl_NB,Dec12_W1_test_NB)
```

```{r}
library(dplyr)
Dec12_W1<-Dec12_W1 %>% group_by(ID,TimePer,Observer,Field,FieldType,Date) %>% summarise(TotalTimeEl=sum(TimeEl))
Dec12_W1_test<-filter(Dec12_W1,TimePer=="test")
```




#December 12 Analysis 2 

```{r}
L155Dec12W2<-read.csv("L155_Dec12_Waddle2.csv")
L157Dec12W2<-read.csv("L157_Dec12_Waddle2.csv")
L158Dec12W2<-read.csv("L158_Dec12_Waddle2.csv")
L160Dec12W2<-read.csv("L160_Dec12_Waddle2.csv",skip=15,header=T)
L163Dec12W2<-read.csv("L163_Dec12_Waddle2.csv")
L164Dec12W2<-read.csv("C:/Users/kkmgo/Documents/L164_Dec12_Waddle4.csv",skip=15,header=T)
L166Dec12W2<-read.csv("L166_Dec12_Waddle2.csv")
L168Dec12W2<-read.csv("L168_Dec12_Waddle2.csv")
```


```{r}
L155Dec12W2$ID<-rep(NA)
L155Dec12W2$ID<-L155Dec12W2$ID[is.na(L155Dec12W2$ID)]<- "L155"
L157Dec12W2$ID<-rep(NA)
L157Dec12W2$ID<-L157Dec12W2$ID[is.na(L157Dec12W2$ID)]<- "L157"
L158Dec12W2$ID<-rep(NA)
L158Dec12W2$ID<-L158Dec12W2$ID[is.na(L158Dec12W2$ID)]<- "L158"
L160Dec12W2$ID<-rep(NA)
L160Dec12W2$ID<-L160Dec12W2$ID[is.na(L160Dec12W2$ID)]<- "L160"
L163Dec12W2$ID<-rep(NA)
L163Dec12W2$ID<-L163Dec12W2$ID[is.na(L163Dec12W2$ID)]<- "L163"
L164Dec12W2$ID<-rep(NA)
L164Dec12W2$ID<-L164Dec12W2$ID[is.na(L164Dec12W2$ID)]<- "L164"
L166Dec12W2$ID<-rep(NA)
L166Dec12W2$ID<-L166Dec12W2$ID[is.na(L166Dec12W2$ID)]<- "L166"
L168Dec12W2$ID<-rep(NA)
L168Dec12W2$ID<-L168Dec12W2$ID[is.na(L168Dec12W2$ID)]<- "L168"
```

```{r}
library(plyr)
dfs_Dec12_2<-list(L155Dec12W2,L157Dec12W2,L158Dec12W2,L160Dec12W2,L163Dec12W2,L164Dec12W2,L166Dec12W2,L168Dec12W2)

drops<-c("Total.length","FPS","Subject","Comment","Status")

DropFunction<- function(x) {
  x<-x[ , !(names(x) %in% drops)]
  return(x)
}

Dec12_Waddle2 = ldply(dfs_Dec12_2,DropFunction)

names(Dec12_Waddle2)<-c("Time","Observer", "Behavior", "Start_Stop","ID")

detach(package:plyr)
```


```{r}
Dec12_StartTimes2<-subset(Dec12_Waddle2,Start_Stop== "START")
names(Dec12_StartTimes2)<- c("StartTime","Observer","Behavior","Start","ID")
Dec12_StopTimes2<-subset(Dec12_Waddle2,Start_Stop=="STOP")
names(Dec12_StopTimes2)<-c("StopTime","Observer","Behavior","Stop","ID")
Dec12_WaddleTimes2<-cbind(Dec12_StartTimes2,Dec12_StopTimes2)
```

```{r}
names(Dec12_WaddleTimes2)<-c("StartTime","Observer","Behavior","Start","ID","StopTime","Obs.2","Beh.2","Stop","ID.2")
drops_doubles<-c("Start","Obs.2","Beh.2","Stop","ID.2")
Dec12_WaddleTimes2<-Dec12_WaddleTimes2[ , !(names(Dec12_WaddleTimes2) %in% drops_doubles)]
Dec12_WaddleTimes2<-mutate(Dec12_WaddleTimes2,TimeEl=StopTime-StartTime)
Dec12_WaddleTimes2<-mutate(Dec12_WaddleTimes2,Minutes=StartTime/60)
```


##Subset Data by ID to set acclimation and test periods

```{r}
library(dplyr)
L155Dec12_W2<-filter(Dec12_WaddleTimes2,ID=="L155")
L155Dec12_W2$Observer<-rep(NA)
L155Dec12_W2$Observer<-L155Dec12_W2$Observer[is.na(L155Dec12_W2$Observer)]<- "EmT"

L157Dec12_W2<-filter(Dec12_WaddleTimes2,ID=="L157")
L157Dec12_W2$Observer<-rep(NA)
L157Dec12_W2$Observer<-L157Dec12_W2$Observer[is.na(L157Dec12_W2$Observer)]<- "EmT"

L158Dec12_W2<-filter(Dec12_WaddleTimes2,ID=="L158")
L158Dec12_W2$Observer<-rep(NA)
L158Dec12_W2$Observer<-L158Dec12_W2$Observer[is.na(L158Dec12_W2$Observer)]<- "MjH"

L160Dec12_W2<-filter(Dec12_WaddleTimes2,ID=="L160")
L160Dec12_W2$Observer<-rep(NA)
L160Dec12_W2$Observer<-L160Dec12_W2$Observer[is.na(L160Dec12_W2$Observer)]<- "AnJ"

L163Dec12_W2<-filter(Dec12_WaddleTimes2,ID=="L163")
L163Dec12_W2$Observer<-rep(NA)
L163Dec12_W2$Observer<-L163Dec12_W2$Observer[is.na(L163Dec12_W2$Observer)]<- "EmT"

L164Dec12_W2<-filter(Dec12_WaddleTimes2,ID=="L164")
L164Dec12_W2$Observer<-rep(NA)
L164Dec12_W2$Observer<-L164Dec12_W2$Observer[is.na(L164Dec12_W2$Observer)]<- "EmT"

L166Dec12_W2<-filter(Dec12_WaddleTimes2,ID=="L166")
L166Dec12_W2$Observer<-rep(NA)
L166Dec12_W2$Observer<-L166Dec12_W2$Observer[is.na(L166Dec12_W2$Observer)]<- "NaB"

L168Dec12_W2<-filter(Dec12_WaddleTimes2,ID=="L168")
L168Dec12_W2$Observer<-rep(NA)
L168Dec12_W2$Observer<-L168Dec12_W2$Observer[is.na(L168Dec12_W2$Observer)]<- "NaB"
```

```{r}
library(dplyr)
L155Dec12_W2_accl<-filter(L155Dec12_W2,Minutes<=22)
L155Dec12_W2_test<-filter(L155Dec12_W2,Minutes>22 & Minutes<=42)
L157Dec12_W2_accl<-filter(L157Dec12_W2,Minutes<=22)
L157Dec12_W2_test<-filter(L157Dec12_W2,Minutes>22 & Minutes<=42)
L158Dec12_W2_accl<-filter(L158Dec12_W2,Minutes<=21)
L158Dec12_W2_test<-filter(L158Dec12_W2,Minutes>21 & Minutes <=41)
L160Dec12_W2_accl<-filter(L160Dec12_W2,Minutes<=21)
L160Dec12_W2_test<-filter(L160Dec12_W2,Minutes>21 & Minutes <=41)
L163Dec12_W2_accl<-filter(L163Dec12_W2,Minutes<=20)
L163Dec12_W2_test<-filter(L163Dec12_W2,Minutes>20 & Minutes<=40)
L164Dec12_W2_accl<-filter(L164Dec12_W2,Minutes<=21)
L164Dec12_W2_test<-filter(L164Dec12_W2,Minutes>21 & Minutes<=41)
L166Dec12_W2_accl<-filter(L166Dec12_W2,Minutes<=25)
L166Dec12_W2_test<-filter(L166Dec12_W2,Minutes>25 & Minutes<=45)
L168Dec12_W2_accl<-filter(L168Dec12_W2,Minutes<=22)
L168Dec12_W2_test<-filter(L168Dec12_W2,Minutes>22 & Minutes<=42)
```


Dec12 W2 test 5 mins

```{r}
library(dplyr)
L155Dec12_W2_test5<-filter(L155Dec12_W2,Minutes>22 & Minutes<=27)

L157Dec12_W2_test5<-filter(L157Dec12_W2,Minutes>22 & Minutes<=27)

L158Dec12_W2_test5<-filter(L158Dec12_W2,Minutes>21 & Minutes<=26)

L160Dec12_W2_test5<-filter(L160Dec12_W2,Minutes>21 & Minutes<=26)

L163Dec12_W2_test5<-filter(L163Dec12_W2,Minutes>20 & Minutes<=25)

L164Dec12_W2_test5<-filter(L164Dec12_W2,Minutes>21 & Minutes<=26)

L166Dec12_W2_test5<-filter(L166Dec12_W2,Minutes>25 & Minutes<=30)

L168Dec12_W2_test5<-filter(L168Dec12_W2,Minutes>22 & Minutes<=27)

Dec12_W2_test5_BH<-rbind(L155Dec12_W2_test5,L158Dec12_W2_test5,L163Dec12_W2_test5,L166Dec12_W2_test5)
Dec12_W2_test5_BH<-mutate(Dec12_W2_test5_BH,FieldType=rep("control"))
Dec12_W2_test5_NB<-rbind(L157Dec12_W2_test5,L160Dec12_W2_test5,L164Dec12_W2_test5,L168Dec12_W2_test5)
Dec12_W2_test5_NB<-mutate(Dec12_W2_test5_NB,FieldType=rep("conditioned"))
Dec12_W2_test5<-rbind(Dec12_W2_test5_BH,Dec12_W2_test5_NB)

Dec12_W2_test5<-Dec12_W2_test5 %>% group_by(ID,Observer,FieldType) %>% summarise(TotalTimeEl=sum(TimeEl)) 
```




```{r}
Dec12_W2_accl_BH<-rbind(L155Dec12_W2_accl,L158Dec12_W2_accl,L163Dec12_W2_accl,L166Dec12_W2_accl)
Dec12_W2_test_BH<-rbind(L155Dec12_W2_test,L158Dec12_W2_test,L163Dec12_W2_test,L166Dec12_W2_test)
library(dplyr)
Dec12_W2_accl_BH<-mutate(Dec12_W2_accl_BH,Field=rep("BH"))
Dec12_W2_accl_BH<-mutate(Dec12_W2_accl_BH,TimePer=rep("accl"))
Dec12_W2_accl_BH<-mutate(Dec12_W2_accl_BH,FieldType=rep("control"))
Dec12_W2_test_BH<-mutate(Dec12_W2_test_BH,Field=rep("BH"))
Dec12_W2_test_BH<-mutate(Dec12_W2_test_BH,TimePer=rep("test"))
Dec12_W2_test_BH<-mutate(Dec12_W2_test_BH,FieldType=rep("control"))
```

```{r}
Dec12_W2_accl_NB<-rbind(L157Dec12_W2_accl,L160Dec12_W2_accl,L164Dec12_W2_accl,L168Dec12_W2_accl)
Dec12_W2_test_NB<-rbind(L157Dec12_W2_test,L160Dec12_W2_test,L164Dec12_W2_test,L168Dec12_W2_test)
library(dplyr)
Dec12_W2_accl_NB<-mutate(Dec12_W2_accl_NB,Field=rep("NB"))
Dec12_W2_accl_NB<-mutate(Dec12_W2_accl_NB,TimePer=rep("accl"))
Dec12_W2_accl_NB<-mutate(Dec12_W2_accl_NB,FieldType=rep("conditioned"))
Dec12_W2_test_NB<-mutate(Dec12_W2_test_NB,Field=rep("NB"))
Dec12_W2_test_NB<-mutate(Dec12_W2_test_NB,TimePer=rep("test"))
Dec12_W2_test_NB<-mutate(Dec12_W2_test_NB,FieldType=rep("conditioned"))
```

##Master Data Sets 
```{r}
Dec12_W2<-rbind(Dec12_W2_accl_BH,Dec12_W2_accl_NB,Dec12_W2_test_BH,Dec12_W2_test_NB)
Dec12_W2<-mutate(Dec12_W2,Date=rep("Dec12"))
Dec12_W2_BH<-rbind(Dec12_W2_accl_BH,Dec12_W2_test_BH)
Dec12_W2_NB<-rbind(Dec12_W2_accl_NB,Dec12_W2_test_NB)
```

```{r}
library(dplyr)
Dec12_W2<-Dec12_W2 %>% group_by(ID,TimePer,Observer,Field,FieldType,Date) %>% summarise(TotalTimeEl=sum(TimeEl))
Dec12_W2_test<-filter(Dec12_W2,TimePer=="test")
```

#December 12 Analysis 3#############################

```{r}
L155Dec12W3<-read.csv("L155_Dec12_Waddle4.csv",skip=15,header=T)
L157Dec12W3<-read.csv("L157_Dec12_Waddle3.csv",skip=15,header=T)
L158Dec12W3<-read.csv("L158_Dec12_Waddle3.csv",skip=15,header=T)
L160Dec12W3<-read.csv("L160_Dec12_Waddle3.csv",skip=15,header=T)
L163Dec12W3<-read.csv("L163_Dec12_Waddle4.csv",skip=15,header=T)
L164Dec12W3<-read.csv("L164_Dec12_Waddle3.csv",skip=15,header=T)
L166Dec12W3<-read.csv("L166_Dec12_Waddle3.csv",skip=15,header=T)
L168Dec12W3<-read.csv("L168_Dec12_Waddle3.csv",skip=15,header=T)
```


```{r}
L155Dec12W3$ID<-rep(NA)
L155Dec12W3$ID<-L155Dec12W3$ID[is.na(L155Dec12W3$ID)]<- "L155"
L157Dec12W3$ID<-rep(NA)
L157Dec12W3$ID<-L157Dec12W3$ID[is.na(L157Dec12W3$ID)]<- "L157"
L158Dec12W3$ID<-rep(NA)
L158Dec12W3$ID<-L158Dec12W3$ID[is.na(L158Dec12W3$ID)]<- "L158"
L160Dec12W3$ID<-rep(NA)
L160Dec12W3$ID<-L160Dec12W3$ID[is.na(L160Dec12W3$ID)]<- "L160"
L163Dec12W3$ID<-rep(NA)
L163Dec12W3$ID<-L163Dec12W3$ID[is.na(L163Dec12W3$ID)]<- "L163"
L164Dec12W3$ID<-rep(NA)
L164Dec12W3$ID<-L164Dec12W3$ID[is.na(L164Dec12W3$ID)]<- "L164"
L166Dec12W3$ID<-rep(NA)
L166Dec12W3$ID<-L166Dec12W3$ID[is.na(L166Dec12W3$ID)]<- "L166"
L168Dec12W3$ID<-rep(NA)
L168Dec12W3$ID<-L168Dec12W3$ID[is.na(L168Dec12W3$ID)]<- "L168"
```

```{r}
library(plyr)
dfs_Dec12_3<-list(L155Dec12W3,L157Dec12W3,L158Dec12W3,L160Dec12W3,L163Dec12W3,L164Dec12W3,L166Dec12W3,L168Dec12W3)

drops<-c("Total.length","FPS","Subject","Comment","Status")

DropFunction<- function(x) {
  x<-x[ , !(names(x) %in% drops)]
  return(x)
}

Dec12_Waddle3 = ldply(dfs_Dec12_3,DropFunction)

names(Dec12_Waddle3)<-c("Time","Observer", "Behavior", "Start_Stop","ID")

detach(package:plyr)
```


```{r}
Dec12_StartTimes3<-subset(Dec12_Waddle3,Start_Stop== "START")
names(Dec12_StartTimes3)<- c("StartTime","Observer","Behavior","Start","ID")
Dec12_StopTimes3<-subset(Dec12_Waddle3,Start_Stop=="STOP")
names(Dec12_StopTimes3)<-c("StopTime","Observer","Behavior","Stop","ID")
Dec12_WaddleTimes3<-cbind(Dec12_StartTimes3,Dec12_StopTimes3)
```

```{r}
names(Dec12_WaddleTimes3)<-c("StartTime","Observer","Behavior","Start","ID","StopTime","Obs.2","Beh.2","Stop","ID.2")
drops_doubles<-c("Start","Obs.2","Beh.2","Stop","ID.2")
Dec12_WaddleTimes3<-Dec12_WaddleTimes3[ , !(names(Dec12_WaddleTimes3) %in% drops_doubles)]
Dec12_WaddleTimes3<-mutate(Dec12_WaddleTimes3,TimeEl=StopTime-StartTime)
Dec12_WaddleTimes3<-mutate(Dec12_WaddleTimes3,Minutes=StartTime/60)
```


##Subset Data by ID to set acclimation and test periods

```{r}
library(dplyr)
L155Dec12_W3<-filter(Dec12_WaddleTimes3,ID=="L155")
L155Dec12_W3$Observer<-rep(NA)
L155Dec12_W3$Observer<-L155Dec12_W3$Observer[is.na(L155Dec12_W3$Observer)]<- "MjH"

L157Dec12_W3<-filter(Dec12_WaddleTimes3,ID=="L157")
L157Dec12_W3$Observer<-rep(NA)
L157Dec12_W3$Observer<-L157Dec12_W3$Observer[is.na(L157Dec12_W3$Observer)]<- "NiI"

L158Dec12_W3<-filter(Dec12_WaddleTimes3,ID=="L158")
L158Dec12_W3$Observer<-rep(NA)
L158Dec12_W3$Observer<-L158Dec12_W3$Observer[is.na(L158Dec12_W3$Observer)]<- "AnJ"

L160Dec12_W3<-filter(Dec12_WaddleTimes3,ID=="L160")
L160Dec12_W3$Observer<-rep(NA)
L160Dec12_W3$Observer<-L160Dec12_W3$Observer[is.na(L160Dec12_W3$Observer)]<- "EmT"

L163Dec12_W3<-filter(Dec12_WaddleTimes3,ID=="L163")
L163Dec12_W3$Observer<-rep(NA)
L163Dec12_W3$Observer<-L163Dec12_W3$Observer[is.na(L163Dec12_W3$Observer)]<- "MjH"

L164Dec12_W3<-filter(Dec12_WaddleTimes3,ID=="L164")
L164Dec12_W3$Observer<-rep(NA)
L164Dec12_W3$Observer<-L164Dec12_W3$Observer[is.na(L164Dec12_W3$Observer)]<- "MjH"

L166Dec12_W3<-filter(Dec12_WaddleTimes3,ID=="L166")
L166Dec12_W3$Observer<-rep(NA)
L166Dec12_W3$Observer<-L166Dec12_W3$Observer[is.na(L166Dec12_W3$Observer)]<- "EmT"

L168Dec12_W3<-filter(Dec12_WaddleTimes3,ID=="L168")
L168Dec12_W3$Observer<-rep(NA)
L168Dec12_W3$Observer<-L168Dec12_W3$Observer[is.na(L168Dec12_W3$Observer)]<- "MjH"
```

```{r}
library(dplyr)
L155Dec12_W3_accl<-filter(L155Dec12_W3,Minutes<=22)
L155Dec12_W3_test<-filter(L155Dec12_W3,Minutes>22 & Minutes<=42)
L157Dec12_W3_accl<-filter(L157Dec12_W3,Minutes<=22)
L157Dec12_W3_test<-filter(L157Dec12_W3,Minutes>22 & Minutes<=42)
L158Dec12_W3_accl<-filter(L158Dec12_W3,Minutes<=21)
L158Dec12_W3_test<-filter(L158Dec12_W3,Minutes>21 & Minutes <=41)
L160Dec12_W3_accl<-filter(L160Dec12_W3,Minutes<=21)
L160Dec12_W3_test<-filter(L160Dec12_W3,Minutes>21 & Minutes <=41)
L163Dec12_W3_accl<-filter(L163Dec12_W3,Minutes<=20)
L163Dec12_W3_test<-filter(L163Dec12_W3,Minutes>20 & Minutes<=40)
L164Dec12_W3_accl<-filter(L164Dec12_W3,Minutes<=21)
L164Dec12_W3_test<-filter(L164Dec12_W3,Minutes>21 & Minutes<=41)
L166Dec12_W3_accl<-filter(L166Dec12_W3,Minutes<=25)
L166Dec12_W3_test<-filter(L166Dec12_W3,Minutes>25 & Minutes<=45)
L168Dec12_W3_accl<-filter(L168Dec12_W3,Minutes<=22)
L168Dec12_W3_test<-filter(L168Dec12_W3,Minutes>22 & Minutes<=42)
```

Dec12 W3 test 5 mins

```{r}
library(dplyr)
L155Dec12_W3_test5<-filter(L155Dec12_W2,Minutes>22 & Minutes<=27)

L157Dec12_W3_test5<-filter(L157Dec12_W2,Minutes>22 & Minutes<=27)

L158Dec12_W3_test5<-filter(L158Dec12_W2,Minutes>21 & Minutes<=26)

L160Dec12_W3_test5<-filter(L160Dec12_W2,Minutes>21 & Minutes<=26)

L163Dec12_W3_test5<-filter(L163Dec12_W2,Minutes>20 & Minutes<=25)

L164Dec12_W3_test5<-filter(L164Dec12_W2,Minutes>21 & Minutes<=26)

L166Dec12_W3_test5<-filter(L166Dec12_W2,Minutes>25 & Minutes<=30)

L168Dec12_W3_test5<-filter(L168Dec12_W2,Minutes>22 & Minutes<=27)

Dec12_W3_test5_BH<-rbind(L155Dec12_W3_test5,L158Dec12_W3_test5,L163Dec12_W3_test5,L166Dec12_W3_test5)
Dec12_W3_test5_BH<-mutate(Dec12_W3_test5_BH,FieldType=rep("control"))
Dec12_W3_test5_NB<-rbind(L157Dec12_W3_test5,L160Dec12_W3_test5,L164Dec12_W3_test5,L168Dec12_W3_test5)
Dec12_W3_test5_NB<-mutate(Dec12_W3_test5_NB,FieldType=rep("conditioned"))
Dec12_W3_test5<-rbind(Dec12_W3_test5_BH,Dec12_W3_test5_NB)

Dec12_W3_test5<-Dec12_W3_test5 %>% group_by(ID,Observer,FieldType) %>% summarise(TotalTimeEl=sum(TimeEl)) 
```


```{r}
Dec12_W3_accl_BH<-rbind(L155Dec12_W3_accl,L158Dec12_W3_accl,L163Dec12_W3_accl,L166Dec12_W3_accl)
Dec12_W3_test_BH<-rbind(L155Dec12_W3_test,L158Dec12_W3_test,L163Dec12_W3_test,L166Dec12_W3_test)
library(dplyr)
Dec12_W3_accl_BH<-mutate(Dec12_W3_accl_BH,Field=rep("BH"))
Dec12_W3_accl_BH<-mutate(Dec12_W3_accl_BH,TimePer=rep("accl"))
Dec12_W3_accl_BH<-mutate(Dec12_W3_accl_BH,FieldType=rep("control"))
Dec12_W3_test_BH<-mutate(Dec12_W3_test_BH,Field=rep("BH"))
Dec12_W3_test_BH<-mutate(Dec12_W3_test_BH,TimePer=rep("test"))
Dec12_W3_test_BH<-mutate(Dec12_W3_test_BH,FieldType=rep("control"))
```

```{r}
Dec12_W3_accl_NB<-rbind(L157Dec12_W3_accl,L160Dec12_W3_accl,L164Dec12_W3_accl,L168Dec12_W3_accl)
Dec12_W3_test_NB<-rbind(L157Dec12_W3_test,L160Dec12_W3_test,L164Dec12_W3_test,L168Dec12_W3_test)
library(dplyr)
Dec12_W3_accl_NB<-mutate(Dec12_W3_accl_NB,Field=rep("NB"))
Dec12_W3_accl_NB<-mutate(Dec12_W3_accl_NB,TimePer=rep("accl"))
Dec12_W3_accl_NB<-mutate(Dec12_W3_accl_NB,FieldType=rep("conditioned"))
Dec12_W3_test_NB<-mutate(Dec12_W3_test_NB,Field=rep("NB"))
Dec12_W3_test_NB<-mutate(Dec12_W3_test_NB,TimePer=rep("test"))
Dec12_W3_test_NB<-mutate(Dec12_W3_test_NB,FieldType=rep("conditioned"))
```

##Master Data Sets 
```{r}
Dec12_W3<-rbind(Dec12_W3_accl_BH,Dec12_W3_accl_NB,Dec12_W3_test_BH,Dec12_W3_test_NB)
Dec12_W3<-mutate(Dec12_W3,Date=rep("Dec12"))
Dec12_W3_BH<-rbind(Dec12_W3_accl_BH,Dec12_W3_test_BH)
Dec12_W3_NB<-rbind(Dec12_W3_accl_NB,Dec12_W3_test_NB)
```

```{r}
library(dplyr)
Dec12_W3<-Dec12_W3 %>% group_by(ID,TimePer,Observer,Field,FieldType,Date) %>% summarise(TotalTimeEl=sum(TimeEl))
Dec12_W3_test<-filter(Dec12_W3,TimePer=="test")
```


#######################################################################

##Dec 13 Analysis

```{r}
L153Dec13W1<-read.csv("L153_Dec13_Waddle.csv")
#L153Dec13W2<-read.csv("L153_Dec13_Waddle2.csv")
L153Dec13W3<-read.csv("L153_Dec13_Waddle3.csv",skip = 15,header=T)
L154Dec13W1<-read.csv("L154_Dec13_Waddle.csv")
L154Dec13W2<-read.csv("L154_Dec13_Waddle2.csv")
L154Dec13W3<-read.csv("L154_Dec13_Waddle3.csv",skip = 15,header=T)
L156Dec13W1<-read.csv("L156_Dec13_Waddle.csv")
L156Dec13W2<-read.csv("L156_Dec13_Waddle2.csv")
L156Dec13W3<-read.csv("L156_Dec13_Waddle3.csv",skip = 15,header=T)
L159Dec13W1<-read.csv("L159_Dec13_Waddle.csv")
L159Dec13W2<-read.csv("L159_Dec13_Waddle2.csv")
L159Dec13W3<-read.csv("L159_Dec13_Waddle3.csv",skip = 15,header=T)
```


```{r}
L153Dec13W1$ID<-rep(NA)
L153Dec13W1$ID<-L153Dec13W1$ID[is.na(L153Dec13W1$ID)]<- "L153"
#L153Dec13W2$ID<-rep(NA)
#L153Dec13W2$ID<-L153Dec13W2$ID[is.na(L153Dec13W2$ID)]<- "L153"
L153Dec13W3$ID<-rep(NA)
L153Dec13W3$ID<-L153Dec13W3$ID[is.na(L153Dec13W3$ID)]<- "L153"
L154Dec13W1$ID<-rep(NA)
L154Dec13W1$ID<-L154Dec13W1$ID[is.na(L154Dec13W1$ID)]<- "L154"
L154Dec13W2$ID<-rep(NA)
L154Dec13W2$ID<-L154Dec13W2$ID[is.na(L154Dec13W2$ID)]<- "L154"
L154Dec13W3$ID<-rep(NA)
L154Dec13W3$ID<-L154Dec13W3$ID[is.na(L154Dec13W3$ID)]<- "L154"
L156Dec13W1$ID<-rep(NA)
L156Dec13W1$ID<-L156Dec13W1$ID[is.na(L156Dec13W1$ID)]<- "L156"
L156Dec13W2$ID<-rep(NA)
L156Dec13W2$ID<-L156Dec13W2$ID[is.na(L156Dec13W2$ID)]<- "L156"
L156Dec13W3$ID<-rep(NA)
L156Dec13W3$ID<-L156Dec13W3$ID[is.na(L156Dec13W3$ID)]<- "L156"
L159Dec13W1$ID<-rep(NA)
L159Dec13W1$ID<-L159Dec13W1$ID[is.na(L159Dec13W1$ID)]<- "L159"
L159Dec13W2$ID<-rep(NA)
L159Dec13W2$ID<-L159Dec13W2$ID[is.na(L159Dec13W2$ID)]<- "L159"
L159Dec13W3$ID<-rep(NA)
L159Dec13W3$ID<-L159Dec13W3$ID[is.na(L159Dec13W3$ID)]<- "L159"
```

```{r}
library(plyr)
dfs_Dec13<-list(L153Dec13W1,L154Dec13W1, L156Dec13W1,L159Dec13W1)
dfs_Dec13_2<-list(L154Dec13W2,L156Dec13W2,L159Dec13W2)
dfs_Dec13_3<-list(L153Dec13W3,L154Dec13W3,L156Dec13W3,L159Dec13W3)

drops<-c("Total.length","FPS","Subject","Comment","Status")

DropFunction<- function(x) {
  x<-x[ , !(names(x) %in% drops)]
  return(x)
}

Dec13_Waddle1 = ldply(dfs_Dec13,DropFunction)

names(Dec13_Waddle1)<-c("Time","Observer", "Behavior", "Start_Stop","ID")

Dec13_Waddle2 = ldply(dfs_Dec13_2,DropFunction)

names(Dec13_Waddle2)<-c("Time", "Observer", "Behavior", "Start_Stop","ID")

Dec13_Waddle3 = ldply(dfs_Dec13_3,DropFunction)

names(Dec13_Waddle3)<-c("Time", "Observer", "Behavior", "Start_Stop","ID")

detach(package:plyr)
```


```{r}
Dec13_StartTimes1<-subset(Dec13_Waddle1,Start_Stop== "START")
names(Dec13_StartTimes1)<- c("StartTime","Observer","Behavior","Start","ID")
Dec13_StopTimes1<-subset(Dec13_Waddle1,Start_Stop=="STOP")
names(Dec13_StopTimes1)<-c("StopTime","Observer", "Behavior","Stop","ID")
Dec13_WaddleTimes1<-cbind(Dec13_StartTimes1,Dec13_StopTimes1)

Dec13_StartTimes2<-subset(Dec13_Waddle2,Start_Stop== "START")
names(Dec13_StartTimes2)<- c("StartTime","Observer","Behavior","Start","ID")
Dec13_StopTimes2<-subset(Dec13_Waddle2,Start_Stop=="STOP")
names(Dec13_StopTimes2)<-c("StopTime","Observer", "Behavior","Stop","ID")
Dec13_WaddleTimes2<-cbind(Dec13_StartTimes2,Dec13_StopTimes2)

Dec13_StartTimes3<-subset(Dec13_Waddle3,Start_Stop== "START")
names(Dec13_StartTimes3)<- c("StartTime","Observer","Behavior","Start","ID")
Dec13_StopTimes3<-subset(Dec13_Waddle3,Start_Stop=="STOP")
names(Dec13_StopTimes3)<-c("StopTime","Observer", "Behavior","Stop","ID")
Dec13_WaddleTimes3<-cbind(Dec13_StartTimes3,Dec13_StopTimes3)
```

```{r}
names(Dec13_WaddleTimes1)<-c("StartTime","Observer", "Behavior","Start","ID","StopTime","Obs.2","Beh.2","Stop","ID.2")
drops_doubles<-c("Start","Obs.2","Beh.2","Stop","ID.2")
Dec13_WaddleTimes1<-Dec13_WaddleTimes1[ , !(names(Dec13_WaddleTimes1) %in% drops_doubles)]
Dec13_WaddleTimes1<-mutate(Dec13_WaddleTimes1,TimeEl=StopTime-StartTime)
Dec13_WaddleTimes1<-mutate(Dec13_WaddleTimes1,Minutes=StartTime/60)

names(Dec13_WaddleTimes2)<-c("StartTime","Observer", "Behavior","Start","ID","StopTime","Obs.2","Beh.2","Stop","ID.2")
drops_doubles<-c("Start","Obs.2","Beh.2","Stop","ID.2")
Dec13_WaddleTimes2<-Dec13_WaddleTimes2[ , !(names(Dec13_WaddleTimes2) %in% drops_doubles)]
Dec13_WaddleTimes2<-mutate(Dec13_WaddleTimes2,TimeEl=StopTime-StartTime)
Dec13_WaddleTimes2<-mutate(Dec13_WaddleTimes2,Minutes=StartTime/60)

names(Dec13_WaddleTimes3)<-c("StartTime","Observer", "Behavior","Start","ID","StopTime","Obs.2","Beh.2","Stop","ID.2")
drops_doubles<-c("Start","Obs.2","Beh.2","Stop","ID.2")
Dec13_WaddleTimes3<-Dec13_WaddleTimes3[ , !(names(Dec13_WaddleTimes3) %in% drops_doubles)]
Dec13_WaddleTimes3<-mutate(Dec13_WaddleTimes3,TimeEl=StopTime-StartTime)
Dec13_WaddleTimes3<-mutate(Dec13_WaddleTimes3,Minutes=StartTime/60)
```


##Subset Data by ID to set acclimation and test periods

```{r}
library(dplyr)
L153Dec13_W1<-filter(Dec13_WaddleTimes1,ID=="L153")
#L153Dec13_W2<-filter(Dec13_WaddleTimes2,ID=="L153")
L153Dec13_W3<-filter(Dec13_WaddleTimes3,ID=="L153")
L153Dec13_W1$Observer<-rep(NA)
L153Dec13_W1$Observer<-L153Dec13_W1$Observer[is.na(L153Dec13_W1$Observer)]<- "NaB"
L153Dec13_W3$Observer<-rep(NA)
L153Dec13_W3$Observer<-L153Dec13_W3$Observer[is.na(L153Dec13_W3$Observer)]<- "KaG"

L154Dec13_W1<-filter(Dec13_WaddleTimes1,ID=="L154")
L154Dec13_W2<-filter(Dec13_WaddleTimes2,ID=="L154")
L154Dec13_W3<-filter(Dec13_WaddleTimes3,ID=="L154")
L154Dec13_W1$Observer<-rep(NA)
L154Dec13_W1$Observer<-L154Dec13_W1$Observer[is.na(L154Dec13_W1$Observer)]<- "NaB"
L154Dec13_W2$Observer<-rep(NA)
L154Dec13_W2$Observer<-L154Dec13_W2$Observer[is.na(L154Dec13_W2$Observer)]<- "NiI"
L154Dec13_W3$Observer<-rep(NA)
L154Dec13_W3$Observer<-L154Dec13_W3$Observer[is.na(L154Dec13_W3$Observer)]<- "KaG"

L156Dec13_W1<-filter(Dec13_WaddleTimes1,ID=="L156")
L156Dec13_W2<-filter(Dec13_WaddleTimes2,ID=="L156")
L156Dec13_W3<-filter(Dec13_WaddleTimes3,ID=="L156")
L156Dec13_W1$Observer<-rep(NA)
L156Dec13_W1$Observer<-L156Dec13_W1$Observer[is.na(L156Dec13_W1$Observer)]<- "AnJ"
L156Dec13_W2$Observer<-rep(NA)
L156Dec13_W2$Observer<-L156Dec13_W2$Observer[is.na(L156Dec13_W2$Observer)]<- "NiI"
L156Dec13_W3$Observer<-rep(NA)
L156Dec13_W3$Observer<-L156Dec13_W3$Observer[is.na(L156Dec13_W3$Observer)]<- "KaG"


L159Dec13_W1<-filter(Dec13_WaddleTimes1,ID=="L159")
L159Dec13_W2<-filter(Dec13_WaddleTimes2,ID=="L159")
L159Dec13_W3<-filter(Dec13_WaddleTimes3,ID=="L159")
L159Dec13_W1$Observer<-rep(NA)
L159Dec13_W1$Observer<-L159Dec13_W1$Observer[is.na(L159Dec13_W1$Observer)]<- "AnJ"
L159Dec13_W2$Observer<-rep(NA)
L159Dec13_W2$Observer<-L159Dec13_W2$Observer[is.na(L159Dec13_W2$Observer)]<- "NiI"
L159Dec13_W3$Observer<-rep(NA)
L159Dec13_W3$Observer<-L159Dec13_W3$Observer[is.na(L159Dec13_W3$Observer)]<- "KaG"

```

```{r}
library(dplyr)
L153Dec13_W1_accl<-filter(L153Dec13_W1,Minutes<=21)
L153Dec13_W1_test<-filter(L153Dec13_W1,Minutes>21 & Minutes<=41)
#L153Dec13_W2_accl<-filter(L153Dec13_W2,Minutes<=21)
#L153Dec13_W2_test<-filter(L153Dec13_W2,Minutes>21 & Minutes<=41)
L153Dec13_W3_accl<-filter(L153Dec13_W3,Minutes<=21)
L153Dec13_W3_test<-filter(L153Dec13_W3,Minutes>21 & Minutes<=41)

L154Dec13_W1_accl<-filter(L154Dec13_W1,Minutes<=21)
L154Dec13_W1_test<-filter(L154Dec13_W1,Minutes>21 & Minutes <=41)
L154Dec13_W2_accl<-filter(L154Dec13_W2,Minutes<=21)
L154Dec13_W2_test<-filter(L154Dec13_W2,Minutes>21 & Minutes <=41)
L154Dec13_W3_accl<-filter(L154Dec13_W3,Minutes<=21)
L154Dec13_W3_test<-filter(L154Dec13_W3,Minutes>21 & Minutes <=41)

L156Dec13_W1_accl<-filter(L156Dec13_W1,Minutes<=21)
L156Dec13_W1_test<-filter(L156Dec13_W1,Minutes>21 & Minutes<=41)
L156Dec13_W2_accl<-filter(L156Dec13_W2,Minutes<=21)
L156Dec13_W2_test<-filter(L156Dec13_W2,Minutes>21 & Minutes<=41)
L156Dec13_W3_accl<-filter(L156Dec13_W3,Minutes<=21)
L156Dec13_W3_test<-filter(L156Dec13_W3,Minutes>21 & Minutes<=41)

L159Dec13_W1_accl<-filter(L159Dec13_W1,Minutes<=21)
L159Dec13_W1_test<-filter(L159Dec13_W1,Minutes>21 & Minutes<=41)
L159Dec13_W2_accl<-filter(L159Dec13_W2,Minutes<=21)
L159Dec13_W2_test<-filter(L159Dec13_W2,Minutes>21 & Minutes<=41)
L159Dec13_W3_accl<-filter(L159Dec13_W3,Minutes<=21)
L159Dec13_W3_test<-filter(L159Dec13_W3,Minutes>21 & Minutes<=41)
```

Dec13 W1 5 mins test

```{r}
library(dplyr)
L153Dec13_W1_test5<-filter(L153Dec13_W1,Minutes>21 & Minutes<=26)

L154Dec13_W1_test5<-filter(L154Dec13_W1,Minutes>21 & Minutes<=26)

L156Dec13_W1_test5<-filter(L156Dec13_W1,Minutes>21 & Minutes<=26)

L159Dec13_W1_test5<-filter(L159Dec13_W1,Minutes>21 & Minutes<=26)


Dec13_W1_test5_BH<-rbind(L154Dec13_W1_test5,L159Dec13_W1_test5)
Dec13_W1_test5_BH<-mutate(Dec13_W1_test5_BH,FieldType=rep("conditioned"))
Dec13_W1_test5_NB<-rbind(L153Dec13_W1_test5,L156Dec13_W1_test5)
Dec13_W1_test5_NB<-mutate(Dec13_W1_test5_NB,FieldType=rep("control"))
Dec13_W1_test5<-rbind(Dec13_W1_test5_BH,Dec13_W1_test5_NB)

Dec13_W1_test5<-Dec13_W1_test5 %>% group_by(ID,Observer,FieldType) %>% summarise(TotalTimeEl=sum(TimeEl)) 
```


Dec13 W2 test 5 mins
```{r}
library(dplyr)
L153Dec13_W2_test5<-filter(L153Dec13_W1,Minutes>21 & Minutes<=26)

L154Dec13_W2_test5<-filter(L154Dec13_W1,Minutes>21 & Minutes<=26)

L156Dec13_W2_test5<-filter(L156Dec13_W1,Minutes>21 & Minutes<=26)

L159Dec13_W2_test5<-filter(L159Dec13_W1,Minutes>21 & Minutes<=26)


Dec13_W2_test5_BH<-rbind(L154Dec13_W2_test5,L159Dec13_W2_test5)
Dec13_W2_test5_BH<-mutate(Dec13_W2_test5_BH,FieldType=rep("conditioned"))
Dec13_W2_test5_NB<-rbind(L153Dec13_W2_test5,L156Dec13_W2_test5)
Dec13_W2_test5_NB<-mutate(Dec13_W2_test5_NB,FieldType=rep("control"))
Dec13_W2_test5<-rbind(Dec13_W2_test5_BH,Dec13_W2_test5_NB)

Dec13_W2_test5<-Dec13_W2_test5 %>% group_by(ID,Observer,FieldType) %>% summarise(TotalTimeEl=sum(TimeEl)) 
```

Dec13 W3 test 5 mins
```{r}
library(dplyr)
L153Dec13_W3_test5<-filter(L153Dec13_W3,Minutes>21 & Minutes<=26)

L154Dec13_W3_test5<-filter(L154Dec13_W3,Minutes>21 & Minutes<=26)

L156Dec13_W3_test5<-filter(L156Dec13_W3,Minutes>21 & Minutes<=26)

L159Dec13_W3_test5<-filter(L159Dec13_W3,Minutes>21 & Minutes<=26)


Dec13_W3_test5_BH<-rbind(L154Dec13_W3_test5,L159Dec13_W3_test5)
Dec13_W3_test5_BH<-mutate(Dec13_W3_test5_BH,FieldType=rep("conditioned"))
Dec13_W3_test5_NB<-rbind(L153Dec13_W3_test5,L156Dec13_W3_test5)
Dec13_W3_test5_NB<-mutate(Dec13_W3_test5_NB,FieldType=rep("control"))
Dec13_W3_test5<-rbind(Dec13_W3_test5_BH,Dec13_W3_test5_NB)

Dec13_W3_test5<-Dec13_W3_test5 %>% group_by(ID,Observer,FieldType) %>% summarise(TotalTimeEl=sum(TimeEl)) 
```


```{r}
Dec13_W1_accl_BH<-rbind(L154Dec13_W1_accl,L159Dec13_W1_accl)
Dec13_W1_test_BH<-rbind(L154Dec13_W1_test,L159Dec13_W1_test)
library(dplyr)
Dec13_W1_accl_BH<-mutate(Dec13_W1_accl_BH,Field=rep("BH"))
Dec13_W1_accl_BH<-mutate(Dec13_W1_accl_BH,TimePer=rep("accl"))
Dec13_W1_accl_BH<-mutate(Dec13_W1_accl_BH,FieldType=rep("conditioned"))
Dec13_W1_test_BH<-mutate(Dec13_W1_test_BH,Field=rep("BH"))
Dec13_W1_test_BH<-mutate(Dec13_W1_test_BH,TimePer=rep("test"))
Dec13_W1_test_BH<-mutate(Dec13_W1_test_BH,FieldType=rep("conditioned"))
```

```{r}
Dec13_W2_accl_BH<-rbind(L154Dec13_W2_accl,L159Dec13_W2_accl)
Dec13_W2_test_BH<-rbind(L154Dec13_W2_test,L159Dec13_W2_test)
library(dplyr)
Dec13_W2_accl_BH<-mutate(Dec13_W2_accl_BH,Field=rep("BH"))
Dec13_W2_accl_BH<-mutate(Dec13_W2_accl_BH,TimePer=rep("accl"))
Dec13_W2_accl_BH<-mutate(Dec13_W2_accl_BH,FieldType=rep("conditioned"))
Dec13_W2_test_BH<-mutate(Dec13_W2_test_BH,Field=rep("BH"))
Dec13_W2_test_BH<-mutate(Dec13_W2_test_BH,TimePer=rep("test"))
Dec13_W2_test_BH<-mutate(Dec13_W2_test_BH,FieldType=rep("conditioned"))
```

```{r}
Dec13_W3_accl_BH<-rbind(L154Dec13_W3_accl,L159Dec13_W3_accl)
Dec13_W3_test_BH<-rbind(L154Dec13_W3_test,L159Dec13_W3_test)
library(dplyr)
Dec13_W3_accl_BH<-mutate(Dec13_W3_accl_BH,Field=rep("BH"))
Dec13_W3_accl_BH<-mutate(Dec13_W3_accl_BH,TimePer=rep("accl"))
Dec13_W3_accl_BH<-mutate(Dec13_W3_accl_BH,FieldType=rep("conditioned"))
Dec13_W3_test_BH<-mutate(Dec13_W3_test_BH,Field=rep("BH"))
Dec13_W3_test_BH<-mutate(Dec13_W3_test_BH,TimePer=rep("test"))
Dec13_W3_test_BH<-mutate(Dec13_W3_test_BH,FieldType=rep("conditioned"))
```

```{r}
Dec13_W1_accl_NB<-rbind(L153Dec13_W1_accl,L156Dec13_W1_accl)
Dec13_W1_test_NB<-rbind(L153Dec13_W1_test,L156Dec13_W1_test)
library(dplyr)
Dec13_W1_accl_NB<-mutate(Dec13_W1_accl_NB,Field=rep("NB"))
Dec13_W1_accl_NB<-mutate(Dec13_W1_accl_NB,TimePer=rep("accl"))
Dec13_W1_accl_NB<-mutate(Dec13_W1_accl_NB,FieldType=rep("control"))
Dec13_W1_test_NB<-mutate(Dec13_W1_test_NB,Field=rep("NB"))
Dec13_W1_test_NB<-mutate(Dec13_W1_test_NB,TimePer=rep("test"))
Dec13_W1_test_NB<-mutate(Dec13_W1_test_NB,FieldType=rep("control"))
```

```{r}
Dec13_W2_accl_NB<-rbind(L156Dec13_W2_accl)
Dec13_W2_test_NB<-rbind(L156Dec13_W2_test)
library(dplyr)
Dec13_W2_accl_NB<-mutate(Dec13_W2_accl_NB,Field=rep("NB"))
Dec13_W2_accl_NB<-mutate(Dec13_W2_accl_NB,TimePer=rep("accl"))
Dec13_W2_accl_NB<-mutate(Dec13_W2_accl_NB,FieldType=rep("control"))
Dec13_W2_test_NB<-mutate(Dec13_W2_test_NB,Field=rep("NB"))
Dec13_W2_test_NB<-mutate(Dec13_W2_test_NB,TimePer=rep("test"))
Dec13_W2_test_NB<-mutate(Dec13_W2_test_NB,FieldType=rep("control"))
```

```{r}
Dec13_W3_accl_NB<-rbind(L153Dec13_W3_accl,L156Dec13_W3_accl)
Dec13_W3_test_NB<-rbind(L153Dec13_W3_test,L156Dec13_W3_test)
library(dplyr)
Dec13_W3_accl_NB<-mutate(Dec13_W3_accl_NB,Field=rep("NB"))
Dec13_W3_accl_NB<-mutate(Dec13_W3_accl_NB,TimePer=rep("accl"))
Dec13_W3_accl_NB<-mutate(Dec13_W3_accl_NB,FieldType=rep("control"))
Dec13_W3_test_NB<-mutate(Dec13_W3_test_NB,Field=rep("NB"))
Dec13_W3_test_NB<-mutate(Dec13_W3_test_NB,TimePer=rep("test"))
Dec13_W3_test_NB<-mutate(Dec13_W3_test_NB,FieldType=rep("control"))
```

##Master Data Sets 
```{r}
Dec13_W1<-rbind(Dec13_W1_accl_BH,Dec13_W1_accl_NB,Dec13_W1_test_BH,Dec13_W1_test_NB)
Dec13_W1<-mutate(Dec13_W1,Date=rep("Dec13"))
Dec13_W1_BH<-rbind(Dec13_W1_accl_BH,Dec13_W1_test_BH)
Dec13_W1_NB<-rbind(Dec13_W1_accl_NB,Dec13_W1_test_NB)
```

```{r}
Dec13_W2<-rbind(Dec13_W2_accl_BH,Dec13_W2_accl_NB,Dec13_W2_test_BH,Dec13_W2_test_NB)
Dec13_W2<-mutate(Dec13_W2,Date=rep("Dec13"))
Dec13_W2_BH<-rbind(Dec13_W2_accl_BH,Dec13_W2_test_BH)
Dec13_W2_NB<-rbind(Dec13_W2_accl_NB,Dec13_W2_test_NB)
```

```{r}
Dec13_W3<-rbind(Dec13_W3_accl_BH,Dec13_W3_accl_NB,Dec13_W3_test_BH,Dec13_W3_test_NB)
Dec13_W3<-mutate(Dec13_W3,Date=rep("Dec13"))
Dec13_W3_BH<-rbind(Dec13_W3_accl_BH,Dec13_W3_test_BH)
Dec13_W3_NB<-rbind(Dec13_W3_accl_NB,Dec13_W3_test_NB)
```

```{r}
library(dplyr)
Dec13_W1<-Dec13_W1 %>% group_by(ID,TimePer,Observer,Field,FieldType,Date) %>% summarise(TotalTimeEl=sum(TimeEl))
Dec13_W1_test<-filter(Dec13_W1,TimePer=="test")
```

```{r}
library(dplyr)
Dec13_W2<-Dec13_W2 %>% group_by(ID,TimePer,Observer,Field,FieldType,Date) %>% summarise(TotalTimeEl=sum(TimeEl))
Dec13_W2_test<-filter(Dec13_W2,TimePer=="test")
```

```{r}
library(dplyr)
Dec13_W3<-Dec13_W3 %>% group_by(ID,TimePer,Observer,Field,FieldType,Date) %>% summarise(TotalTimeEl=sum(TimeEl))
Dec13_W3_test<-filter(Dec13_W3,TimePer=="test")
```

###############################################

#Combined & Averaged Master Data Sets

###Dec9
```{r Dec9}
library(dplyr)
Dec9_W_Avg<-full_join(Dec9_W1,Dec9_W3,by=c("ID","Date","TimePer","Field","FieldType"),na.rm=T)
Dec9_W_Avg<-full_join(Dec9_W_Avg,Dec9_W2,by=c("ID","Date","TimePer","Field","FieldType"),na.rm=T)
Dec9_W_Avg[is.na(Dec9_W_Avg)]<- 0
Dec9_W_Avg$TotalTimeEl<-as.numeric(Dec9_W_Avg$TotalTimeEl)
Dec9_W_Avg$TotalTimeEl.x<-as.numeric(Dec9_W_Avg$TotalTimeEl.x)
Dec9_W_Avg$TotalTimeEl.y<-as.numeric(Dec9_W_Avg$TotalTimeEl.y)
dropnotneeded<-c("Observer.x","Observer.y","Observer")
Dec9_W_Avg<-Dec9_W_Avg[ , !(names(Dec9_W_Avg) %in% dropnotneeded)]
Dec9_W_Avg$Freq <- rowMeans(Dec9_W_Avg[,6:8])
dropnotneeded<-c("TotalTimeEl.x","TotalTimeEl.y","TotalTimeEl")
Dec9_W<-Dec9_W_Avg[ , !(names(Dec9_W_Avg) %in% dropnotneeded)] 
#Dec9_W$Freq<-rowMeans(select(Dec9_W_Avg,starts_with("TotalTimeEl")))

```

```{r}
L162<-data.frame("L162","Dec9","NB","test","control",0)
names(L162)<-c("ID","Date","Field","TimePer","FieldType","Freq")
Dec9_W<-rbind.data.frame(Dec9_W,L162)
Dec9_W_Test<-filter(Dec9_W,TimePer=="test")
```



##Dec9 Five mins

```{r Dec9}
library(dplyr)
Dec9_W_Avg5<-full_join(Dec9_W1_test5,Dec9_W3_test5,by=c("ID","FieldType"),na.rm=T)
Dec9_W_Avg5<-full_join(Dec9_W_Avg5,Dec9_W2_test5,by=c("ID","FieldType"),na.rm=T)
Dec9_W_Avg5[is.na(Dec9_W_Avg5)]<- 0
Dec9_W_Avg5$TotalTimeEl<-as.numeric(Dec9_W_Avg5$TotalTimeEl)
Dec9_W_Avg5$TotalTimeEl.x<-as.numeric(Dec9_W_Avg5$TotalTimeEl.x)
Dec9_W_Avg5$TotalTimeEl.y<-as.numeric(Dec9_W_Avg5$TotalTimeEl.y)
dropnotneeded<-c("Observer.x","Observer.y","Observer")
Dec9_W_Avg5<-Dec9_W_Avg5[ , !(names(Dec9_W_Avg5) %in% dropnotneeded)]
Dec9_W_Avg5$Freq <- rowMeans(Dec9_W_Avg5[,3:5])
dropnotneeded<-c("TotalTimeEl.x","TotalTimeEl.y","TotalTimeEl")
Dec9_W_Avg5<-Dec9_W_Avg5[ , !(names(Dec9_W_Avg5) %in% dropnotneeded)] 

L162_5<-data.frame("L162","control",0)
names(L162_5)<-c("ID","FieldType","Freq")
Dec9_W_Avg5<-rbind(Dec9_W_Avg5,L162_5)
```



###Dec10
```{r}
library(dplyr)
Dec10_W_Avg<-full_join(Dec10_W1,Dec10_W2,by=c("ID","Date","TimePer","Field","FieldType"),na.rm=T)
Dec10_W_Avg<-full_join(Dec10_W_Avg,Dec10_W3,by=c("ID","Date","TimePer","Field","FieldType"),na.rm=T)
Dec10_W_Avg[is.na(Dec10_W_Avg)]<- 0
Dec10_W_Avg$TotalTimeEl<-as.numeric(Dec10_W_Avg$TotalTimeEl)
Dec10_W_Avg$TotalTimeEl.x<-as.numeric(Dec10_W_Avg$TotalTimeEl.x)
Dec10_W_Avg$TotalTimeEl.y<-as.numeric(Dec10_W_Avg$TotalTimeEl.y)
dropnotneeded<-c("Observer.x","Observer.y", "Observer") #Observer
Dec10_W_Avg<-Dec10_W_Avg[ , !(names(Dec10_W_Avg) %in% dropnotneeded)]
Dec10_W_Avg$Freq <- rowMeans(Dec10_W_Avg[,6:8])
dropnotneeded<-c("TotalTimeEl.x","TotalTimeEl.y","TotalTimeEl") #TotalTimeEL
Dec10_W<-Dec10_W_Avg[ , !(names(Dec10_W_Avg) %in% dropnotneeded)] 

#Dec10_W<-Dec10_W_Avg %>% group_by(ID,Date,Field,TimePer,FieldType) %>% summarize(Freq=mean(TotalTimeEl.x:TotalTimeEl.y))
Dec10_W_Test<-filter(Dec10_W,TimePer=="test")
```

#Dec10 five mins

```{r Dec9}
library(dplyr)
Dec10_W_Avg5<-full_join(Dec10_W1_test5,Dec10_W3_test5,by=c("ID","FieldType"),na.rm=T)
Dec10_W_Avg5<-full_join(Dec10_W_Avg5,Dec10_W2_test5,by=c("ID","FieldType"),na.rm=T)
Dec10_W_Avg5[is.na(Dec10_W_Avg5)]<- 0
Dec10_W_Avg5$TotalTimeEl<-as.numeric(Dec10_W_Avg5$TotalTimeEl)
Dec10_W_Avg5$TotalTimeEl.x<-as.numeric(Dec10_W_Avg5$TotalTimeEl.x)
Dec10_W_Avg5$TotalTimeEl.y<-as.numeric(Dec10_W_Avg5$TotalTimeEl.y)
dropnotneeded<-c("Observer.x","Observer.y","Observer")
Dec10_W_Avg5<-Dec10_W_Avg5[ , !(names(Dec10_W_Avg5) %in% dropnotneeded)]
Dec10_W_Avg5$Freq <- rowMeans(Dec10_W_Avg5[,3:5])
dropnotneeded<-c("TotalTimeEl.x","TotalTimeEl.y","TotalTimeEl")
Dec10_W_Avg5<-Dec10_W_Avg5[ , !(names(Dec10_W_Avg5) %in% dropnotneeded)] 
```


###Dec11 

```{r}
library(dplyr)
Dec11_W_Avg<-full_join(Dec11_W1,Dec11_W2,by=c("ID","Date","TimePer","Field","FieldType"),na.rm=T)
Dec11_W_Avg<-full_join(Dec11_W_Avg,Dec11_W3,by=c("ID","Date","TimePer","Field","FieldType"),na.rm=T)
Dec11_W_Avg[is.na(Dec11_W_Avg)]<- 0
Dec11_W_Avg$TotalTimeEl<-as.numeric(Dec11_W_Avg$TotalTimeEl)
Dec11_W_Avg$TotalTimeEl.x<-as.numeric(Dec11_W_Avg$TotalTimeEl.x)
Dec11_W_Avg$TotalTimeEl.y<-as.numeric(Dec11_W_Avg$TotalTimeEl.y)
dropnotneeded<-c("Observer.x","Observer.y","Observer")
Dec11_W_Avg<-Dec11_W_Avg[ , !(names(Dec11_W_Avg) %in% dropnotneeded)]
Dec11_W_Avg$Freq <- rowMeans(Dec11_W_Avg[,6:7])
dropnotneeded<-c("TotalTimeEl.x","TotalTimeEl.y","TotalTimeEl")
Dec11_W<-Dec11_W_Avg[ , !(names(Dec11_W_Avg) %in% dropnotneeded)] 


#Dec11_W <- Dec11_W_Avg %>% group_by(ID,Date,Field,TimePer,FieldType) %>% summarize(Freq=mean(TotalTimeEl.x:TotalTimeEl.y))

```

```{r}
#L165<-data.frame("L165","Dec11","NB","test","control",0)
#names(L165)<-c("ID","Date","Field","TimePer","FieldType","Freq")
#Dec11_W<-rbind.data.frame(Dec11_W,L165)
Dec11_W_Test<-filter(Dec11_W,TimePer=="test")
```

#Dec11 five mins

```{r Dec9}
library(dplyr)
Dec11_W_Avg5<-full_join(Dec11_W1_test5,Dec11_W3_test5,by=c("ID","FieldType"),na.rm=T)
Dec11_W_Avg5<-full_join(Dec11_W_Avg5,Dec11_W2_test5,by=c("ID","FieldType"),na.rm=T)
Dec11_W_Avg5[is.na(Dec11_W_Avg5)]<- 0
Dec11_W_Avg5$TotalTimeEl<-as.numeric(Dec11_W_Avg5$TotalTimeEl)
Dec11_W_Avg5$TotalTimeEl.x<-as.numeric(Dec11_W_Avg5$TotalTimeEl.x)
Dec11_W_Avg5$TotalTimeEl.y<-as.numeric(Dec11_W_Avg5$TotalTimeEl.y)
dropnotneeded<-c("Observer.x","Observer.y","Observer")
Dec11_W_Avg5<-Dec11_W_Avg5[ , !(names(Dec11_W_Avg5) %in% dropnotneeded)]
Dec11_W_Avg5$Freq <- rowMeans(Dec11_W_Avg5[,3:5])
dropnotneeded<-c("TotalTimeEl.x","TotalTimeEl.y","TotalTimeEl")
Dec11_W_Avg5<-Dec11_W_Avg5[ , !(names(Dec11_W_Avg5) %in% dropnotneeded)] 

L162_5<-data.frame("L162","conditioned",0)
names(L162_5)<-c("ID","FieldType","Freq")
Dec11_W_Avg5<-rbind(Dec11_W_Avg5,L162_5)

L165_5<-data.frame("L165","control",0)
names(L165_5)<-c("ID","FieldType","Freq")
Dec11_W_Avg5<-rbind(Dec11_W_Avg5,L165_5)
```


###Dec12


```{r}
library(dplyr)
Dec12_W_Avg<-full_join(Dec12_W1,Dec12_W2,by=c("ID","Date","TimePer","Field","FieldType"),na.rm=T)
Dec12_W_Avg<-full_join(Dec12_W_Avg,Dec12_W3,by=c("ID","Date","TimePer","Field","FieldType"),na.rm=T)
Dec12_W_Avg[is.na(Dec12_W_Avg)]<- 0
Dec12_W_Avg$TotalTimeEl<-as.numeric(Dec12_W_Avg$TotalTimeEl)
Dec12_W_Avg$TotalTimeEl.x<-as.numeric(Dec12_W_Avg$TotalTimeEl.x)
Dec12_W_Avg$TotalTimeEl.y<-as.numeric(Dec12_W_Avg$TotalTimeEl.y)
dropnotneeded<-c("Observer.x","Observer.y","Observer")
Dec12_W_Avg<-Dec12_W_Avg[ , !(names(Dec12_W_Avg) %in% dropnotneeded)]
Dec12_W_Avg$Freq <- rowMeans(Dec12_W_Avg[,6:8])
dropnotneeded<-c("TotalTimeEl.x","TotalTimeEl.y","TotalTimeEl")
Dec12_W<-Dec12_W_Avg[ , !(names(Dec12_W_Avg) %in% dropnotneeded)] 

#Dec12_W <- Dec12_W_Avg %>% group_by(ID,Date,Field,TimePer,FieldType) %>% summarize(Freq=mean(TotalTimeEl.x:TotalTimeEl.y))
Dec12_W_Test<-filter(Dec12_W,TimePer=="test")
```

#December 12 five min test

```{r Dec9}
library(dplyr)
Dec12_W_Avg5<-full_join(Dec12_W1_test5,Dec12_W3_test5,by=c("ID","FieldType"),na.rm=T)
Dec12_W_Avg5<-full_join(Dec12_W_Avg5,Dec12_W2_test5,by=c("ID","FieldType"),na.rm=T)
Dec12_W_Avg5[is.na(Dec12_W_Avg5)]<- 0
Dec12_W_Avg5$TotalTimeEl<-as.numeric(Dec12_W_Avg5$TotalTimeEl)
Dec12_W_Avg5$TotalTimeEl.x<-as.numeric(Dec12_W_Avg5$TotalTimeEl.x)
Dec12_W_Avg5$TotalTimeEl.y<-as.numeric(Dec12_W_Avg5$TotalTimeEl.y)
dropnotneeded<-c("Observer.x","Observer.y","Observer")
Dec12_W_Avg5<-Dec12_W_Avg5[ , !(names(Dec12_W_Avg5) %in% dropnotneeded)]
Dec12_W_Avg5$Freq <- rowMeans(Dec12_W_Avg5[,3:5])
dropnotneeded<-c("TotalTimeEl.x","TotalTimeEl.y","TotalTimeEl")
Dec12_W_Avg5<-Dec12_W_Avg5[ , !(names(Dec12_W_Avg5) %in% dropnotneeded)]

L157_5<-data.frame("L157","conditioned",0)
names(L157_5)<-c("ID","FieldType","Freq")
Dec12_W_Avg5<-rbind(Dec12_W_Avg5,L157_5)
```



###Dec13

```{r}
library(dplyr)
Dec13_W_Avg<-full_join(Dec13_W1,Dec13_W2,by=c("ID","Date","TimePer","Field","FieldType"),na.rm=T)
Dec13_W_Avg<-full_join(Dec13_W_Avg,Dec13_W3,by=c("ID","Date","TimePer","Field","FieldType"),na.rm=T)
Dec13_W_Avg[is.na(Dec13_W_Avg)]<- 0
Dec13_W_Avg$TotalTimeEl<-as.numeric(Dec13_W_Avg$TotalTimeEl)
Dec13_W_Avg$TotalTimeEl.x<-as.numeric(Dec13_W_Avg$TotalTimeEl.x)
Dec13_W_Avg$TotalTimeEl.y<-as.numeric(Dec13_W_Avg$TotalTimeEl.y)
dropnotneeded<-c("Observer.x","Observer.y","Observer")
Dec13_W_Avg<-Dec13_W_Avg[ , !(names(Dec13_W_Avg) %in% dropnotneeded)]
Dec13_W_Avg$Freq <- rowMeans(Dec13_W_Avg[,6:8])
dropnotneeded<-c("TotalTimeEl.x","TotalTimeEl.y","TotalTimeEl")
Dec13_W<-Dec13_W_Avg[ , !(names(Dec13_W_Avg) %in% dropnotneeded)] 

#Dec13_W <- Dec13_W_Avg %>% group_by(ID,Date,Field,TimePer,FieldType) %>% summarize(Freq=mean(TotalTimeEl.x:TotalTimeEl.y))
#Dec13_W_Test<-filter(Dec13_W,TimePer=="test")
```
#use mutate to get average

```{r}
L153<-data.frame("L153","Dec13","NB","test","control",0)
names(L153)<-c("ID","Date","Field","TimePer","FieldType","Freq")
Dec13_W<-rbind.data.frame(Dec13_W,L153)
Dec13_W_Test<-filter(Dec13_W,TimePer=="test")
```


#Dec13 five mins test

```{r Dec9}
library(dplyr)
Dec13_W_Avg5<-full_join(Dec13_W1_test5,Dec13_W3_test5,by=c("ID","FieldType"),na.rm=T)
Dec13_W_Avg5<-full_join(Dec13_W_Avg5,Dec13_W2_test5,by=c("ID","FieldType"),na.rm=T)
Dec13_W_Avg5[is.na(Dec13_W_Avg5)]<- 0
Dec13_W_Avg5$TotalTimeEl<-as.numeric(Dec13_W_Avg5$TotalTimeEl)
Dec13_W_Avg5$TotalTimeEl.x<-as.numeric(Dec13_W_Avg5$TotalTimeEl.x)
Dec13_W_Avg5$TotalTimeEl.y<-as.numeric(Dec13_W_Avg5$TotalTimeEl.y)
dropnotneeded<-c("Observer.x","Observer.y","Observer")
Dec13_W_Avg5<-Dec13_W_Avg5[ , !(names(Dec13_W_Avg5) %in% dropnotneeded)]
Dec13_W_Avg5$Freq <- rowMeans(Dec13_W_Avg5[,3:5])
dropnotneeded<-c("TotalTimeEl.x","TotalTimeEl.y","TotalTimeEl")
Dec13_W_Avg5<-Dec13_W_Avg5[ , !(names(Dec13_W_Avg5) %in% dropnotneeded)]

L153_5<-data.frame("L153","control",0)
names(L153_5)<-c("ID","FieldType","Freq")
Dec13_W_Avg5<-rbind(Dec13_W_Avg5,L153_5)

L159_5<-data.frame("L159","conditioned",0)
names(L159_5)<-c("ID","FieldType","Freq")
Dec13_W_Avg5<-rbind(Dec13_W_Avg5,L159_5)
```


```{r}
Dec11_W_Avg5<-Dec11_W_Avg5[!(Dec11_W_Avg5$ID=="L153"),]
Dec11_W_Avg5<-Dec11_W_Avg5[!(Dec11_W_Avg5$ID=="L154"),]
Dec11_W_Avg5<-Dec11_W_Avg5[!(Dec11_W_Avg5$ID=="L156"),]
Dec11_W_Avg5<-Dec11_W_Avg5[!(Dec11_W_Avg5$ID=="L159"),]
Dec11_W_Avg5<-rbind(Dec11_W_Avg5,Dec13_W_Avg5)
```


#Fivemins Data Set

```{r}
W_Avg5<- rbind(Dec9_W_Avg5,Dec10_W_Avg5,Dec11_W_Avg5,Dec12_W_Avg5)
wilcox.test(Freq~FieldType,W_Avg5)
t.test(Freq~FieldType,W_Avg5)

Purple_Avg5<-rbind(Dec9_W_Avg5,Dec11_W_Avg5)
Red_Avg5<-rbind(Dec10_W_Avg5,Dec12_W_Avg5)
```

```{r}
write.csv(W_Avg5,"WaddlingData_FiveMins.csv")
```

###Red Group 
```{r}
Red_W<-rbind(Dec10_W,Dec12_W)
Red_W_Test<-rbind(Dec10_W_Test,Dec12_W_Test)
Red_W_Test<-Red_W_Test %>% mutate(Group = rep("Red"))
Red_W_Test<- Red_W_Test %>% mutate(Prop=Freq/(20*60))
Red_W_Test<- Red_W_Test %>% mutate(MagField = ifelse(Field == "NB","Canada", "Bahamas"))
```


```{r}
t.test(Freq~FieldType,Red_W_Test)
wilcox.test(Freq~FieldType,Red_W_Test)
```

paired t-test- variation per individual

pair=

difference between Conditioned & control per ID - mann-whitney

##Fixes to Dec11 & Dec13

```{r}
Dec11_W_Test<-Dec11_W_Test[!(Dec11_W_Test$ID=="L153"),]
Dec11_W_Test<-Dec11_W_Test[!(Dec11_W_Test$ID=="L154"),]
Dec11_W_Test<-Dec11_W_Test[!(Dec11_W_Test$ID=="L156"),]
Dec11_W_Test<-Dec11_W_Test[!(Dec11_W_Test$ID=="L159"),]
Dec11_W_Test<-rbind(Dec11_W_Test,Dec13_W_Test)
```

###Purple Group 
```{r}
Purple_W<-rbind(Dec9_W,Dec11_W)
Purple_W_Test<-rbind(Dec9_W_Test,Dec11_W_Test)
Purple_W_Test<- Purple_W_Test %>% mutate(Group = rep("Purple"))
Purple_W_Test<- Purple_W_Test %>% mutate(Prop=Freq/(20*60))
Purple_W_Test<- Purple_W_Test %>% mutate(MagField = ifelse(Field == "NB","Canada", "Bahamas"))
#Purple_updated<-subset(Purple_W_Test,ID!="L167")
```

```{r}
t.test(Freq~FieldType,Purple_W_Test)
wilcox.test(Freq~FieldType,Purple_W_Test)
```

###Combined Purple & Red Test Periods
```{r}
WaddleAll<-rbind(Red_W_Test,Purple_W_Test)
#write.csv(WaddleAll,"ConditioningData2017.csv")
```

###Comparison Tests -- SIGNIFICANT!!!!!!! 
```{r}
shapiro.test(WaddleAll$Freq) #Not normally distributed
levene.test(Freq~Group,WaddleAll)

library(car)

leveneTest(Freq~Group,WaddleAll)

t.test(Freq~FieldType,WaddleAll)
wilcox.test(Freq~FieldType,WaddleAll)

wilcox.test(Prop~FieldType,WaddleAll)

```

```{r}
Dec9_W_Accl<-filter(Dec9_W,TimePer=="accl")
Dec10_W_Accl<-filter(Dec10_W,TimePer=="accl")
Dec11_W_Accl<-filter(Dec11_W,TimePer=="accl")
Dec12_W_Accl<-filter(Dec12_W,TimePer=="accl")
```

```{r}
Purple_W_Cond<-filter(Purple_W_Test,FieldType=="conditioned")
Purple_W_Control<-filter(Purple_W_Test,FieldType=="control")
Purple_W_Diff<-left_join(Purple_W_Cond,Purple_W_Control,by=c("ID","TimePer"))
Purple_W_Diff<-mutate(Purple_W_Diff,TimeDiff=Freq.x-Freq.y)
Purple_W_Diff<-filter(Purple_W_Diff,TimePer=="test")
dropcols<-c("Field.x","FieldType.x","Date.x","Field.y","FieldType.y","Date.y")
Purple_W_Diff<-Purple_W_Diff[ , !(names(Purple_W_Diff) %in% dropcols)]
#names(Purple_W_Diff)<-c("ID","TimePer","Cond","Control","TimeDiff")
```

```{r}
Red_W_Cond<-filter(Red_W_Test,FieldType=="conditioned")
Red_W_Control<-filter(Red_W_Test,FieldType=="control")
Red_W_Diff<-left_join(Red_W_Cond,Red_W_Control,by=c("ID","TimePer"))
Red_W_Diff<-mutate(Red_W_Diff,TimeDiff=Freq.x-Freq.y)
Red_W_Diff<-filter(Red_W_Diff,TimePer=="test")
dropcols<-c("Field.x","FieldType.x","Date.x","Field.y","FieldType.y","Date.y")
Red_W_Diff<-Red_W_Diff[ , !(names(Red_W_Diff) %in% dropcols)]
#names(Red_W_Diff)<-c("ID","TimePer","Cond","Control","TimeDiff")
```

```{r}
Total_Diff<-full_join(Purple_W_Diff,Red_W_Diff,by=c("ID","TimePer","Cond","Control","TimeDiff"))
```

```{r}
cond<-as.vector(Total_Diff$Cond)
control<-as.vector(Total_Diff$Control)
wilcox.test(cond,control)
t.test(cond,control)

cond_data<-rbind(Purple_W_Cond,Red_W_Cond)

wilcox.test(Freq~Group,cond_data)
```

##bootstrap anova 
residulas

em means

Kruskal wallis

##unequal variances -
```{r}
aov<-aov(Freq~FieldType,data=WaddleAll)
summary(aov)
#res<-bartlett.test(Freq~FieldType,data=WaddleAll)
#res
```

```{r}
WaddleAll %>% group_by(FieldType,Group) %>% summarise(mean=mean(Freq),sd=sd(Freq),sum=sum(Freq))
```

```{r}

RedStats<-Red_W_Test %>% group_by(FieldType) %>% summarise(meanFreq=mean(Freq),sd=sd(Freq),sum=sum(Freq),meanProp=mean(Prop))
RedStats<-mutate(RedStats,Group=rep("Red"))


PurpleStats<-Purple_W_Test %>% group_by(FieldType) %>% summarise(meanFreq=mean(Freq),sd=sd(Freq),sum=sum(Freq), meanProp=mean(Prop))
PurpleStats<-mutate(PurpleStats,Group=rep("Purple"))

WaddleStats<-rbind(RedStats,PurpleStats)
WaddleStats_cond<- WaddleStats %>% filter(FieldType=="conditioned")

wilcox.test(meanFreq~Group,WaddleStats_cond)

mean(subset(WaddleAll,FieldType=="conditioned")$Prop)

mean(subset(WaddleAll,FieldType=="control")$Prop)

mean(subset(WaddleAll,Group=="Red")$Prop)

mean(Red_W_Cond$Prop)
mean(Purple_W_Cond$Prop)

mean(Red_W_Control$Prop)
mean(Purple_W_Control$Prop)

wilcox.test(Red_W_Cond$Prop,Purple_W_Cond$Prop)
```

```{r}
write.csv(WaddleAll,"C:/Users/kkmgo/OneDrive/Documents/Caretta caretta Conditioning 2017/2018/2017_testperiod_means.csv")
```

###Comaprison of displacements

```{r}

turtleroom<- read.csv("C:/Users/kkmgo/OneDrive/Documents/Caretta caretta Conditioning 2017/TurtleRoomMagField2017_ByTurtle.csv")
experfields<-read.csv("C:/Users/kkmgo/OneDrive/Documents/Caretta caretta Conditioning 2017/MagFieldInformation_ExperimentalFields.csv")

library(dplyr)
detach(package:plyr)
WaddleAll<- merge(WaddleAll,experfields,by.x="Field",all=T)
WaddleAll<- merge(WaddleAll,turtleroom,by="ID",all=T)

WaddleAll<- WaddleAll %>% mutate(Intensity.Diff = abs(Intensity-Intensity.TurtleRoom))
WaddleAll<- WaddleAll %>% mutate(Inclination.Diff = abs(Inclination-Inclination.TurtleRoom))

WaddleAll_condfield <- WaddleAll %>% filter(FieldType=="conditioned")

lm.1<- lm(Prop ~ Inclination.Diff*Intensity.Diff,data=WaddleAll)
summary(lm.1)
anova(lm.1)

lm.2<- lm(Prop ~ Inclination.Diff*Intensity.Diff*FieldType,data=WaddleAll)
summary(lm.2)
anova(lm.2)
confint(lm.2)


lm.3<- lm(Freq ~ Inclination.Diff*Intensity.Diff*Group,data=WaddleAll)
summary(lm.3)
anova(lm.3)

lm.4<- lm(Prop ~ Inclination.Diff*Intensity.Diff,data=WaddleAll_condfield)
summary(lm.4)
anova(lm.4)

lm.5<-lm(Prop ~ Inclination.Diff*Intensity.Diff*Field,data=WaddleAll)
summary(lm.5)
anova(lm.5)
#Field by itself not indicitive of a response


lm.6<-lm(Prop~Inclination.Diff*FieldType+Intensity.Diff*FieldType+Inclination.Diff*Intensity.Diff,data=WaddleAll)
summary(lm.6)
anova(lm.6)

lm.7<-lm(Prop~FieldType*Intensity.Diff*Inclination.Diff,data=WaddleAll)
summary(lm.7)
anova(lm.7)

library(car)
Anova(lm.2,type=2)
anova(lm.2)
Anova(lm.3,type=2)
Anova(lm.4,type=2)
Anova(lm.7,type=2)
```


```{r}
library(ggplot2)
RedPlot<-ggplot(RedStats,aes(x=FieldType,y=mean))+geom_point()
RedPlot
```

```{r}
WaddlebyID<-ggplot (WaddleAll,aes(x=ID,y=Freq))+geom_point(aes(color=FieldType))
WaddlebyID
```


```{r}
PurplePlot<-ggplot(PurpleStats,aes(x=FieldType,y=mean))+geom_point()
PurplePlot
```


```{r}
WaddlePlot<-ggplot(WaddleStats,aes(x=FieldType,y=mean))+geom_point()+facet_grid(~Group)
WaddlePlot + theme_minimal()
```

boxplot with all the points inside

```{r}
boxplot(Freq~FieldType,data=WaddleAll,main="Mean Waddling Time Per Field Type",xlab="Field Type",ylab="Mean Waddling Time (seconds)",col="lightblue")
```

```{r}
boxplot(Freq~FieldType,data=W_Avg5,main="Mean Waddling Time Per Field Type",xlab="Field Type",ylab="Mean Waddling Time (seconds)",col="lightblue")
```


violin plots

```{r}
library(ggplot2)
ggplot(WaddleAll,aes(x=FieldType,y=Freq))+geom_violin()+stat_summary(fun.y=mean,geom="point",size=2,color="red") + geom_jitter(shape=16,position=position_jitter(.03))

```


```{r}
library(ggplot2)
ggplot(WaddleAll,aes(x=FieldType,y=Freq))+geom_boxplot(fill="cadetblue2",color="cadetblue4")+scale_y_continuous(name="Mean Waddling Time (seconds)",breaks=seq(0,450,50))+scale_x_discrete((name="Field Type"))+ggtitle("Mean Waddling Time Per Field Type")+geom_jitter(color="darkblue",position=position_jitter(.05))+theme_bw()
```
stat_summary(fxn=mean)

####use this graph - Figure 1
```{r}
library(ggplot2)
library(extrafont)
font_import()
fonttable()
extrafont::loadfonts(device="win")

figure1<-ggplot(WaddleAll,aes(x=FieldType,y=Prop))+stat_boxplot(geom="errorbar",color="black")+geom_boxplot(outlier.shape=NA,fill="cadetblue3",color="black")+geom_point(color="black",position="jitter")+theme_bw()+scale_y_continuous(name = "Proportion of Time",breaks=c(0.00,0.04,0.08,0.12,0.16,0.2,0.24,0.28,0.32,0.36,0.4))+theme(axis.title.x=element_text(margin = margin(t = 20, r = 0, b = 0, l = 0),size=20))+theme(axis.title.y= element_text(margin = margin(t = 0, r = 20, b = 0, l = 0),size=20))+scale_x_discrete(name="Treatment")+theme(text=element_text(size=18,family="Calibri"))+theme(panel.border = element_blank(), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))

my_comparisons<- list(c("conditioned","control"))

figure1+stat_compare_means(comparison=my_comparisons,label="p.signif",label.y = 0.4,method="wilcox.test")




figure2<-ggplot(Red_W_Test,aes(x=FieldType,y=Prop))+stat_boxplot(geom="errorbar",color="black")+geom_boxplot(outlier.shape=NA,fill="indianred",color="black")+geom_point(color="black",position="jitter")+theme_bw()+scale_y_continuous(breaks=c(0.00,0.04,0.08,0.12,0.16,0.2,0.24,0.28,0.32,0.36,0.4))+theme(axis.title.x=element_text(margin = margin(t = 20, r = 0, b = 0, l = 0),size=20))+theme(axis.title.y= element_text(margin = margin(t = 0, r = 20, b = 0, l = 0),size=20))+theme(text=element_text(size=18,family="Calibri"),axis.title.x = element_blank(),axis.title.y=element_blank())+theme(plot.margin = margin(t=40,r=20,b=10,l=20))+ggtitle("Group 1")+theme(plot.title = element_text(size = 22,hjust=0.5,family = "Calibri",margin = margin(t=0,r=0,b=20,l=0)))+theme(panel.border = element_blank(), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+stat_compare_means(comparison=my_comparisons,label="p.signif",label.y = 0.4,method="wilcox.test")
figure2



figure3<-ggplot(Purple_W_Test,aes(x=FieldType,y=Prop))+stat_boxplot(geom="errorbar",color="black")+geom_boxplot(outlier.shape=NA,fill="thistle3",color="black")+geom_point(color="black",position="jitter")+theme_bw()+scale_y_continuous(breaks=c(0.00,0.04,0.08,0.12,0.16,0.2,0.24,0.28,0.32,0.36,0.4),limits=c(0.00,0.4))+theme(axis.title.x=element_text(margin = margin(t = 20, r = 0, b = 0, l = 0),size=20))+theme(axis.title.y= element_text(margin = margin(t = 0, r = 20, b = 0, l = 0),size=20))+theme(text=element_text(size=18,family="Calibri"),axis.title.x = element_blank(),axis.title.y=element_blank())+theme(plot.margin = margin(t=40,r=20,b=10,l=10))+ggtitle("Group 2")+theme(plot.title = element_text(size = 22,hjust=0.5,family = "Calibri",margin = margin(t=0,r=0,b=20,l=0)))+theme(panel.border = element_blank(), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+stat_compare_means(comparison=my_comparisons,label="p.signif",label.y = 0.4,method="wilcox.test")
figure3


library(cowplot)
library(grid)
library(gridExtra)
library(ggpubr)
figure4a<-plot_grid(figure2,figure3,rel_widths = c(1,1))+draw_label("A",fontfamily = "Calibri", x = 0, y = 1, hjust = -0.5, vjust = 1.5)+draw_label("B",fontfamily = "Calibri",x=0.5,y=1,hjust=0.5,vjust=1.5)
figure4a
grid.arrange(arrangeGrob(figure4a,top=text_grob(""),
                bottom = text_grob("Treatment", color = "black",
                                   hjust = 0.5, size = 20,family="Calibri"),
                left = text_grob("Proportion of Time", color = "black", rot = 90,size=20,family="Calibri"),padding=unit(2,"line"
                )))


mean(Red_W_Test$Prop)
mean(Purple_W_Test$Prop)
mean(WaddleAll_condfield$Prop)


mean(subset(WaddleAll,FieldType=="control")$Prop)

mean(subset(Red_W_Test,FieldType=="control")$Prop)


mean(subset(Purple_W_Test,FieldType=="control")$Prop)
```


```{r}
library(ggplot2)

red<-ggplot(Red_W_Test,aes(x=FieldType,y=Freq))+stat_boxplot(geom='errorbar',color="gray1")+geom_boxplot(fill="red2",color="gray1")+scale_y_continuous(name="Time (seconds)",breaks=seq(0,500,100))+scale_x_discrete((name="Field Type"))+ggtitle("New Brunswick Group\nMean Food-Seeking Behavior Time\nPer Magnetic Field")+theme_bw()+theme(plot.title = element_text(hjust = 0.5))+stat_summary(fun.y=mean, geom="point", shape=22, size=3, color="gray1", fill="gray1")
red


red<-ggplot(Red_W_Test,aes(x=FieldType,y=Prop))+stat_summary(fun.y="mean",geom="bar",color="#990000",fill="#990000")+stat_summary(fun.y=mean,fun.ymin = function(x) mean(x)-sd(x)/length(x),fun.ymax = function(x) mean(x) + sd(x)/length(x),geom="errorbar",color="black")+theme_bw()+scale_y_continuous(breaks=c(0.00,0.04,0.08,0.12,0.16,0.2))+ggtitle("Group 1") +theme(text=element_text(size=24))+theme(plot.title = element_text(margin = margin(t = 20, r = 0, b = 20, l = 0),hjust=0.5))+theme(axis.title.x=element_blank())+theme(axis.title.y=element_blank())+theme(plot.margin=unit(c(0.2,0.2,0.3,0.5),"cm"))
red


purple<-ggplot(Purple_W_Test,aes(x=FieldType,y=Freq))+stat_boxplot(geom='errorbar',color="gray1")+geom_boxplot(fill="darkorchid3",color="gray1")+scale_y_continuous(name="Time (seconds)",breaks=seq(0,200,50))+scale_x_discrete((name="Field Type"))+ggtitle("Bahamas Group \nMean Food-Seeking Behavior Time\nPer Magnetic Field")+theme_bw()+theme(plot.title = element_text(hjust = 0.5))+stat_summary(fun.y=mean, geom="point", shape=22, size=3, color="gray1", fill="gray1")

library(ggpubr)
ggarrange(red,purple,labels=c("A","B"),ncol = 2,nrow = 1)
```


```{r}
library(ggplot2)

ggplot(WaddleAll,aes(x=FieldType,y=Prop))+stat_summary(fun.y="mean",geom="bar",fill="cadetblue1")+stat_summary(fun.y=mean,fun.ymin = function(x) mean(x) - sd(x),fun.ymax = function(x) mean(x) + sd(x),geom="errorbar")+theme_bw()+scale_y_continuous(name="Time (seconds)")+scale_x_discrete(name="Field Type")+ggtitle("Mean Food-Seeking Behavior Time per Magnetic Field")

```


```{r}
library(ggplot2)

ggplot(WaddleAll,aes(x=FieldType,y=Prop))+stat_summary(fun.y="mean",geom="bar",color="lightblue",fill="lightblue")+stat_summary(fun.y=mean,fun.ymin = function(x) mean(x) - sd(x)/length(x),fun.ymax = function(x) mean(x) + sd(x)/length(x),geom="errorbar",color="black")+theme_bw()+scale_y_continuous(name="Time (seconds)")+scale_x_discrete(name="Field Type")+ggtitle("Mean Food-Seeking Behavior Time per Magnetic Field")

```



```{r}
library(ggplot2)

ggplot(W_Avg5,aes(x=FieldType,y=Freq))+stat_summary(fun.y="mean",geom="bar",color="lightblue",fill="lightblue")+stat_summary(fun.y=mean,fun.ymin = function(x) mean(x)-sd(x)/length(x),fun.ymax = function(x) mean(x) + sd(x)/length(x),geom="errorbar",color="black")+theme_bw()+scale_y_continuous(name="Time (seconds)")+scale_x_discrete(name="Field Type")+ggtitle("Mean Food-Seeking Behavior Time per Magnetic Field")

```


```{r}
library(ggplot2)

ggplot(W_Avg5,aes(x=FieldType,y=Freq))+stat_summary(fun.y="mean",geom="bar",color="blue",fill="blue")+stat_summary(fun.ymin=mean,fun.ymax = function(x) mean(x) + sd(x),geom="errorbar",color="blue")+theme_bw()+scale_y_continuous(name="Time (seconds)")+scale_x_discrete(name="Field Type")+ggtitle("Mean Food-Seeking Behavior Time per Magnetic Field")
```


#######Figures for ISTS PRESENTATION
```{r}
library(ggplot2)

red<-ggplot(Red_W_Test,aes(x=FieldType,y=Prop))+stat_summary(fun.y="mean",geom="bar",color="#990000",fill="#990000")+stat_summary(fun.y=mean,fun.ymin = function(x) mean(x)-sd(x)/length(x),fun.ymax = function(x) mean(x) + sd(x)/length(x),geom="errorbar",color="black")+theme_bw()+scale_y_continuous(breaks=c(0.00,0.04,0.08,0.12,0.16,0.2))+ggtitle("Group 1") +theme(text=element_text(size=24))+theme(plot.title = element_text(margin = margin(t = 0, r = 0, b = 20, l = 0),hjust=0.5))+theme(axis.title.x=element_blank())+theme(axis.title.y=element_blank())+theme(plot.margin = margin(t=40,r=20,b=10,l=10)))
red


purple<-ggplot(Purple_W_Test,aes(x=FieldType,y=Prop))+stat_summary(fun.y="mean",geom="bar",color="#CC99FF",fill="#CC99FF")+stat_summary(fun.y=mean,fun.ymin = function(x) mean(x)-sd(x)/length(x),fun.ymax = function(x) mean(x) + sd(x)/length(x),geom="errorbar",color="black")+theme_bw()+theme(text=element_text(size=24),axis.title.x = element_blank(),axis.title.y=element_blank(),axis.text.y=element_blank()) + scale_y_continuous(breaks=c(0.00,0.04,0.08,0.12,0.16,0.2),limits=c(0.00,0.14))+ggtitle("Group 2")+ theme(plot.title = element_text(margin = margin(t = 0, r = 0, b = 20, l = 0),hjust=0.5))+theme(plot.margin=unit(c(0.2,0.2,0.3,0.2),"cm"))
purple

library(ggpubr)
figure<- ggarrange(red,purple,labels= c("A","B"),ncol = 2,nrow = 1)
figure
#par(oma=c(2,2,2,2))
annotate_figure(figure,
                top = text_grob("Food-Seeking Behavior", color = "black", face = "bold", size = 28),
                bottom = text_grob("Treatment", color = "black",
                                   hjust = 0.5, face = "italic", size = 24),
                left = text_grob("Proportion of Time", color = "black", rot = 90,size=24,face="italic")
                )

```


####Bar Figures for Paper
```{r BAR FIGURES - MEAN PROPO}
library(ggplot2)

redgroup<-ggplot(Red_W_Test,aes(x=FieldType,y=Prop))+stat_summary(fun.y="mean",geom="bar",color="gray29",fill="gray29")+stat_summary(fun.y=mean,fun.ymin = function(x) mean(x)-sd(x)/length(x),fun.ymax = function(x) mean(x) + sd(x)/length(x),geom="errorbar",color="black")+theme_bw()+scale_y_continuous(breaks=c(0.00,0.04,0.08,0.12,0.16),expand=c(0,0))+ggtitle("Group 1") +theme(text=element_text(size=18,family = "Calibri"))+theme(plot.title = element_text(margin = margin(t = 20, r = 0, b = 20, l = 0),hjust=0.5,size=22,family = "Calibri"))+theme(axis.title.x=element_blank())+theme(axis.title.y=element_blank())+theme(plot.margin = margin(t=40,r=20,b=10,l=10))+coord_cartesian(ylim = c(0.0,0.16))
redgroup


purplegroup<-ggplot(Purple_W_Test,aes(x=FieldType,y=Prop))+stat_summary(fun.y="mean",geom="bar",color="gray54",fill="gray54")+stat_summary(fun.y=mean,fun.ymin = function(x) mean(x)-sd(x)/length(x),fun.ymax = function(x) mean(x) + sd(x)/length(x),geom="errorbar",color="black")+theme_bw()+theme(text=element_text(size=18,family = "Calibri"),axis.title.x = element_blank(),axis.title.y=element_blank()) + scale_y_continuous(breaks=c(0.00,0.04,0.08,0.12,0.16),limits=c(0.00,0.16),expand=c(0,0))+ggtitle("Group 2")+ theme(plot.title = element_text(margin = margin(t = 20, r = 0, b = 20, l = 0),hjust=0.5,size=20,family = "Calibri"))+theme(plot.margin = margin(t=40,r=20,b=10,l=10))
purplegroup


library(cowplot)
library(grid)
library(gridExtra)
library(ggpubr)
figure_bar<-plot_grid(redgroup,purplegroup,align = 'h',rel_widths = c(1,1),rel_heights = c(1,1))+draw_label("A",fontfamily = "Calibri", x = 0, y = 1, hjust = -0.5, vjust = 1.5)+draw_label("B",fontfamily = "Calibri",x=0.5,y=1,hjust=0.5,vjust=1.5)
figure_bar
grid.arrange(arrangeGrob(figure_bar,top=text_grob(""),
                bottom = text_grob("Treatment", color = "black",
                                   hjust = 0.5, size = 20,family="Calibri"),
                left = text_grob("Proportion of Time", color = "black", rot = 90,size=20,family="Calibri"),padding=unit(2,"line"
                )))




fig4<-ggplot(WaddleAll,aes(x=FieldType,y=Prop))+stat_summary(fun.y="mean",geom="bar",fill="grey48")+stat_summary(fun.y=mean,fun.ymin = function(x) mean(x)-sd(x)/length(x),fun.ymax = function(x) mean(x) + sd(x)/length(x),geom="errorbar",color="black")+theme_bw()+scale_y_continuous(name="Proportion of Time",breaks=c(0.00,0.04,0.08,0.12,0.16),expand = c(0,0))+scale_x_discrete(name="Treatment")+theme(plot.margin=margin(20,20,20,20))+theme(axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0),size=20,family = "Calibri"),axis.title.x = element_text(margin = margin(t = 20, r = 0, b = 0, l = 0),size=20,family = "Calibri"))+theme(text=element_text(size=20,family="Calibri"))+coord_cartesian(ylim=c(0,0.14))
fig4



```









Change fnt size:
theme_bw()+theme(element_text(size=10))+

Using ggarrange:
figure <- ggarrange(sp, bp + font("x.text", size = 10),
                    ncol = 1, nrow = 2)
annotate_figure(figure,
                top = text_grob("Visualizing mpg", color = "red", face = "bold", size = 14),
                bottom = text_grob("Data source: \n mtcars data set", color = "blue",
                                   hjust = 1, x = 1, face = "italic", size = 10),
                left = text_grob("Figure arranged using ggpubr", color = "green", rot = 90),
                right = "I'm done, thanks :-)!",
                fig.lab = "Figure 1", fig.lab.face = "bold"
                )
                
                
Change margins:
theme(axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))
theme(axis.title.x = element_text(margin = margin(t = 20, r = 0, b = 0, l = 0)))
theme(plot.title = element_text(margin = margin(t = 20, r = 0, b = 20, l = 0)))


Remove Axes Titles:
theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

```{r BAR FIGURES}
library(ggplot2)


fig<-ggplot(WaddleAll,aes(x=FieldType,y=Prop,fill=Group))+stat_summary(fun.y="mean",geom="bar")+stat_summary(fun.y=mean,fun.ymin = function(x) mean(x)-sd(x)/length(x),fun.ymax = function(x) mean(x) + sd(x)/length(x),geom="errorbar",color="black")+theme_bw()+scale_y_continuous(name="Proportion of Time",breaks=c(0.00,0.04,0.08,0.12,0.16))+scale_x_discrete(name="Treatment")+ggtitle("Food-Seeking Behaviors per Magnetic Field")+theme(plot.title = element_text(size=24,face="bold",margin = margin(t = 20, r = 0, b = 20, l = 0),hjust=0.5))+theme(plot.margin=unit(c(1,1,1,1),"cm"))+facet_wrap(.~MagField)+scale_fill_manual(labels=c("Group 2","Group 1"),values=c("#CC99FF","#990000"))+theme(axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0),size=20,face="italic"),axis.title.x = element_text(margin = margin(t = 20, r = 0, b = 0, l = 0),size=20,face = "italic"))+theme(text=element_text(size=20))+ guides(fill = guide_legend(reverse=TRUE))+theme(strip.background = element_rect(fill="white"))
fig


fig2<-ggplot(WaddleAll,aes(x=FieldType,y=Prop))+stat_summary(fun.y="mean",geom="bar",fill="#3399FF")+stat_summary(fun.y=mean,fun.ymin = function(x) mean(x)-sd(x)/length(x),fun.ymax = function(x) mean(x) + sd(x)/length(x),geom="errorbar",color="black")+theme_bw()+scale_y_continuous(name="Proportion of Time",breaks=c(0.00,0.04,0.08,0.12,0.16))+scale_x_discrete(name="Treatment")+ggtitle("Food-Seeking Behaviors per Treatment")+theme(plot.title = element_text(size=24,face="bold",margin = margin(t = 20, r = 0, b = 20, l = 0),hjust=0.5))+theme(plot.margin=unit(c(1,1,1,1),"cm"))+theme(axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0),size=20,face="italic"),axis.title.x = element_text(margin = margin(t = 20, r = 0, b = 0, l = 0),size=20,face = "italic"))+theme(text=element_text(size=20))
fig2



```


###Change Strip Color
g <- ggplot_gtable(ggplot_build(fig))
stripr <- which(grepl('strip-r', g$layout$name))
fills <- c("red","purple")
k <- 1
for (i in stripr) {
  j <- which(grepl('rect', g$grobs[[i]]$grobs[[1]]$childrenOrder))
  g$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- fills[k]
  k <- k+1
}
grid.draw(g)

```{r FIGS 5 MINUTE DATA}
library(ggplot2)

red<-ggplot(Red_Avg5,aes(x=FieldType,y=Freq))+stat_summary(fun.y="mean",geom="bar",color="red",fill="red")+stat_summary(fun.y=mean,fun.ymin = function(x) mean(x)-sd(x)/length(x),fun.ymax = function(x) mean(x) + sd(x)/length(x),geom="errorbar",color="black")+theme_bw()+scale_y_continuous(breaks=c(0,5,10,15,20,25,30,35),name="Time (seconds)")+scale_x_discrete(name="Field Type")+ggtitle("New Brunswick Group\nMean Food-Seeking Behavior Time\nper Magnetic Field")


purple<-ggplot(Purple_Avg5,aes(x=FieldType,y=Freq))+stat_summary(fun.y="mean",geom="bar",color="purple",fill="purple")+stat_summary(fun.y=mean,fun.ymin = function(x) mean(x)-sd(x)/length(x),fun.ymax = function(x) mean(x) + sd(x)/length(x),geom="errorbar",color="black")+theme_bw()+scale_y_continuous(breaks=c(0,5,10,15,20,25),name="Time (seconds)")+scale_x_discrete(name="Field Type")+ggtitle("Bahamas Group\nMean Food-Seeking Behavior Time\nper Magnetic Field")


library(ggpubr)
ggarrange(red,purple,labels=c("A","B"),ncol = 2,nrow = 1)

```


```{r SUPPLEMENTAL FIGS}
library(ggplot2)


figure.s3<- ggplot(WaddleAll_condfield,aes(x=Inclination.Diff,y=Prop))+geom_point(aes(color=Group,size=0.01))+theme_bw()+scale_y_continuous(breaks=c(0.00,0.08,0.16,0.24,0.32,0.4),limits=c(0.00,0.36))+theme(axis.title.x=element_text(margin = margin(t = 20, r = 0, b = 0, l = 0),size=16))+scale_x_continuous(name="Difference in\n Inclination Angle",breaks = c(0,2.5,5,7.5,10,12.5),limits=c(2.5,12.5))+theme(axis.title.y= element_text(margin = margin(t = 0, r = 20, b = 0, l = 0),size=16))+theme(text=element_text(size=16,family="Calibri"),axis.title.y = element_blank())+theme(plot.margin = margin(t=40,r=20,b=10,l=10))+scale_color_manual(labels=c("Group 2","Group 1"),values=c("grey20","grey60"),guide=guide_legend(reverse = T))+scale_size(guide='none')
figure.s3


figure.s4<- ggplot(WaddleAll_condfield,aes(x=Intensity.Diff,y=Prop))+geom_point(aes(color=Group,size=0.01))+theme_bw()+scale_y_continuous(breaks=c(0.00,0.08,0.16,0.24,0.32,0.4),limits=c(0.00,0.36))+theme(axis.title.x=element_text(margin = margin(t = 20, r = 0, b = 0, l = 0),size=16))+scale_x_continuous(name="Difference in\n Field Intensity",limits=c(0,8))+theme(axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0),size=16))+theme(text=element_text(size=16,family="Calibri"),axis.title.y = element_blank())+theme(plot.margin = margin(t=40,r=20,b=10,l=10))+scale_color_manual(labels=c("Group 2","Group 1"),values=c("grey20","grey60"),guide=guide_legend(reverse = T))+scale_size(guide='none')
figure.s4


library(cowplot)
library(grid)
library(gridExtra)
library(ggpubr)
figure_bar<-plot_grid(figure.s3 +theme(legend.position = 'none'),figure.s4+theme(legend.position = 'none'),align = 'h',rel_widths = c(1,1),rel_heights = c(1,1))+draw_label("A",fontfamily = "Calibri", x = 0, y = 1, hjust = -0.5, vjust = 1.5)+draw_label("B",fontfamily = "Calibri",x=0.5,y=1,hjust=0.5,vjust=1.5)
figure_bar
grid.arrange(arrangeGrob(figure_bar,top=text_grob(""),
                bottom = text_grob(""),
                left = text_grob("Proportion of Time", color = "black", rot = 90,size=16,family="Calibri"),padding=unit(2,"line"
                )))

legend<-get_legend(figure.s3+theme(legend.position = "bottom"))

figure.s5<-plot_grid(figure_bar,legend,ncol=1,rel_heights = c(1,0.1))
figure.s5
grid.arrange(arrangeGrob(figure.s5,top=text_grob(""),
                bottom = text_grob(""),
                left = text_grob("Proportion of Time", color = "black", rot = 90,size=16,family="Calibri"),padding=unit(2,"line"
                )))


figure.s6<- ggplot(WaddleAll,aes(x=Intensity.Diff,y=Prop))+geom_point(aes(color=FieldType,size=0.01))+theme_bw()+scale_y_continuous(name="Proportion of Time",breaks=c(0.00,0.08,0.16,0.24,0.32,0.4),limits=c(0.00,0.36))+theme(axis.title.x=element_text(margin = margin(t = 20, r = 0, b = 0, l = 0),size=16))+scale_x_continuous(name="Difference in\n Field Intensity",limits=c(5,75),breaks=c(0,25,50))+theme(axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0),size=16))+theme(text=element_text(size=16,family="Calibri"))+theme(plot.margin = margin(t=40,r=20,b=10,l=10))+scale_color_manual(values=c("grey20","grey60"),guide=guide_legend(reverse = T))+scale_size(guide='none')

labels <- c(Red = "Group 1", Purple = "Group 2")

WaddleAll$Group <- factor(WaddleAll$Group, levels=c("Red","Purple"))

figure.s6 + facet_grid(.~Group, labeller=labeller(Group = labels))

figure.s7<- ggplot(WaddleAll,aes(x=Inclination.Diff,y=Prop))+geom_point(aes(color=FieldType,size=0.01))+facet_wrap(.~Group)+theme_bw()+scale_y_continuous(name="Proportion of Time",breaks=c(0.00,0.08,0.16,0.24,0.32,0.4),limits=c(0.00,0.36))+theme(axis.title.x=element_text(margin = margin(t = 20, r = 0, b = 0, l = 0),size=16))+scale_x_continuous(name="Difference in\n Field Inclination",limits=c(2.5,12.5),breaks=c(0,5,10))+theme(axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0),size=16))+theme(text=element_text(size=16,family="Calibri"))+theme(plot.margin = margin(t=40,r=20,b=10,l=10))+scale_color_manual(values=c("grey20","grey60"),guide=guide_legend(reverse = T))+scale_size(guide='none')
figure.s7+facet_grid(.~Group, labeller=labeller(Group = labels))

```





